### 2021-02-02 paper.tex
initial commit

% -*- coding: utf-8; -*-
% vim: set fileencoding=utf-8 :
\documentclass[english]{programming}
%% First parameter: the language is 'english'.
%% Second parameter: use 'submission' for initial submission, remove it for camera-ready (see 5.1)

\usepackage{longtable,booktabs}
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}

\usepackage{color}
\usepackage{fancyvrb}
\newcommand{\VerbBar}{|}
\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
% Add ',fontsize=\small' for more characters per line
\newenvironment{Shaded}{}{}
\newcommand{\AlertTok}[1]{\textcolor[rgb]{1.00,0.00,0.00}{\textbf{#1}}}
\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.38,0.63,0.69}{\textbf{\textit{#1}}}}
\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.49,0.56,0.16}{#1}}
\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.25,0.63,0.44}{#1}}
\newcommand{\BuiltInTok}[1]{#1}
\newcommand{\CharTok}[1]{\textcolor[rgb]{0.25,0.44,0.63}{#1}}
\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.38,0.63,0.69}{\textit{#1}}}
\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.38,0.63,0.69}{\textbf{\textit{#1}}}}
\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.53,0.00,0.00}{#1}}
\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.00,0.44,0.13}{\textbf{#1}}}
\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.56,0.13,0.00}{#1}}
\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.25,0.63,0.44}{#1}}
\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.73,0.13,0.13}{\textit{#1}}}
\newcommand{\ErrorTok}[1]{\textcolor[rgb]{1.00,0.00,0.00}{\textbf{#1}}}
\newcommand{\ExtensionTok}[1]{#1}
\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.25,0.63,0.44}{#1}}
\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.02,0.16,0.49}{#1}}
\newcommand{\ImportTok}[1]{#1}
\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.38,0.63,0.69}{\textbf{\textit{#1}}}}
\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.00,0.44,0.13}{\textbf{#1}}}
\newcommand{\NormalTok}[1]{#1}
\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.40,0.40,0.40}{#1}}
\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.00,0.44,0.13}{#1}}
\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.74,0.48,0.00}{#1}}
\newcommand{\RegionMarkerTok}[1]{#1}
\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.25,0.44,0.63}{#1}}
\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.73,0.40,0.53}{#1}}
\newcommand{\StringTok}[1]{\textcolor[rgb]{0.25,0.44,0.63}{#1}}
\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.10,0.09,0.49}{#1}}
\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.25,0.44,0.63}{#1}}
\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.38,0.63,0.69}{\textbf{\textit{#1}}}}

\usepackage[backend=biber]{biblatex}
\addbibresource{references2.bib}

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

%%% The following is specific to <Programming'20> Companion-CCS and the paper
%%% 'Wildcard: Spreadsheet-Driven Customization of Web Applications'
%%% by Geoffrey Litt and Daniel Jackson.
%%%
%%% (Author note: Commented out this info, doesn't seem to fit with this template)
% \setcopyright{acmlicensed}
% \acmPrice{}
% \acmDOI{10.1145/3397537.3397541}
% \acmYear{2020}
% \copyrightyear{2020}
% \acmSubmissionID{prog20ccs-id3-p}
% \acmISBN{978-1-4503-7507-8/20/03}
% \acmConference[<Programming'20> Companion]{Companion Proceedings of the 4th International Conference on the Art, Science, and Engineering of Programming}{March 23--26, 2020}{Porto, Portugal}
% \acmBooktitle{Companion Proceedings of the 4th International Conference on the Art, Science, and Engineering of Programming (<Programming'20> Companion), March 23--26, 2020, Porto, Portugal}

\begin{document}

\title{Wildcard: Spreadsheet-Driven Customization of Web Applications}
\subtitle{}% optional

\author{Geoffrey Litt}
\authorinfo{is a PhD student at MIT in the Software Design Group. His research focuses on programming languages and environments, particularly tools for end user programming and live programming. Contact him at \email{glitt@mit.edu}.}
\author{Daniel Jackson}
\authorinfo{is Professor in the Department of Electrical Engineering and Computer Science at MIT,  a MacVicar teaching fellow, and Associate Director of the Computer Science and Artificial Intelligence Laboratory. He leads the Software Design Group. Contact him at \email{dnj@csail.mit.edu}.}
\affiliation{Massachusetts Institute of Technology}

\keywords{end-user programming, software customization, web browser extensions} % please provide 1--5 keywords

%%%%%%%%%%%%%%%%%%
%% These data MUST be filled for your submission. (see 5.3)
\paperdetails{
  %% perspective options are: art, sciencetheoretical, scienceempirical, engineering.
  %% Choose exactly the one that best describes this work. (see 2.1)
  perspective=art,
  %% State one or more areas, separated by a comma. (see 2.2)
  %% Please see list of areas in http://programming-journal.org/cfp/
  %% The list is open-ended, so use other areas if yours is/are not listed.
  area={Programming environments, Visual and live programming},
  %% You may choose the license for your paper (see 3.)
  %% License options include: cc-by (default), cc-by-nc
  % license=cc-by-sa,
}
%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%
%% These data are provided by the editors. May be left out on submission.
%\paperdetails{
%  submitted=2016-08-10,
%  published=2016-10-11,
%  year=2016,
%  volume=1,
%  issue=1,
%  articlenumber=1,
%}
%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Please go to https://dl.acm.org/ccs/ccs.cfm and generate your Classification
% System [view CCS TeX Code] stanz and copy _all of it_ to this place.
%% From HERE
\begin{CCSXML}
<ccs2012>
<concept>
<concept_id>10011007.10011006.10011066.10011069</concept_id>
<concept_desc>Software and its engineering~Integrated and visual development environments</concept_desc>
<concept_significance>500</concept_significance>
</concept>
</ccs2012>
\end{CCSXML}

\ccsdesc[500]{Software and its engineering~Integrated and visual development environments}
% To HERE
%%%%%%%%%%%%%%%%%%%%%%%

\maketitle

% Please always include the abstract.
% The abstract MUST be written according to the directives stated in
% http://programming-journal.org/submission/
% Failure to adhere to the abstract directives may result in the paper
% being returned to the authors.
\begin{abstract}
Many Web applications do not meet the precise needs of their users.
Browser extensions offer a way to customize web applications, but most
people do not have the programming skills to implement their own
extensions.

In this paper, we present \emph{spreadsheet-driven customization}, a
technique that enables end users to customize software without doing any
traditional programming. The idea is to augment an application's UI with
a spreadsheet that is synchronized with the application's data. When the
user manipulates the spreadsheet, the underlying data is modified and
the changes are propagated to the UI, and vice versa.

We have implemented this technique in a prototype browser extension
called Wildcard. Through concrete examples, we demonstrate that Wildcard
can support useful customizations---ranging from sorting lists of search
results to showing related data from web APIs---on top of existing
websites. We also present the design principles underlying our
prototype.

Customization can lead to dramatically better experiences with software.
We think that spreadsheet-driven customization offers a promising new
approach to unlocking this benefit for all users, not just programmers.

This paper is best viewed in the online version (\url{https://www.geoffreylitt.com/wildcard/salon2020}), which includes videos demonstrating the interface.
\end{abstract}

\hypertarget{sec:introduction}{%
\section{Introduction}\label{sec:introduction}}

Web applications often don't meet the precise needs of their users.
Sometimes there is a browser extension available to patch an issue, and
if the user is a programmer they might be able to fix it themselves. But
for most people, the only recourse is to complain to the developers, or,
more likely, to simply give up. Back in 1977, in \emph{Personal Dynamic
Media} \autocite{kay1977}, Alan Kay envisioned personal computing as a
medium that let a user ``mold and channel its power to his own needs,''
but today, software behaves more like concrete than clay.

In this paper, we present \emph{spreadsheet-driven customization}, a
technique that enables end users to customize software without doing any
traditional programming. The idea is to augment an application's UI with
a spreadsheet that is synchronized with the application's data. When the
user manipulates the spreadsheet, the underlying data is modified and
the changes are propagated to the UI, and vice versa.

We have implemented this technique in a prototype browser extension
called Wildcard and used it to build demos which suggest that this
paradigm can support useful customizations, ranging from sorting lists
of data to adding whole new features to applications (shown in
Section~\ref{sec:demos}).

\begin{figure}
\hypertarget{fig:overview}{%
\centering
\includegraphics{media/overview-300dpi.png}
\caption{An overview of spreadsheet-driven
customization}\label{fig:overview}
}
\end{figure}

Our approach requires extracting structured data from the user
interfaces of existing applications, but we hide the complexity of data
extraction from end users. Programmers write \emph{site adapters} which
use web scraping techniques to extract structured data from existing
applications and map it to the spreadsheet table. Our prototype suggests
that it is possible to implement site adapters for real websites;
Section~\ref{sec:implementation} describes some of the techniques and
challenges involved.

Spreadsheet-driven customization is based on three design principles,
described in Section~\ref{sec:design-principles}:

\begin{itemize}
\tightlist
\item
  \textbf{Expose a universal structure}: By mapping the data in all
  applications to the same universal table abstraction, Wildcard enables
  users to learn a generic customization toolkit that they can apply to
  any site.
\item
  \textbf{Low floor, high ceiling}: Wildcard provides an easy entry
  point for end users, since small tweaks like sorting data can be
  performed with a single click. At the same time, it also supports a
  variety of richer customizations, like adding private annotations to a
  webpage or joining in related data from a web API.
\item
  \textbf{Design for an ecosystem of users}: Spreadsheet-driven
  customization combines the efforts of programmers and end users,
  rather than putting the full burden on end users. We also envision a
  role for first party developers to help make their applications more
  customizable.
\end{itemize}

Prior work \autocite{mccutchen2016,benson2014,chang2014} has enabled end
users to create ``spreadsheet-driven applications'' which use
spreadsheets as a backing data layer. Spreadsheet-driven
\emph{customization} applies this idea in a different context:
customizing existing software, rather than building new software from
scratch. Our technique does not require that the application actually be
backed by a spreadsheet; it merely uses the spreadsheet as an interface
for viewing and modifying the internal state of the application. In
Section~\ref{sec:related-work}, we describe further how Wildcard relates
to existing work on spreadsheet-driven apps, as well as work in other
areas like web customization and web scraping.

The Wildcard extension is currently an early research prototype. We plan
to continue testing the system with our own use cases to explore how the
spreadsheet abstraction maps to real websites and customization needs.
Eventually we plan to release the tool publicly in order to learn from
real use cases, discover usability challenges, and to test the
feasibility of building and maintaining site adapters.
Section~\ref{sec:conclusion} describes open questions we plan to
continue exploring, as well as our future plans.

\hypertarget{sec:demos}{%
\section{Demos}\label{sec:demos}}

Here are some examples of using Wildcard to customize websites in useful
ways.{ These demos are best viewed as videos in the online version of
this paper (\url{https://www.geoffreylitt.com/wildcard/salon2020}).}

\begin{figure}
\hypertarget{fig:airbnb-demo}{%
\centering
\includegraphics{media/airbnb-demo-300dpi.png}
\caption{Using Wildcard to augment the Airbnb search page for booking
accommodations}\label{fig:airbnb-demo}
}
\end{figure}

\hypertarget{augmenting-search-results}{%
\subsection{Augmenting search results}\label{augmenting-search-results}}

In 2012, the travel site Airbnb removed the ability to sort
accommodation searches by price. Users could still filter by price
range, but could no longer view the cheapest listings first. Many users
complained that the change seemed hostile to users. ``It's so
frustrating! What is the logic behind not having this function?'' said
one user on the
\href{https://community.withairbnb.com/t5/Hosting/Sorting-listing-by-price/td-p/559404}{Airbnb
support forum}. Alas, the feature remains missing to this day.

Using Wildcard, the user can fix this omission, while leaving the page's
design and the rest of its functionality unchanged.{
Figure~\ref{fig:airbnb-demo} shows an overview of augmenting the Airbnb
site.} First, the user opens up the Wildcard panel, which shows a table
corresponding to the search results in the page. As they click around in
the table, the corresponding row in the page is highlighted to indicate
the mapping between the views.

Then, the user clicks on the price column header to sort the spreadsheet
and the Airbnb UI by price{ (Figure~\ref{fig:airbnb-demo}, Note A)}.
They also filter to listings with a user rating above 4.5 (another
feature missing in the original Airbnb UI).

After manipulating the data, the user closes the table view and
continues using the website. Because the application's UI usually has a
nicer visual design than a spreadsheet, Wildcard does not aim to replace
it---at any time, the user can use either the UI, the spreadsheet, or
both together.

Many websites that show lists of data also offer actions on rows in the
table, like adding an item to a shopping cart. Wildcard has the ability
to make these ``row actions'' available in the data table through the
site adapter. In the Airbnb UI, saving multiple listings to a Favorites
list requires tediously clicking through them one by one. Using Wildcard
row actions, the user can select multiple rows and favorite all of them
with a single click{ (Figure~\ref{fig:airbnb-demo}, Note B)}. Similarly,
the user can open the detailed pages for many listings at once.

Next, the user wants to jot down some notes about each listing. To do
this, they type some notes into an additional column in each row, and
the notes appear inside the listings in the original UI{
(Figure~\ref{fig:airbnb-demo}, Note C)}. The annotations are saved in
the browser and associated with the backend ID of the listing, so they
will appear in future browser sessions that display the same listing.

Wildcard also includes a formula language that enables more
sophisticated customizations. When traveling without a car, it's useful
to evaluate potential places to stay based on how walkable the
surroundings are. Using a formula, the user can integrate Airbnb with
Walkscore, an API that rates the walkability of any location on a 1-100
scale. When the user calls the \texttt{walkscore} formula with the
listing's latitude and longitude as arguments, it returns the walk score
for that location and shows it as the cell value. Because the cell's
contents are injected into the page, the score also appears in the UI{
(Figure~\ref{fig:airbnb-demo}, Note D)}.

\hypertarget{snoozing-todos}{%
\subsection{Snoozing todos}\label{snoozing-todos}}

\begin{figure}
\hypertarget{fig:todomvc-demo}{%
\centering
\includegraphics{media/todomvc-demo-300dpi.png}
\caption{Using Wildcard to add a ``snooze'' feature to the TodoMVC todo
list app}\label{fig:todomvc-demo}
}
\end{figure}

In addition to fetching data from other sources, Wildcard formulas can
also perform computations. In this example, the user would like to
augment the TodoMVC todo list app with a ``snooze'' feature, which will
temporarily hide a todo from the list until a certain date.{
Figure~\ref{fig:todomvc-demo} shows an overview of this customization.}

The user opens the table view, which shows the text and completed status
of each todo. They start the customization by adding a new column to
store the snooze date for each todo{ (Figure~\ref{fig:todomvc-demo},
Note A)}.

The next step is to hide snoozed todos. The user creates a
\texttt{snoozed?} column, which uses a formula to compute whether a todo
is snoozed---i.e., whether it has a snooze date in the future{
(Figure~\ref{fig:todomvc-demo}, Note B)}. Then, they simply filter the
table to hide the snoozed todos{ (Figure~\ref{fig:todomvc-demo}, Note
C)}.

Because the built-in \texttt{NOW()} function always returns the current
datetime, snoozed todos will automatically appear once their snooze date
arrives.

Because this implementation of snoozing was built on the spreadsheet
abstraction, it is completely decoupled from this particular todo list
app. We envision that users could share these types of customizations as
generic browser extensions, which could be applied to any site supported
by Wildcard with no additional effort.

\hypertarget{adding-a-custom-datepicker}{%
\subsection{Adding a custom
datepicker}\label{adding-a-custom-datepicker}}

\begin{figure}
\hypertarget{fig:expedia-demo}{%
\centering
\includegraphics{media/expedia-demo-300dpi.png}
\caption{Using Wildcard to augment the Expedia page for booking a
flight}\label{fig:expedia-demo}
}
\end{figure}

It might seem that Wildcard is only useful on websites that display
lists of tabular data, but the table metaphor is flexible enough to
represent many types of data. For example, a flight search form on
Expedia can be represented as a single row, with a column corresponding
to each input{ (Figure~\ref{fig:expedia-demo}, Note A)}.

In some of the previous examples, the table cells were read-only
(because users can't, for example, change the name or price of an Airbnb
listing). In this case, the cells are writable, which means that changes
in the table are reflected in the form inputs. This becomes especially
useful when combined with GUI widgets that can edit the value of a table
cell.

Filling in dates for a flight search often requires a cumbersome
workflow: open up a separate calendar app, find the dates for the trip,
and then carefully copy them into the form. In Wildcard, the user can
avoid this by using a datepicker widget that shows the user's personal
calendar events{ (Figure~\ref{fig:expedia-demo}, Note B)}. The user can
directly click on the correct date, and it gets inserted into both the
spreadsheet and the original form.

In this section we've presented just a few use cases for
spreadsheet-driven customization, to suggest some possibilities of the
paradigm. We think the spreadsheet model is flexible enough to support a
wide range of other useful modifications while remaining familiar and
easy to use.

\hypertarget{sec:implementation}{%
\section{System Implementation}\label{sec:implementation}}

Wildcard is written in Typescript. It is currently injected into pages
using the \href{https://www.tampermonkey.net/}{Tampermonkey} userscript
manager, but in the future we plan to deploy it as a standalone browser
extension to make it easier to install.

In order to promote extensibility, Wildcard is implemented as a small
core program along with several types of plugins: site adapters,
formulas, and cell editors. The core contains functionality for
displaying the data table and handling user interactions, and is built
on the \href{https://handsontable.com/}{Handsontable} Javascript
library.

\begin{figure}
\hypertarget{fig:architecture}{%
\centering
\includegraphics{media/architecture-300dpi.png}
\caption{The architecture of the Wildcard
prototype}\label{fig:architecture}
}
\end{figure}

Site adapters are a key part of Wildcard, since they specify the
bidirectional connection between the web page and its structured data
representation. Wildcard represents data in a relational table with
named and typed columns, and provides an interface for concisely
expressing how the DOM should be mapped to this structure. For example,
here is a code snippet for extracting the name of an Airbnb listing.

\begin{Shaded}
\begin{Highlighting}[]
\OperatorTok{\{}
  \CommentTok{// Field metadata:}
\NormalTok{  fieldName}\OperatorTok{:} \StringTok{"name"}\OperatorTok{,}
\NormalTok{  type}\OperatorTok{:} \StringTok{"text"}\OperatorTok{,}
\NormalTok{  readOnly}\OperatorTok{:} \KeywordTok{true}\OperatorTok{,}

  \CommentTok{// Function to extract DOM element:}
\NormalTok{  el}\OperatorTok{:}\NormalTok{ (row) }\KeywordTok{=>} \VariableTok{row}\OperatorTok{.}\FunctionTok{querySelector}\NormalTok{(}\StringTok{".\_1ebt2xej"}\NormalTok{)}\OperatorTok{,}
\OperatorTok{\}}
\end{Highlighting}
\end{Shaded}

Sometimes, more advanced scraping techniques are necessary to extract
data from the application. For example, we have prototyped a mechanism
for site adapters to observe AJAX requests made by the browser and
extract data directly from JSON responses. This mechanism was used to
implement the Airbnb Walkscore example, since latitude and longitude
aren't shown in the Airbnb UI, but they are available in AJAX responses.
This technique seems promising because AJAX responses already contain
data in a structured form, and web applications are increasingly loading
data using AJAX. Another technique we might consider is enabling site
adapters to scrape data across multiple pages for paginated lists of
results (as explored in \autocite{huynh2006}).

Because Wildcard requires a live bidirectional connection between the UI
and the structured data, there are some additional challenges beyond
those typically associated with web scraping.

First, the site adapter needs to support sending updates from the table
to the original page. We have made this fairly straightforward, because
most DOM manipulation is not performed directly by the site adapter.
Instead, Wildcard automatically mutates the DOM to reflect the
spreadsheet state, using the same specification that was used to extract
the data. The only exception to this is row actions (like favoriting an
Airbnb listing), which are implemented as Javascript functions that can
perform arbitrary behaviors like simulating clicks on buttons or
mutating the DOM.

Another challenge is triggering updates to the spreadsheet data in
response to UI changes that happen after initial page load. Site
adapters are responsible for recognizing these changes by observing the
DOM. So far, we have been able to use event listeners and the
MutationObserver API to successfully observe changes, but it may prove
challenging to observe changes on some sites only through the DOM.

\hypertarget{sec:design-principles}{%
\section{Design Principles}\label{sec:design-principles}}

The idea of spreadsheet-driven customization is guided by three design
principles, inspired by prior work and our own experimentation. We think
these principles might also broadly inform the design of tools for end
user software customization.

\hypertarget{expose-a-universal-data-structure}{%
\subsection{Expose a universal data
structure}\label{expose-a-universal-data-structure}}

Today, most personal computing consists of using applications, which
bundle together behavior and data to provide some set of functionality.
While there are some limited points of interoperability, applications
generally are designed to operate independently of one another.

Computing does not need to be organized this way. For example, UNIX
offers a compelling alternative: many small single-purpose programs, all
of which manipulate a universal format of text streams. Users get high
leverage from mastering a text editor and other text manipulation tools,
since they can be applied to a huge variety of tasks. A user's preferred
text editor can even serve as an interactive input mechanism in shell
programs, e.g.~for editing git commit messages.

Spreadsheet-driven customization aims to bring some of this UNIX ethos
to the world of isolated Web applications by creating a consistent data
structure to represent the data inside many applications. In UNIX, the
universal format is a text stream; in Wildcard, it is a relational
table. Because Wildcard maps the data from all applications to the table
format, users can master the tools provided by Wildcard and apply them
to customize many different applications.

This idea relates to Beaudouin-Lafon and Mackay's notion of
\emph{polymorphic interface instruments} \autocite{beaudouin-lafon2000},
which are UI elements that can be used in different contexts (for
example, a color picker that can be used in many drawing applications).
It also relates to ideas of literacy in a medium. DiSessa notes that
textual literacy depends on the fact that writing can be adapted to many
different genres \autocite{disessa2000}: if people needed to relearn
reading and writing from scratch when switching from essays to emails,
the medium would lose its potency. Generic tools are especially
important for software customization, because a common barrier to
customizing software is not having enough time
\autocite{mackay1991}---it's more likely that people will customize
software frequently if they can reuse the same tools across many
applications.

This design principle leads to several challenges. First, any universal
abstraction has its limits, and may not naturally express the data in
every application. We plan to explore the limits of the table
abstraction further by trying to build adapters for more sites with
varied data formats. We expect that many types of data will fit easily
into tables: lists of search results, news articles, and messages can
all naturally be seen as relations. Documents (e.g.~Google Docs) or
graphs (e.g.~social network friend graphs) may prove more challenging to
map to the table abstraction.

\hypertarget{low-floor-high-ceiling}{%
\subsection{Low floor, high ceiling}\label{low-floor-high-ceiling}}

Seymour Papert advocated for programming systems to have a ``low
floor,'' making it easy for novices to get started, and a ``high
ceiling,'' providing a large range of possibilities for more
sophisticated users \autocite{resnick2016}. Our goal is for
spreadsheet-driven customization to meet both of these criteria.

One of the most interesting properties of spreadsheets is that users
familiar with only a tiny sliver of their functionality (e.g., storing
tables of numbers and computing simple sums) can still use them in
valuable ways. This supports the user's natural motivation to continue
using the tool, and to eventually learn its more powerful features if
needed \autocite{nardi1991}. In contrast, many traditional programming
systems require an enormous upfront time investment before someone is
able to write a program that helps them achieve a useful task.

As part of ensuring a low floor, we have focused on including features
that have immediate value for novices. For example, a user can sort a
table with a single click, or simply type in some annotations. We would
expect many Wildcard users to start by using these simpler features
before moving on to more sophisticated features like formulas.

Another aspect of providing a low floor is providing an ``in-place
toolchain'' \autocite{2019}: minimizing the effort of moving from using
to customizing by making customization tools available in the same
environment where the user is already using the software. This quality
is distinct from the level of technical skill needed to use the tool.
For example, setting up a workflow in an end user programming system
like \href{https://ifttt.com/}{IFTTT} does not require much programming
skill, but it does require leaving the user's normal software and
entering a separate environment; conversely, running a Javascript
snippet in the browser console requires programming skills, but can be
done immediately in the flow of using a website.

\begin{longtable}[]{@{}llc@{}}
\toprule
\endhead
& \emph{In-place} & \emph{Not in-place}\tabularnewline
\emph{End user friendly} & \textbf{Wildcard} & IFTTT\tabularnewline
\emph{Requires programming} & browser JS console & using Web APIs in
Python\tabularnewline
\bottomrule
\end{longtable}

Wildcard provides an in-place toolchain because the spreadsheet can be
instantly opened in the browser window while using any supported
website. Once the user starts editing, Wildcard also provides live
feedback, so that even if a user isn't yet totally familiar with
Wildcard, they can learn to use the system through experimentation.

Since we have only built a few site adapters and demos so far, it is
still too early to tell how high the ceiling is for the customizations
that can be achieved with Wildcard. But we think that with enough
built-in formulas (both standard spreadsheet formulas for computation,
and formulas for fetching data from other sources), the language could
support a wide variety of customizations. We plan to explore this aspect
further by trying to solve real problems and observing where limitations
emerge in practice (discussed more in Section~\ref{sec:conclusion}).

\hypertarget{design-for-an-ecosystem-of-users}{%
\subsection{Design for an ecosystem of
users}\label{design-for-an-ecosystem-of-users}}

Real-world spreadsheet usage is highly collaborative. Many users only
perform simple changes, while their coworkers help with writing complex
formulas or programming macros \autocite{nardi1990}. Inspired by this
collaborative dynamic, we aim for spreadsheet-driven customization to
bring together the abilities of different users.

The main way we do this is by separating website customization into two
separate stages: structured data extraction, performed by programmers
who code site adapters in Javascript, and then customization using the
resulting spreadsheet, which is available to all end users. This
architecture frees end users from needing to think about data
extraction, and enables a community of end users to reuse the efforts of
programmers building site adapters.

The group of users building adapters does not necessarily need to be
limited only to programmers. In the future, we plan to explore enabling
end users to also create site adapters, drawing on related work in this
area \autocite{chasins2018,huynh2006}. But even then, we still envision
a separation between highly motivated, tech-savvy end users building
adapters, and more casual end users just using the spreadsheet view.

The first party developers of the original software can also play a role
in enabling customization. Although spreadsheet-driven customization
does not depend on cooperation from first party website developers,
their participation in exposing structured data would eliminate the need
for third party site adapters. The first parties could themselves
benefit from such a system; providing Wildcard support---a fairly
low-effort undertaking for a developer with direct access to the
structured data---would allow users to build extensions to fulfill some
of their own feature requests. There is also precedent for first parties
implementing an official client extension API: for several years, Google
maintained an official extension API in Gmail for Greasemonkey scripts
to use.

Google no longer maintains its own API, but third parties have continued
to maintain successful replacements---Gmail.js \autocite{talwar2019} is
an open source wrapper API with over 70 contributors and hundreds of
commits. This library demonstrates another benefit of designing for an
ecosystem: it's easier for many programmers to collectively maintain a
generic site adapter that can support many extensions, rather than each
programmer creating custom scraping logic for their own single-purpose
extension.

\hypertarget{sec:related-work}{%
\section{Related Work}\label{sec:related-work}}

Spreadsheet-driven customization relates to existing work in four areas:
malleable software, web customization, spreadsheet-driven applications,
and web scraping.

\hypertarget{malleable-software}{%
\subsection{Malleable software}\label{malleable-software}}

In the broadest sense, Wildcard is inspired by systems aiming to make
software into a dynamic medium where end users frequently create and
modify software to meet their own needs, rather than only consuming
applications built by programmers. These systems include Smalltalk
\autocite{kay1977}, Hypercard \autocite{hypercard2019}, Boxer
\autocite{disessa1986}, Webstrates \autocite{klokmose2015}, and
Dynamicland \autocite{victor}. In fact, the name Wildcard comes from the
internal pre-release name for Hypercard, a project which doubly inspired
our work by promoting both software modification by end users and the
ideas behind the Web.

Although Wildcard shares broad goals with these projects, it employs a
different solution strategy. These other systems generally require
building software from scratch in a new environment. On the other hand,
Wildcard aims to maximize the malleability of software built with
existing tools.

With substantial future work, we think Wildcard could become more
similar to these other projects, growing from a platform for tweaking
existing software into a platform for building new software from
scratch. This would likely end up resembling existing tools for building
spreadsheet-driven applications (discussed more below), but with an
additional focus on customization by end users of the software.

\hypertarget{web-customization}{%
\subsection{Web customization}\label{web-customization}}

Wildcard's goals are closely shared with other systems that provide
interfaces in the browser for end users to customize websites.

\hypertarget{structured-augmentation}{%
\subsubsection{Structured augmentation}\label{structured-augmentation}}

Wildcard's solution approach is most similar to other tools that
identify structured data in a web page and then use that structure to
support end user customization of the page.

Sifter \autocite{huynh2006} enables users to sort and filter lists of
data on web pages, which resembles Wildcard's sorting functionality. The
underlying mechanism is similar, since Sifter extracts structured data
from the page to enable its user-facing functionality. However, the
systems also have significant differences:

\begin{itemize}
\tightlist
\item
  Wildcard hides data extraction from end users by having programmers
  develop site adapters, whereas Sifter uses a combination of automated
  heuristics and interactive user feedback to involve end users in
  extracting data. User studies of Sifter indicated that users were
  surprised by the need to participate in the data augmentation process,
  which influenced our decision to hide this process from the user. We
  suspect Wildcard's workflow results in a simpler end user experience,
  but at the cost of only working with a smaller subset of supported
  websites.
\item
  Wildcard supports a broad set of customizations. Sifter only supports
  sorting and filtering.
\item
  Wildcard shows the structured data table directly to the user. Sifter
  only shows sorting controls, and does not reveal the underlying data
  table.
\end{itemize}

Thresher \autocite{hogue2005} enables users to create wrappers which map
unstructured website content to Semantic Web content. Like Wildcard and
Sifter, Thresher augments the page: once semantic content has been
identified, it creates context menus in the original website which allow
users to take actions based on that content. Wildcard and Thresher focus
on complementary parts of the customization process. Thresher aims to
enable end users to create content wrappers, but the actions available
on the structured data are determined in advance. Conversely, Wildcard
delegates wrapper creation to programmers, but gives end users more
flexibility to use the structured data in an open-ended way.

\hypertarget{sloppy-augmentation}{%
\subsubsection{Sloppy augmentation}\label{sloppy-augmentation}}

``Sloppy programming'' \autocite{little2010} tools like Chickenfoot
\autocite{bolin2005} and Coscripter \autocite{leshed2008} enable users
to create web automation scripts without directly interacting with the
DOM. The scripts can perform actions like filling in text boxes and
clicking on buttons. Users express the desired page elements in natural,
informal terms (e.g.~writing ``the username box'' to represent the
textbox closest to the label ``username''), and then the system uses a
set of heuristics to determine which elements most likely match the
user's intent. This approach allows for expressing a wide variety of
commands with minimal training, but it also has downsides
\autocite{little2010}:

\begin{itemize}
\tightlist
\item
  \emph{Reliability}: It can be difficult to know whether a command will
  consistently work over time. Changes to the website or to the system's
  heuristics can cause unexpected changes in behavior.
\item
  \emph{Discoverability}: it can be difficult for users to explore the
  space of possible commands.
\end{itemize}

Wildcard offers a sharp contrast to sloppy programming, instead choosing
to expose a high degree of structure through the spreadsheet table.
Wildcard offers more consistency; for example, clicking a sort header
will always work correctly as long as the site adapter is maintained.
Wildcard also offers clearer affordances for what types of actions are
possible. On the other hand, Wildcard's explicit site adapter approach
means that fewer websites can be customized, and also that users can't
perform customizations if the relevant data is not exposed in the
spreadsheet.

Another difference between Wildcard and these tools is that there is no
way for users to express imperative workflows with sequences of actions
in Wildcard. Chickenfoot and Coscripter have shown these types of
workflows to be useful in practice so it might be worth considering how
to incorporate them, but it's not obvious how such workflows could fit
into Wildcard. Spreadsheets have a fundamentally different computation
model, and site adapters created by programmers cannot easily account
for every possible action a user might want to perform in a page.

\hypertarget{spreadsheet-driven-applications}{%
\subsection{Spreadsheet-driven
applications}\label{spreadsheet-driven-applications}}

Many researchers and companies have explored the idea of
\emph{spreadsheet-driven applications}: using spreadsheets as a backing
data store and computation layer for interactive web applications,
enabling end users to create such applications more easily. Research
projects like Object Spreadsheets \autocite{mccutchen2016}, Quilt
\autocite{benson2014}, Gneiss \autocite{chang2014}, and Marmite
\autocite{wong2007}, as well as commercial tools like Airtable
\autocite{zotero-79} and Glide \autocite{zotero-81} allow users to view
data in a spreadsheet table, compute over the data using formulas, and
then connect the table to a GUI. Because many users are already familiar
with spreadsheets, this way of creating applications tends to be much
easier than traditional software methods; for example, in a user study
of Quilt, many users were able to create applications in under 10
minutes, even if they expected it would take them many hours.

Wildcard builds on this idea, but applies it to modifying existing
applications, rather than building new applications from scratch. For
many people, we suspect that tweaking existing applications provides
more motivation as a starting point for programming than creating a new
application from scratch.

An important design decision for tools in this space is how far to
deviate from traditional spreadsheets like Microsoft Excel or Google
Sheets. Quilt and Glide use existing spreadsheet software as a backend,
providing maximum familiarity for users, and even compatibility with
existing spreadsheets. Gneiss has its own spreadsheet implementation
with additional features useful for building GUIs. Marmite provides a
live data view that resembles a spreadsheet, but programming is actually
done using a separate data flow pane rather than spreadsheet formulas.
Marmite's approach led to some confusion in a user study, because users
expected behavior more similar to spreadsheets \autocite{wong2007}.
Airtable deviates the furthest: although the user interface resembles a
spreadsheet, the underlying structure is a relational database with
typed columns. Wildcard's table is most similar to Airtable; the
structure of a relational table is most appropriate for most data in
websites, and we have not yet found a need for arbitrary untyped cells.

\hypertarget{web-scraping-data-extraction}{%
\subsection{Web scraping / data
extraction}\label{web-scraping-data-extraction}}

Web scraping tools focus on extracting structured data out of
unstructured web pages. Web scraping is closely related to the
implementation of Wildcard, but has different end goals: web scraping
generally extracts static data for processing in another environment,
whereas Wildcard customizes the application's UI by maintaining a
bidirectional connection between the extracted data and the page.

Web scraping tools differ in how much structure they attempt to map onto
the data. Some tools like Rousillon \autocite{chasins2018} extract data
in a minimally structured relational format; other tools like Piggy Bank
\autocite{huynh2005} more ambitiously map the data to a rich semantic
schema. In Wildcard, we chose to avoid semantic schemas, in order to
minimize the work associated with creating a site adapter.

In the future, we might try to integrate existing web scraping tools, to
help create more reliable site adapters for Wildcard with less work, and
to open up adapter creation to end users. Although Wildcard has
additional requirements beyond traditional web scraping as discussed in
Section~\ref{sec:implementation}, there is still enough overlap that
existing tools might prove helpful.

\hypertarget{sec:conclusion}{%
\section{Conclusion and Future Work}\label{sec:conclusion}}

In this paper, we have presented \emph{spreadsheet-driven
customization}, a technique that enables end users to customize software
by augmenting an application's UI with a spreadsheet. We still have many
open questions which we hope to answer through targeted development and
usage of Wildcard.{\footnote{Up to date information about Wildcard is
  available on the project website
  (\url{https://geoffreylitt.com/wildcard}), which includes a signup for
  receiving updates and notifications about a public release. We also
  welcome hearing from readers who might be interested in being private
  beta testers or who have feedback on the project.}}

The most important question is: what are the limits of this
computational model? What types of useful customizations can it support
or not support? While initial demos suggest a variety of use cases, we
plan to develop more site adapters and demos to explore this question
further. We will start by privately testing the system with our own
needs and then eventually deploy the tool publicly once it has a stable
API and can support a critical mass of sites and use cases. We also plan
to run usability studies to evaluate and improve the design of the tool.

We suspect that some areas of the current model may prove overly
simplistic. For example, Wildcard's data model currently shows a single
table at a time, without any notion of relationships between tables. A
richer data model with foreign keys might help support certain use
cases. For designing a spreadsheet interface on top of a richer
relational model, we could learn from other systems with this design
\autocite{mccutchen2016,bakke2016}.

Another question is how easily site adapters can be created and
maintained for real websites, which often include complex markup and
change frequently. We plan to explore this question by creating adapters
for sites with different data structures and in different domains, and
perhaps running user tests with programmers. Possible future
improvements we've considered include developing automated heuristics to
assist with the adapter creation process and developing new abstractions
that make it easier for programmers to efficiently create robust
adapters.

Ultimately, we hope that spreadsheet-driven customization helps the Web
reach its full potential as a dynamic medium that users can mold to
their own needs.

\acks
Thanks to Tarfah Alrashed, Glen Chiacchieri, David Karger, Steve Krouse, Rob Miller, Santiago Perez De Rosso, Arvind Satyanarayan, Daniel Windham, and Maggie Yellen for providing valuable feedback on this work.

\printbibliography

\end{document}

% Local Variables:
% TeX-engine: luatex
% End:

### 2021-02-02 compile-html.sh

@@ -1,0 +1,15 @@
+set -e
+
+ pandoc \
+  --filter pandoc-crossref \
+  --citeproc \
+  --metadata=format:html \
+  -s \
+  --number-sections \
+  -o paper.html \
+  --css basic.css \
+  --toc \
+  --toc-depth=1 \
+  --variable=toc-title:"Contents" \
+  --template=templates/pandoc-template-html.html \
+  paper.md

### 2021-02-02 watch.sh

@@ -1,0 +1,10 @@
+set -e
+
+# kill any existing servers
+ps aux | grep node | grep browser-sync | awk '{ print $2}' | xargs kill
+
+ls *.md | entr ./compile-html.sh &
+browser-sync start --server --files paper.html --no-notify --no-open --port 9000 &
+
+open "http://localhost:9000/paper.html"
+

### 2021-02-11 compile-latex.sh
Updated demo videos

@@ -1,11 +1,5 @@
 set -e
 
-convert media/airbnb-demo.png -density 300 -units pixelsperinch media/airbnb-demo-300dpi.png
-convert media/expedia-demo.png -density 300 -units pixelsperinch media/expedia-demo-300dpi.png
-convert media/todomvc-demo.png -density 300 -units pixelsperinch media/todomvc-demo-300dpi.png
-convert media/overview.png -density 300 -units pixelsperinch media/overview-300dpi.png
-convert media/architecture.png -density 300 -units pixelsperinch media/architecture-300dpi.png
-
 pandoc \
   --filter conditional-render \
   --filter pandoc-crossref \

### 2021-02-13 paper.tex
initial latex compile

@@
-% -*- coding: utf-8; -*-
-% vim: set fileencoding=utf-8 :
-\documentclass[english]{programming}
-%% First parameter: the language is 'english'.
-%% Second parameter: use 'submission' for initial submission, remove it for camera-ready (see 5.1)
-
-\usepackage{longtable,booktabs}
-% Correct order of tables after \paragraph or \subparagraph
-\usepackage{etoolbox}
-\makeatletter
-\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
-\makeatother
-% Allow footnotes in longtable head/foot
-\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
-\makesavenoteenv{longtable}
+%%
+%% This is file `sample-sigconf.tex',
+%% generated with the docstrip utility.
+%%
+%% The original source files were:
+%%
+%% samples.dtx  (with options: `sigconf')
+%%
+%% IMPORTANT NOTICE:
+%%
+%% For the copyright see the source file.
+%%
+%% Any modified versions of this file must be renamed
+%% with new filenames distinct from sample-sigconf.tex.
+%%
+%% For distribution of the original source see the terms
+%% for copying and modification in the file samples.dtx.
+%%
+%% This generated file may be distributed as long as the
+%% original source files, as listed above, are part of the
+%% same distribution. (The sources need not necessarily be
+%% in the same archive or directory.)
+%%
+%% The first command in your LaTeX source must be the \documentclass command.
+\documentclass[sigconf,10pt]{acmart}
 
@@
 
-\usepackage[backend=biber]{biblatex}
-\addbibresource{references2.bib}
-
 \providecommand{\tightlist}{%
@@
 
-%%% The following is specific to <Programming'20> Companion-CCS and the paper
-%%% 'Wildcard: Spreadsheet-Driven Customization of Web Applications'
-%%% by Geoffrey Litt and Daniel Jackson.
-%%%
-%%% (Author note: Commented out this info, doesn't seem to fit with this template)
-% \setcopyright{acmlicensed}
-% \acmPrice{}
-% \acmDOI{10.1145/3397537.3397541}
-% \acmYear{2020}
-% \copyrightyear{2020}
-% \acmSubmissionID{prog20ccs-id3-p}
-% \acmISBN{978-1-4503-7507-8/20/03}
-% \acmConference[<Programming'20> Companion]{Companion Proceedings of the 4th International Conference on the Art, Science, and Engineering of Programming}{March 23--26, 2020}{Porto, Portugal}
-% \acmBooktitle{Companion Proceedings of the 4th International Conference on the Art, Science, and Engineering of Programming (<Programming'20> Companion), March 23--26, 2020, Porto, Portugal}
+%%
+%% \BibTeX command to typeset BibTeX logo in the docs
+\AtBeginDocument{%
+  \providecommand\BibTeX{{%
+    \normalfont B\kern-0.5em{\scshape i\kern-0.25em b}\kern-0.8em\TeX}}}
 
+%% Rights management information.  This information is sent to you
+%% when you complete the rights form.  These commands have SAMPLE
+%% values in them; it is your responsibility as an author to replace
+%% the commands and values with those provided to you when you
+%% complete the rights form.
+
+%%
+%% Submission ID.
+%% Use this when submitting an article to a sponsored event. You'll
+%% receive a unique submission ID from the organizers
+%% of the event, and this ID should be used as the parameter to this command.
+%%\acmSubmissionID{123-A56-BU3}
+
+%%
+%% The majority of ACM publications use numbered citations and
+%% references.  The command \citestyle{authoryear} switches to the
+%% "author year" style.
+%%
+%% If you are preparing content for an event
+%% sponsored by ACM SIGGRAPH, you must use the "author year" style of
+%% citations and references.
+%% Uncommenting
+%% the next command will enable that style.
+%%\citestyle{acmauthoryear}
+
+%%
+%% end of the preamble, start of the body of the document source.
 \begin{document}
 
-\title{Wildcard: Spreadsheet-Driven Customization of Web Applications}
-\subtitle{}% optional
+%%
+%% The "title" command has an optional parameter,
+%% allowing the author to define a "short title" to be used in page headers.
+\title{End-user Web Scraping For Customization}
+
+%%
+%% The "author" command and its associated commands are used to define
+%% the authors and their affiliations.
+%% Of note is the shared affiliation of the first two authors, and the
+%% "authornote" and "authornotemark" commands
+%% used to denote shared contribution to the research.
+
+\author{Kapaya Katongo}
+\affiliation{%
+  \institution{MIT CSAIL}
+  \city{Cambridge, MA}
+  \country{USA}
+}
+\email{kkatongo@mit.edu}
 
 \author{Geoffrey Litt}
-\authorinfo{is a PhD student at MIT in the Software Design Group.
-His research focuses on programming languages and environments, particularly tools for end user programming and live programming.
-Contact him at \email{glitt@mit.edu}.}
+\affiliation{%
+  \institution{MIT CSAIL}
+  \city{Cambridge, MA}
+  \country{USA}
+}
+\email{glitt@mit.edu}
+
 \author{Daniel Jackson}
-\authorinfo{is Professor in the Department of Electrical Engineering and Computer Science at MIT,  a MacVicar teaching fellow, and Associate Director of the Computer Science and Artificial Intelligence Laboratory.
-He leads the Software Design Group.
-Contact him at \email{dnj@csail.mit.edu}.}
-\affiliation{Massachusetts Institute of Technology}
+\affiliation{%
+  \institution{MIT CSAIL}
+  \city{Cambridge, MA}
+  \country{USA}
+}
+\email{dnj@csail.mit.edu}
 
-\keywords{end-user programming, software customization, web browser extensions} % please provide 1--5 keywords
+%%
+%% By default, the full list of authors will be used in the page
+%% headers. Often, this list is too long, and will overlap
+%% other information printed in the page headers. This command allows
+%% the author to define a more concise list
+%% of authors' names for this purpose.
+% \renewcommand{\shortauthors}{Trovato and Tobin, et al.}
 
-%%%%%%%%%%%%%%%%%%
-%% These data MUST be filled for your submission. (see 5.3)
-\paperdetails{
-  %% perspective options are: art, sciencetheoretical, scienceempirical, engineering.
-  %% Choose exactly the one that best describes this work. (see 2.1)
-  perspective=art,
-  %% State one or more areas, separated by a comma. (see 2.2)
-  %% Please see list of areas in http://programming-journal.org/cfp/
-  %% The list is open-ended, so use other areas if yours is/are not listed.
-  area={Programming environments, Visual and live programming},
-  %% You may choose the license for your paper (see 3.)
-  %% License options include: cc-by (default), cc-by-nc
-  % license=cc-by-sa,
-}
-%%%%%%%%%%%%%%%%%%
+%%
+%% The abstract is a short summary of the work to be presented in the
+%% article.
+\begin{abstract}
+  Websites are malleable: users can install browser extensions and run
+  arbitrary Javascript in the developer console to change them. However,
+  this malleability is only accessible to programmers with knowledge of
+  HTML, CSS, Javascript and the DOM. To broaden access to customization,
+  our prior work developed an approach that empowers end-users to
+  customize websites without traditional programming via a browser
+  extension called Wildcard. Wildcard's customizations are powered by
+  web scraping adapters which are currently written in Javascript by
+  programmers. This means that end-users can only customize a website if
+  a programmer has written an adapter for it. Furthermore, end-users do
+  not have the ability to extend adapters in order to perform new
+  customizations or repair adapters to fix broken customizations.
 
-%%%%%%%%%%%%%%%%%%
-%% These data are provided by the editors. May be left out on submission.
-%\paperdetails{
-%  submitted=2016-08-10,
-%  published=2016-10-11,
-%  year=2016,
-%  volume=1,
-%  issue=1,
-%  articlenumber=1,
-%}
-%%%%%%%%%%%%%%%%%%
+  In this paper, we extend Wildcard with a new system for \emph{end-user
+  web scraping for customization} which enables end-users to create,
+  extend and repair adapters by demonstration. We describe three design
+  principles that guided our system's development and are applicable to
+  other end-user web scraping and customization systems: (a) users
+  should be able to scrape data and use it in a single, unified
+  environment, (b) users should be able to extend and repair the
+  programs that scrape data via demonstration and (c) users should
+  receive live feedback during their demonstrations.
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Please go to https://dl.acm.org/ccs/ccs.cfm and generate your Classification
-% System [view CCS TeX Code] stanz and copy _all of it_ to this place.
+  We have successfully used our system to create, extend and repair
+  adapters by demonstration on a variety of websites. We provide example
+  usage scenarios that showcase each of our design principles.
+\end{abstract}
+
+%%
+%% The code below is generated by the tool at http://dl.acm.org/ccs.cfm.
+%% Please copy and paste the code instead of the example below.
+%%
 %% From HERE
@@
 % To HERE
-%%%%%%%%%%%%%%%%%%%%%%%
 
+%%
+%% Keywords. The author(s) should pick words that accurately describe
+%% the work being presented. Separate the keywords with commas.
+\keywords{end-user programming, software customization, web browser extensions}
+
+%% A "teaser" image appears between the author and affiliation
+%% information and the body of the document, and typically spans the
+%% page.
+%\begin{teaserfigure}
+%  \includegraphics[width=\textwidth]{sampleteaser}
+%  \caption{Seattle Mariners at Spring Training, 2010.}
+%  \Description{Enjoying the baseball game from the third-base
+%  seats. Ichiro Suzuki preparing to bat.}
+%  \label{fig:teaser}
+%\end{teaserfigure}
+
+%%
+%% This command processes the author and affiliation and title
+%% information and builds the first part of the formatted document.
 \maketitle
-
-% Please always include the abstract.
-% The abstract MUST be written according to the directives stated in
-% http://programming-journal.org/submission/
-% Failure to adhere to the abstract directives may result in the paper
-% being returned to the authors.
-\begin{abstract}
-Many Web applications do not meet the precise needs of their users.
-Browser extensions offer a way to customize web applications, but most
-people do not have the programming skills to implement their own
-extensions.
-
-In this paper, we present \emph{spreadsheet-driven customization}, a
-technique that enables end users to customize software without doing any
-traditional programming. The idea is to augment an application's UI with
-a spreadsheet that is synchronized with the application's data. When the
-user manipulates the spreadsheet, the underlying data is modified and
-the changes are propagated to the UI, and vice versa.
-
-We have implemented this technique in a prototype browser extension
-called Wildcard. Through concrete examples, we demonstrate that Wildcard
-can support useful customizations---ranging from sorting lists of search
-results to showing related data from web APIs---on top of existing
-websites. We also present the design principles underlying our
-prototype.
-
-Customization can lead to dramatically better experiences with software.
-We think that spreadsheet-driven customization offers a promising new
-approach to unlocking this benefit for all users, not just programmers.
-
-This paper is best viewed in the online version (\url{https://www.geoffreylitt.com/wildcard/salon2020}), which includes videos demonstrating the interface.
-\end{abstract}
 
@@
 
-Web applications often don't meet the precise needs of their users.
-Sometimes there is a browser extension available to patch an issue, and
-if the user is a programmer they might be able to fix it themselves. But
-for most people, the only recourse is to complain to the developers, or,
-more likely, to simply give up. Back in 1977, in \emph{Personal Dynamic
-Media} \autocite{kay1977}, Alan Kay envisioned personal computing as a
-medium that let a user ``mold and channel its power to his own needs,''
-but today, software behaves more like concrete than clay.
+Many websites on the internet do not meet the exact needs of all of
+their users. End-user web customization systems like Chickenfoot
+\citep{bolin2005}, Thresher \citep{hogue2005}, Sifter \citep{huynh2006}
+and Vegemite {[}lin2009{]} help users tweak and adapt websites to fit
+their unique requirements, ranging from reorganizing or annotating
+content on the website to automating common tasks. In our prior work, we
+presented Wildcard \citep{litt2020a}, a customization system which
+enables end-users to customize websites through direct manipulation. It
+does this by augmenting websites with a table view that shows their
+underlying structured data. The table is bidirectionally synchronized
+with the original website, so end-users can easily customize the website
+by interacting with the table, including sorting and filtering data,
+adding annotations, and running computations in a spreadsheet formula
+language.
 
-In this paper, we present \emph{spreadsheet-driven customization}, a
-technique that enables end users to customize software without doing any
-traditional programming. The idea is to augment an application's UI with
-a spreadsheet that is synchronized with the application's data. When the
-user manipulates the spreadsheet, the underlying data is modified and
-the changes are propagated to the UI, and vice versa.
+Wildcard has a key limitation. In order to enable end-users to customize
+a website, a Javascript programmer first needs to code an adapter that
+specifies how to scrape the website content and set up a bidirectional
+synchronization with Wildcard's table view. Take Alice, an end-user who
+uses Wildcard to customize her experience on Google Scholar as shown
+above. Wildcard's sorting customization gives her the power to sort
+publications by title which the website does not natively allow. She
+thinks this will be useful on Weather.com to sort the ten day forecast
+by the weather descriptions so that she can quickly find all the sunny
+days. Unfortunately, a programmer has not coded an adapter for
+Weather.com so Alice is unable to customize it. Additionally, if the
+adapter for Google Scholar stops functioning when the website changes,
+Alice has no recourse to repair it on her own.
 
-We have implemented this technique in a prototype browser extension
-called Wildcard and used it to build demos which suggest that this
-paradigm can support useful customizations, ranging from sorting lists
-of data to adding whole new features to applications (shown in
-Section~\ref{sec:demos}).
+In this paper, we describe an addition to Wildcard: a system that
+enables end-users to create, extend and repair website adapters by
+demonstration within the browser. Using this scraping system, an
+end-user can perform end-to-end web customizations using Wildcard on
+arbitrary websites, without ever needing to code an adapter. Through a
+series of examples, we show that end-users can utilize our system to
+successfully create Wildcard adapters on a variety of websites via
+demonstration (Section~\ref{sec:demos}). We also describe key aspects of
+our system and how web scraping for customization reveals a constraint
+that simplifies the \emph{wrapper induction} \citep{kushmerick2000} task
+used to generalize user demonstrations
+(Section~\ref{sec:implementation}).
 
-\begin{figure}
-\hypertarget{fig:overview}{%
-\centering
-\includegraphics{media/overview-300dpi.png}
-\caption{An overview of spreadsheet-driven
-customization}\label{fig:overview}
-}
-\end{figure}
-
-Our approach requires extracting structured data from the user
-interfaces of existing applications, but we hide the complexity of data
-extraction from end users. Programmers write \emph{site adapters} which
-use web scraping techniques to extract structured data from existing
-applications and map it to the spreadsheet table. Our prototype suggests
-that it is possible to implement site adapters for real websites;
-Section~\ref{sec:implementation} describes some of the techniques and
-challenges involved.
-
-Spreadsheet-driven customization is based on three design principles,
-described in Section~\ref{sec:design-principles}:
+Our key contribution is a set of three design principles that guided the
+development of our system, which also offer insights that might be
+applied to other end-user web scraping and customization tools
+(Section~\ref{sec:design-principles}):
 
@@
 \item
-  \textbf{Expose a universal structure}: By mapping the data in all
-  applications to the same universal table abstraction, Wildcard enables
-  users to learn a generic customization toolkit that they can apply to
-  any site.
+  \textbf{Unified Environment}: Users should be able to scrape data and
+  interact with the scraped data in a single, unified environment. This
+  minimizes the barrier to fluidly switching back and forth between the
+  two tasks, rather than treating them as entirely independent tasks.
 \item
-  \textbf{Low floor, high ceiling}: Wildcard provides an easy entry
-  point for end users, since small tweaks like sorting data can be
-  performed with a single click. At the same time, it also supports a
-  variety of richer customizations, like adding private annotations to a
-  webpage or joining in related data from a web API.
+  \textbf{Editing By Demonstration}: Users should be able to not only
+  create programs for scraping data by demonstration, but also extend
+  and repair the programs by demonstration. This enables users to build
+  on other user's work, and is especially important in the context of
+  web scraping since programs that scrape data sometimes break as the
+  underlying website changes.
 \item
-  \textbf{Design for an ecosystem of users}: Spreadsheet-driven
-  customization combines the efforts of programmers and end users,
-  rather than putting the full burden on end users. We also envision a
-  role for first party developers to help make their applications more
-  customizable.
+  \textbf{Live Programming}: Users should receive live feedback as they
+  perform demonstrations. The system should indicate how it is
+  generalizing from the user's example and what the resulting data will
+  look like, so that the user can adjust their demonstrations on the fly
+  and quickly arrive at the desired result.
 \end{itemize}
 
-Prior work \autocite{mccutchen2016,benson2014,chang2014} has enabled end
-users to create ``spreadsheet-driven applications'' which use
-spreadsheets as a backing data layer. Spreadsheet-driven
-\emph{customization} applies this idea in a different context:
-customizing existing software, rather than building new software from
-scratch. Our technique does not require that the application actually be
-backed by a spreadsheet; it merely uses the spreadsheet as an interface
-for viewing and modifying the internal state of the application. In
-Section~\ref{sec:related-work}, we describe further how Wildcard relates
-to existing work on spreadsheet-driven apps, as well as work in other
-areas like web customization and web scraping.
-
-The Wildcard extension is currently an early research prototype. We plan
-to continue testing the system with our own use cases to explore how the
-spreadsheet abstraction maps to real websites and customization needs.
-Eventually we plan to release the tool publicly in order to learn from
-real use cases, discover usability challenges, and to test the
-feasibility of building and maintaining site adapters.
-Section~\ref{sec:conclusion} describes open questions we plan to
-continue exploring, as well as our future plans.
+Finally, we share our broader vision for web scraping for customization,
+and some opportunities for future work, including a proposal for how
+Wildcard's spreadsheet-like formula language might augment
+demonstrations to provide end-users with more expressiveness in the web
+scraping process (Section~\ref{sec:conclusion}).
 
 \hypertarget{sec:demos}{%
-\section{Demos}\label{sec:demos}}
+\section{Motivating Examples}\label{sec:demos}}
 
-Here are some examples of using Wildcard to customize websites in useful
-ways.{ These demos are best viewed as videos in the online version of
-this paper (\url{https://www.geoffreylitt.com/wildcard/salon2020}).}
+In this section, we show how end-users can create, extend and repair
+adapters for Wildcard via demonstration.
 
-\begin{figure}
-\hypertarget{fig:airbnb-demo}{%
-\centering
-\includegraphics{media/airbnb-demo-300dpi.png}
-\caption{Using Wildcard to augment the Airbnb search page for booking
-accommodations}\label{fig:airbnb-demo}
-}
-\end{figure}
+\hypertarget{creating-an-adapter}{%
+\subsection{Creating An Adapter}\label{creating-an-adapter}}
 
-\hypertarget{augmenting-search-results}{%
-\subsection{Augmenting search results}\label{augmenting-search-results}}
+Alice, our end-user from Section~\ref{sec:introduction}, wants to
+customize her experience on Weather.com by sorting the ten-day forecast
+based on the description of the weather on each day, allowing her to
+easily view all the sunny days. She starts the adapter creation process
+by clicking a context menu item within the Weather.com page, and hovers
+over a data value she might like to scrape.
 
-In 2012, the travel site Airbnb removed the ability to sort
-accommodation searches by price. Users could still filter by price
-range, but could no longer view the cheapest listings first. Many users
-complained that the change seemed hostile to users. ``It's so
-frustrating! What is the logic behind not having this function?'' said
-one user on the
-\href{https://community.withairbnb.com/t5/Hosting/Sorting-listing-by-price/td-p/559404}{Airbnb
-support forum}. Alas, the feature remains missing to this day.
+The system provides live feedback as Alice hovers, demonstrating the
+\textbf{live programming} principle:
 
-Using Wildcard, the user can fix this omission, while leaving the page's
-design and the rest of its functionality unchanged.{
-Figure~\ref{fig:airbnb-demo} shows an overview of augmenting the Airbnb
-site.} First, the user opens up the Wildcard panel, which shows a table
-corresponding to the search results in the page. As they click around in
-the table, the corresponding row in the page is highlighted to indicate
-the mapping between the views.
+\begin{itemize}
+\tightlist
+\item
+  The selected row of data is annotated in the page with a border, to
+  indicate that she will be demonstrating values from within that row.
+\item
+  The selected column of data is highlighted in the page with a green
+  background, to show how the system has generalized her demonstration
+  across all the rows in the data.
+\item
+  A table view appears at the bottom of the screen, and displays how the
+  values will appear in the data table.
+\end{itemize}
 
-Then, the user clicks on the price column header to sort the spreadsheet
-and the Airbnb UI by price{ (Figure~\ref{fig:airbnb-demo}, Note A)}.
-They also filter to listings with a user rating above 4.5 (another
-feature missing in the original Airbnb UI).
+Alice tries hovering over several other elements in the page, taking
+advantage of the live feedback environment to decide what data would be
+useful. After considering several options, she decides to save the date
+field in the first column of the table, and commits the action by
+clicking.
 
-After manipulating the data, the user closes the table view and
-continues using the website. Because the application's UI usually has a
-nicer visual design than a spreadsheet, Wildcard does not aim to replace
-it---at any time, the user can use either the UI, the spreadsheet, or
-both together.
+Next, she performs a similar process to fill the next column with the
+weather descriptions. After filling both columns, she also tries
+hovering over previously scraped data, and the toolbar at the top of the
+page indicates which column corresponds to the previously scraped data.
+Finally, she ends the adapter creation process and is able to
+immediately sort the forecast by the weather description column, because
+Wildcard provides a \textbf{unified environment} that combines both
+scraping and customizing:
 
-Many websites that show lists of data also offer actions on rows in the
-table, like adding an item to a shopping cart. Wildcard has the ability
-to make these ``row actions'' available in the data table through the
-site adapter. In the Airbnb UI, saving multiple listings to a Favorites
-list requires tediously clicking through them one by one. Using Wildcard
-row actions, the user can select multiple rows and favorite all of them
-with a single click{ (Figure~\ref{fig:airbnb-demo}, Note B)}. Similarly,
-the user can open the detailed pages for many listings at once.
+\hypertarget{extending-an-adapter}{%
+\subsection{Extending An Adapter}\label{extending-an-adapter}}
 
-Next, the user wants to jot down some notes about each listing. To do
-this, they type some notes into an additional column in each row, and
-the notes appear inside the listings in the original UI{
-(Figure~\ref{fig:airbnb-demo}, Note C)}. The annotations are saved in
-the browser and associated with the backend ID of the listing, so they
-will appear in future browser sessions that display the same listing.
+Alice has previously used Wildcard to customize timeanddate.com. In
+addition to sorting the list of holidays in a year by the day of the
+week, she also wants to sort them by category so she can view all the
+federal holidays together. Previously, she would have needed to find a
+programmer to help her edit the adapter code to incorporate this
+additional data, but using our system's support for \textbf{editing by
+demonstration}, Alice can extend the adapter herself.
 
-Wildcard also includes a formula language that enables more
-sophisticated customizations. When traveling without a car, it's useful
-to evaluate potential places to stay based on how walkable the
-surroundings are. Using a formula, the user can integrate Airbnb with
-Walkscore, an API that rates the walkability of any location on a 1-100
-scale. When the user calls the \texttt{walkscore} formula with the
-listing's latitude and longitude as arguments, it returns the walk score
-for that location and shows it as the cell value. Because the cell's
-contents are injected into the page, the score also appears in the UI{
-(Figure~\ref{fig:airbnb-demo}, Note D)}.
+While viewing the website, she clicks the ``Edit Adapter'' button above
+the Wildcard table to initiate the adapter editing process. As she
+hovers over the currently scraped values, the columns they belong to are
+highlighted. Finally, she clicks on ``Federal Holiday'' to add the new
+column of data and saves the changes. Alice then proceeds to sort the
+list by the type of holiday without the intervention of a programmer.
 
-\hypertarget{snoozing-todos}{%
-\subsection{Snoozing todos}\label{snoozing-todos}}
+\hypertarget{repairing-an-adapter}{%
+\subsection{Repairing An Adapter}\label{repairing-an-adapter}}
 
-\begin{figure}
-\hypertarget{fig:todomvc-demo}{%
-\centering
-\includegraphics{media/todomvc-demo-300dpi.png}
-\caption{Using Wildcard to add a ``snooze'' feature to the TodoMVC todo
-list app}\label{fig:todomvc-demo}
-}
-\end{figure}
+Alice next visits Google Scholar to look up references for her thesis
+project. Unfortunately, the customization she had applied to sort
+publications by their title (which is not natively supported by Google
+Scholar) is no longer working. In fact, the column in the Wildcard table
+that contained all the publication titles is empty, because the
+website's internals changed and broke the adapter's scraping logic.
+Alice can repair this on her own, again taking advantage of
+\textbf{editing by demonstration}.
 
-In addition to fetching data from other sources, Wildcard formulas can
-also perform computations. In this example, the user would like to
-augment the TodoMVC todo list app with a ``snooze'' feature, which will
-temporarily hide a todo from the list until a certain date.{
-Figure~\ref{fig:todomvc-demo} shows an overview of this customization.}
-
-The user opens the table view, which shows the text and completed status
-of each todo. They start the customization by adding a new column to
-store the snooze date for each todo{ (Figure~\ref{fig:todomvc-demo},
-Note A)}.
-
-The next step is to hide snoozed todos. The user creates a
-\texttt{snoozed?} column, which uses a formula to compute whether a todo
-is snoozed---i.e., whether it has a snooze date in the future{
-(Figure~\ref{fig:todomvc-demo}, Note B)}. Then, they simply filter the
-table to hide the snoozed todos{ (Figure~\ref{fig:todomvc-demo}, Note
-C)}.
-
-Because the built-in \texttt{NOW()} function always returns the current
-datetime, snoozed todos will automatically appear once their snooze date
-arrives.
-
-Because this implementation of snoozing was built on the spreadsheet
-abstraction, it is completely decoupled from this particular todo list
-app. We envision that users could share these types of customizations as
-generic browser extensions, which could be applied to any site supported
-by Wildcard with no additional effort.
-
-\hypertarget{adding-a-custom-datepicker}{%
-\subsection{Adding a custom
-datepicker}\label{adding-a-custom-datepicker}}
-
-\begin{figure}
-\hypertarget{fig:expedia-demo}{%
-\centering
-\includegraphics{media/expedia-demo-300dpi.png}
-\caption{Using Wildcard to augment the Expedia page for booking a
-flight}\label{fig:expedia-demo}
-}
-\end{figure}
-
-It might seem that Wildcard is only useful on websites that display
-lists of tabular data, but the table metaphor is flexible enough to
-represent many types of data. For example, a flight search form on
-Expedia can be represented as a single row, with a column corresponding
-to each input{ (Figure~\ref{fig:expedia-demo}, Note A)}.
-
-In some of the previous examples, the table cells were read-only
-(because users can't, for example, change the name or price of an Airbnb
-listing). In this case, the cells are writable, which means that changes
-in the table are reflected in the form inputs. This becomes especially
-useful when combined with GUI widgets that can edit the value of a table
-cell.
-
-Filling in dates for a flight search often requires a cumbersome
-workflow: open up a separate calendar app, find the dates for the trip,
-and then carefully copy them into the form. In Wildcard, the user can
-avoid this by using a datepicker widget that shows the user's personal
-calendar events{ (Figure~\ref{fig:expedia-demo}, Note B)}. The user can
-directly click on the correct date, and it gets inserted into both the
-spreadsheet and the original form.
-
-In this section we've presented just a few use cases for
-spreadsheet-driven customization, to suggest some possibilities of the
-paradigm. We think the spreadsheet model is flexible enough to support a
-wide range of other useful modifications while remaining familiar and
-easy to use.
+Alice initiates the editing process, and initially hovers over the
+desired value to demonstrate the column she wants to scrape. However,
+the \textbf{live programming} interface indicates to her that the values
+would be populated into column D; instead, she wants the values to be
+inserted into column A where they previously appeared. So, Alice clicks
+on the symbol for column A to indicate that she wants to scrape the
+values into that column. She then proceeds to re-apply her customization
+to the website by sorting the publications by their title without the
+intervention of a programmer.
 
@@
 
-Wildcard is written in Typescript. It is currently injected into pages
-using the \href{https://www.tampermonkey.net/}{Tampermonkey} userscript
-manager, but in the future we plan to deploy it as a standalone browser
-extension to make it easier to install.
+We implemented our end-user web scraping system as an addition to the
+Wildcard browser extension. We start by describing our implementations
+of row and column generalization, live programming, and editing by
+demonstration, and then discuss some of the current limitations of our
+system.
 
-In order to promote extensibility, Wildcard is implemented as a small
-core program along with several types of plugins: site adapters,
-formulas, and cell editors. The core contains functionality for
-displaying the data table and handling user interactions, and is built
-on the \href{https://handsontable.com/}{Handsontable} Javascript
-library.
+\hypertarget{generalization-algorithms}{%
+\subsection{Generalization Algorithms}\label{generalization-algorithms}}
 
-\begin{figure}
-\hypertarget{fig:architecture}{%
-\centering
-\includegraphics{media/architecture-300dpi.png}
-\caption{The architecture of the Wildcard
-prototype}\label{fig:architecture}
-}
-\end{figure}
+In order to generate reusable scrapers from user demonstrations, our
+system solves the \emph{wrapper induction} \citep{kushmerick2000} task:
+generalizing from a small set of user-provided examples to a scraping
+specification that will work on other parts of the website, and on
+future versions of the website.
 
-Site adapters are a key part of Wildcard, since they specify the
-bidirectional connection between the web page and its structured data
-representation. Wildcard represents data in a relational table with
-named and typed columns, and provides an interface for concisely
-expressing how the DOM should be mapped to this structure. For example,
-here is a code snippet for extracting the name of an Airbnb listing.
+We take an approach similar to that used in other tools like Vegemite
+\citep{lin2009} and Sifter \citep{huynh2006}:
+
+\begin{itemize}
+\tightlist
+\item
+  We generate a single \emph{row selector} for the website: a CSS
+  selector that returns a set of DOM elements corresponding to
+  individual rows of the table.
+\item
+  For each column in the table, we generate a \emph{column selector}, a
+  CSS selector that returns the element containing the column value
+  within that row.
+\end{itemize}
+
+One important difference is that our algorithm only accepts row elements
+that have direct siblings with a similar structure. We refer to this as
+the \emph{row-sibling} constraint. Later in this section, we describe
+how the constraint provides a useful simplification of the wrapper
+induction task and discuss the resulting limitations this puts on our
+system in a section that follows.
+
+When a user first demonstrates a column value, the generalization
+algorithm is responsible for turning the demonstration into a row
+selector that will correctly identify all the row elements in the
+website and a column selector that will correctly identify the element
+that contains the column value within a row element. During subsequent
+demonstrations, the generalization algorithm uses the generated row
+selector to find the row element that contains the column value and
+generates a column selector which identifies the corresponding column
+element.
+
+At a high level, the generalization algorithm's challenge is to traverse
+far enough up in the DOM tree from the demonstrated element to find the
+element which corresponds to the row. We solve this using a heuristic;
+the basic intuition is to find a large set of elements with similar
+parallel structure. Consider the following sample HTML layout, which
+displays a truncated table of superheroes, with each row containing some
+nested structure:
 
@@
 \begin{Highlighting}[]
-\OperatorTok{\{}
-  \CommentTok{// Field metadata:}
-\NormalTok{  fieldName}\OperatorTok{:} \StringTok{"name"}\OperatorTok{,}
-\NormalTok{  type}\OperatorTok{:} \StringTok{"text"}\OperatorTok{,}
-\NormalTok{  readOnly}\OperatorTok{:} \KeywordTok{true}\OperatorTok{,}
-
-  \CommentTok{// Function to extract DOM element:}
-\NormalTok{  el}\OperatorTok{:}\NormalTok{ (row) }\KeywordTok{=>} \VariableTok{row}\OperatorTok{.}\FunctionTok{querySelector}\NormalTok{(}\StringTok{".\_1ebt2xej"}\NormalTok{)}\OperatorTok{,}
-\OperatorTok{\}}
+\KeywordTok{\textless{}body\textgreater{}}
+    \KeywordTok{\textless{}h1\textgreater{}}\NormalTok{ Team Iron Man }\KeywordTok{\textless{}/h1\textgreater{}}
+    \KeywordTok{\textless{}div}\OtherTok{ class=}\StringTok{’container’}\KeywordTok{\textgreater{}}
+        \KeywordTok{\textless{}div}\OtherTok{ class=}\StringTok{\textquotesingle{}avenger\textquotesingle{}}\KeywordTok{\textgreater{}}
+            \KeywordTok{\textless{}div}\OtherTok{ class=}\StringTok{\textquotesingle{}names\textquotesingle{}}\KeywordTok{\textgreater{}}
+                \KeywordTok{\textless{}span}\OtherTok{ class=}\StringTok{\textquotesingle{}super\_hero\_name\textquotesingle{}}\KeywordTok{\textgreater{}}\NormalTok{ Iron Man }\KeywordTok{\textless{}/span\textgreater{}}
+                \KeywordTok{\textless{}span}\OtherTok{ class=}\StringTok{\textquotesingle{}real\_name\textquotesingle{}}\KeywordTok{\textgreater{}}\NormalTok{ Tony Stark }\KeywordTok{\textless{}/span\textgreater{}}
+            \KeywordTok{\textless{}/div\textgreater{}}
+           \KeywordTok{\textless{}span}\OtherTok{ class=}\StringTok{’gender’}\KeywordTok{\textgreater{}}\NormalTok{ Male }\KeywordTok{\textless{}/span\textgreater{}}
+        \KeywordTok{\textless{}/div\textgreater{}}
+        \KeywordTok{\textless{}div}\OtherTok{ class=}\StringTok{\textquotesingle{}avenger\textquotesingle{}}\KeywordTok{\textgreater{}}
+            \KeywordTok{\textless{}div}\OtherTok{ class=}\StringTok{\textquotesingle{}names\textquotesingle{}}\KeywordTok{\textgreater{}}
+                \KeywordTok{\textless{}span}\OtherTok{ class=}\StringTok{\textquotesingle{}super\_hero\_name\textquotesingle{}}\KeywordTok{\textgreater{}}\NormalTok{  Black Widow }\KeywordTok{\textless{}/span\textgreater{}}
+                \KeywordTok{\textless{}span}\OtherTok{ class=}\StringTok{\textquotesingle{}real\_name\textquotesingle{}}\KeywordTok{\textgreater{}}\NormalTok{ Natalia Romanoff }\KeywordTok{\textless{}/span\textgreater{}}
+            \KeywordTok{\textless{}/div\textgreater{}}
+            \KeywordTok{\textless{}span}\OtherTok{ class=}\StringTok{’gender’}\KeywordTok{\textgreater{}}\NormalTok{ Female }\KeywordTok{\textless{}/span\textgreater{}}
+        \KeywordTok{\textless{}/div\textgreater{}}
+\NormalTok{        ...}
+    \KeywordTok{\textless{}/div\textgreater{}}
+\KeywordTok{\textless{}/body\textgreater{}}
 \end{Highlighting}
@@
 
-Sometimes, more advanced scraping techniques are necessary to extract
-data from the application. For example, we have prototyped a mechanism
-for site adapters to observe AJAX requests made by the browser and
-extract data directly from JSON responses. This mechanism was used to
-implement the Airbnb Walkscore example, since latitude and longitude
-aren't shown in the Airbnb UI, but they are available in AJAX responses.
-This technique seems promising because AJAX responses already contain
-data in a structured form, and web applications are increasingly loading
-data using AJAX. Another technique we might consider is enabling site
-adapters to scrape data across multiple pages for paginated lists of
-results (as explored in \autocite{huynh2006}).
+The user performs a demonstration by clicking on the SPAN element
+containing ``Tony Stark.'' Our algorithm traverses upwards from the
+demonstrated element, considering each successive parent element as a
+potential candidate for the row element. For each parent element \(n\),
+the process is as follows:
 
-Because Wildcard requires a live bidirectional connection between the UI
-and the structured data, there are some additional challenges beyond
-those typically associated with web scraping.
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\tightlist
+\item
+  compute a selector \(s\) that when executed on \(n\) only returns the
+  demonstrated element
+\item
+  for each sibling \(m\) of \(n\), execute \(s\) on \(m\) and record
+  whether the selector returned an element. Intuitively, if the selector
+  returns an element, this suggests that the sibling \(m\) has some
+  parallel structure to \(n\)
+\item
+  compute \(n_{siblings}\), the number of sibling elements of \(n\) for
+  which \(s\) returned an element
+\end{enumerate}
 
-First, the site adapter needs to support sending updates from the table
-to the original page. We have made this fairly straightforward, because
-most DOM manipulation is not performed directly by the site adapter.
-Instead, Wildcard automatically mutates the DOM to reflect the
-spreadsheet state, using the same specification that was used to extract
-the data. The only exception to this is row actions (like favoriting an
-Airbnb listing), which are implemented as Javascript functions that can
-perform arbitrary behaviors like simulating clicks on buttons or
-mutating the DOM.
+Notice how the row-sibling constraint simplifies the problem: row
+candidates without siblings that return an element after \(s\) is
+executed on them have \(n_{siblings}\) = 0, thus disqualifying them.
+Furthermore, a candidate element \(n\) is only accepted as the row
+element if the row selector associated with it only matches itself and
+elements that are its direct siblings.
 
-Another challenge is triggering updates to the spreadsheet data in
-response to UI changes that happen after initial page load. Site
-adapters are responsible for recognizing these changes by observing the
-DOM. So far, we have been able to use event listeners and the
-MutationObserver API to successfully observe changes, but it may prove
-challenging to observe changes on some sites only through the DOM.
+From the parent of the initial SPAN element, the algorithm moves up the
+DOM tree until it reaches the BODY element. Then, it generates a
+selector for each \(n\) and discards any \(n\) with a selector that
+matches elements that are either not itself or a direct sibling.
+Finally, the algorithm picks an \(n\) with the largest, positive
+\(n_{siblings}\), preferring nodes lower in the tree as a tiebreaker.
+\(s\) is used as the selector for the column.
+
+Applying this to our example, if the user clicks on the SPAN element
+containing ``Tony Stark,'' , the first parent element is the DIV with
+the class \emph{names}This DIV has a sibling SPAN element, but the
+sibling doesn't return an element when \emph{.super\_hero}, the selector
+that identifies the initial SPAN in the DIV, is executed on it. As a
+result, it has \(n_{siblings}\) = 0. At the level above that, we
+consider the DIV with class \emph{avenger}, which has at least one
+sibling that returns an element when the selector \emph{.super\_hero} is
+executed on it. Finally, the level above that once again has no siblings
+that return an element when the selector \emph{.super\_hero} is executed
+on them. Therefore, our algorithm returns the DIV element and outputs
+\emph{.avenger} as the row selector and \emph{.super\_hero} as the
+column selector. These selectors are used to generate a DOM scraping
+adapter which returns the DOM elements corresponding to a superhero data
+row in the table.
+
+\hypertarget{live-programming}{%
+\subsection{Live Programming}\label{live-programming}}
+
+Live programming is implemented by continually running the
+generalization algorithm on the DOM element under the user's cursor,
+reverting if the user hovers away and committing when the user clicks.
+The generated row and column selectors are used to highlight all the
+matching elements on the website and create an adapter. Highlighting all
+the matching column elements on the website provides visual feedback
+about the system's generalization to the user. Creating an adapter
+enables the system to populate the table view and set up the
+bidirectional synchronization. Because the table is populated and the
+bidirectional synchronization is set up, users can customize as they
+scrape.
+
+\hypertarget{editing-by-demonstration}{%
+\subsection{Editing By Demonstration}\label{editing-by-demonstration}}
+
+Our system generates adapters with the row selector and the column
+selectors used to scrape the data. The row selector is a CSS selector
+that identifies all the row elements of the data and the column
+selectors are CSS selectors that identify each column's column elements.
+
+When the editing process is initiated, the adapter's row selector and
+column selectors are used to highlight the previously scraped values on
+the website. Furthermore, the generalization algorithm takes the
+adapter's row selector and uses it as the basis to generate new column
+selectors after each demonstration. When a new column is demonstrated,
+our system appends the generated column selector to the list of column
+selectors. This is how adapters are extended to create new columns. When
+an existing column is demonstrated, our system replaces the column's
+current column selector with the generated column selector. This is how
+adapters are repaired to fix broken columns.
+
+Extending and repairing adapters in this manner is feasible because
+column selectors are independent of each other: changing one column's
+selector does not affect another column's selector. This is not the case
+for system's in which the output of demonstrations are dependent on each
+other. For example, in a web automation sequence that involves clicking
+on a button to open a menu and then entering text into the menu's text
+input, the step that enters the text is not independent because it
+depends on the step that clicks the button to open the menu.
+
+\hypertarget{limitations}{%
+\subsection{Limitations}\label{limitations}}
+
+The row-sibling constraint we mentioned earlier is important for the end
+goal of customization because row elements that are not direct siblings
+may not represent data on the website that should be related as part of
+the same table by customizations such as sorting and filtering. Take the
+following sample HTML layout showing two tables of superheros (Team Iron
+Man and Team Captain America):
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\KeywordTok{\textless{}body\textgreater{}}
+  \KeywordTok{\textless{}h1\textgreater{}}\NormalTok{ Team Iron Man }\KeywordTok{\textless{}/h1\textgreater{}}
+  \KeywordTok{\textless{}div}\OtherTok{ class=}\StringTok{’container’}\KeywordTok{\textgreater{}}
+      \KeywordTok{\textless{}div}\OtherTok{ class=}\StringTok{\textquotesingle{}avenger\textquotesingle{}}\KeywordTok{\textgreater{}}
+          \KeywordTok{\textless{}span}\OtherTok{ class=}\StringTok{\textquotesingle{}super\_hero\_name\textquotesingle{}}\KeywordTok{\textgreater{}}\NormalTok{ Iron Man }\KeywordTok{\textless{}/span\textgreater{}}
+      \KeywordTok{\textless{}/div\textgreater{}}
+      \KeywordTok{\textless{}div}\OtherTok{ class=}\StringTok{\textquotesingle{}avenger\textquotesingle{}}\KeywordTok{\textgreater{}}
+          \KeywordTok{\textless{}span}\OtherTok{ class=}\StringTok{\textquotesingle{}super\_hero\_name\textquotesingle{}}\KeywordTok{\textgreater{}}\NormalTok{  Black Widow }\KeywordTok{\textless{}/span\textgreater{}}
+      \KeywordTok{\textless{}/div\textgreater{}}
+\NormalTok{      ...}
+  \KeywordTok{\textless{}/div\textgreater{}}
+  \KeywordTok{\textless{}h1\textgreater{}}\NormalTok{ Team Captain America }\KeywordTok{\textless{}/h1\textgreater{}}
+  \KeywordTok{\textless{}div\textgreater{}}
+      \KeywordTok{\textless{}div}\OtherTok{ class=}\StringTok{\textquotesingle{}avenger\textquotesingle{}}\KeywordTok{\textgreater{}}
+          \KeywordTok{\textless{}span}\OtherTok{ class=}\StringTok{\textquotesingle{}super\_hero\_name\textquotesingle{}}\KeywordTok{\textgreater{}}\NormalTok{ Captain America }\KeywordTok{\textless{}/span\textgreater{}}
+      \KeywordTok{\textless{}/div\textgreater{}}
+      \KeywordTok{\textless{}div}\OtherTok{ class=}\StringTok{\textquotesingle{}avenger\textquotesingle{}}\KeywordTok{\textgreater{}}
+          \KeywordTok{\textless{}span}\OtherTok{ class=}\StringTok{\textquotesingle{}super\_hero\_name\textquotesingle{}}\KeywordTok{\textgreater{}}\NormalTok{  Scarlet Witch }\KeywordTok{\textless{}/span\textgreater{}}
+      \KeywordTok{\textless{}/div\textgreater{}}
+\NormalTok{      ...}
+  \KeywordTok{\textless{}/div\textgreater{}}
+\KeywordTok{\textless{}/body\textgreater{}}
+\end{Highlighting}
+\end{Shaded}
+
+Without the constraint that row elements have to be direct siblings, the
+row generalization algorithm could determine the row selector to be
+\emph{.avenger} because it matches the largest number of parallel
+structures (has the largest \(n_{siblings}\)). While this may be the
+correct result for the task of extraction, it is not for the task of
+customization. The selector matches all rows across the two tables so
+the sorting and filtering customizations could place rows in the
+incorrect table and thereby distort what the tables represent. Because
+of this, our system currently does not support such DOM structures but
+we plan to explore the possibility of extracting multiple tables from a
+website and joining them.
+
+Another structure that our system cannot currently generalize over is
+one in which column elements are not contained within a row element that
+is a direct sibling of all the other row elements. Take the following
+sample HTML layout showing a table of superheros:
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\KeywordTok{\textless{}body\textgreater{}}
+  \KeywordTok{\textless{}h1}\OtherTok{ class=}\StringTok{\textquotesingle{}super\_hero\_name\textquotesingle{}}\KeywordTok{\textgreater{}}\NormalTok{ Iron Man }\KeywordTok{\textless{}/h1\textgreater{}}
+  \KeywordTok{\textless{}span}\OtherTok{ class=}\StringTok{\textquotesingle{}real\_name\textquotesingle{}}\KeywordTok{\textgreater{}}\NormalTok{ Real Name: Tony Stark }\KeywordTok{\textless{}/span\textgreater{}}
+  \KeywordTok{\textless{}h1}\OtherTok{ class=}\StringTok{\textquotesingle{}super\_hero\_name\textquotesingle{}}\KeywordTok{\textgreater{}}\NormalTok{ Captain America }\KeywordTok{\textless{}/h1\textgreater{}}
+  \KeywordTok{\textless{}span}\OtherTok{ class=}\StringTok{\textquotesingle{}real\_name\textquotesingle{}}\KeywordTok{\textgreater{}}\NormalTok{ Real Name: Steven Rogers }\KeywordTok{\textless{}/span\textgreater{}}
+  \KeywordTok{\textless{}h1}\OtherTok{ class=}\StringTok{\textquotesingle{}super\_hero\_name\textquotesingle{}}\KeywordTok{\textgreater{}}\NormalTok{ Black Widow }\KeywordTok{\textless{}/h1\textgreater{}}
+  \KeywordTok{\textless{}span}\OtherTok{ class=}\StringTok{\textquotesingle{}real\_name\textquotesingle{}}\KeywordTok{\textgreater{}}\NormalTok{ Real Name: Natalia Romanoff }\KeywordTok{\textless{}/span\textgreater{}}
+\NormalTok{  ...}
+\KeywordTok{\textless{}/body\textgreater{}}
+\end{Highlighting}
+\end{Shaded}
+
+This page contains one table of data in which rows are made up of an H1
+tag (super hero name) and a SPAN tag (real name). For the task of
+extraction, the DOM elements can be scraped using the shown classes to
+output a table in which the values of the H1 tags form the first column
+and the values of the SPAN tag form the second column. For the task of
+customization, our system would need to know what the row boundaries
+were in order for customizations such as sorting and filtering to work
+as expected. In Wildcard, this can be done with a hand-coded adapter by
+creating artificial row boundaries. In the above DOM structure, an
+artificial row boundary could be created by representing a row as an H1
+tag and the SPAN tag that immediately follows it. These artificial rows
+would form a single unit which would not distort the website after a
+sorting or filtering customization. We plan to explore how such
+artificial row boundaries might be created via demonstration in order to
+support these structures (which are not uncommon, and can be seen, for
+example, in HackerNews).
 
@@
 
-The idea of spreadsheet-driven customization is guided by three design
-principles, inspired by prior work and our own experimentation. We think
-these principles might also broadly inform the design of tools for end
-user software customization.
+Below, we discuss the three design principles underlying our work and
+how they relate to the broader field of end-user web scraping and
+customization.
 
-\hypertarget{expose-a-universal-data-structure}{%
-\subsection{Expose a universal data
-structure}\label{expose-a-universal-data-structure}}
+\hypertarget{unified-environment}{%
+\subsection{Unified Environment}\label{unified-environment}}
 
-Today, most personal computing consists of using applications, which
-bundle together behavior and data to provide some set of functionality.
-While there are some limited points of interoperability, applications
-generally are designed to operate independently of one another.
+In the previous iteration of Wildcard, web scraping was an entirely
+separate activity from customization. Programmers that wrote scraping
+adapters would need to switch into an IDE to write code as part of
+customizing a new website, making it a much less unified environment.
 
-Computing does not need to be organized this way. For example, UNIX
-offers a compelling alternative: many small single-purpose programs, all
-of which manipulate a universal format of text streams. Users get high
-leverage from mastering a text editor and other text manipulation tools,
-since they can be applied to a huge variety of tasks. A user's preferred
-text editor can even serve as an interactive input mechanism in shell
-programs, e.g.~for editing git commit messages.
+This type of divide between tasks appears in other domains. In data
+science, workflows revolve between cleaning and using data but this
+often happens in different environments. The creators of Wrex
+\citep{drosos2020}, a programming-by-example system for data wrangling,
+reported that ``although data scientists were aware of and appreciated
+the productivity benefits of existing data wrangling tools, having to
+leave their native notebook environment to perform wrangling limited the
+usefulness of these tools.'' In web scraping, if a user comes across an
+omission while working with data scraped from a website, they need to
+switch from the environment in which they are using the data to the
+environment in which they wrote their scraping code in order to edit and
+re-run it. Sometimes, the divide is more subtle. Vegemite
+\citep{lin2009}, a system for end-user programming of mashups, had
+separate steps for scraping data from a website and augmenting that data
+via automation tasks. During a user study, participants reported that
+``it was confusing to use one technique to create the initial table, and
+another technique to add information to a new column.''
 
-Spreadsheet-driven customization aims to bring some of this UNIX ethos
-to the world of isolated Web applications by creating a consistent data
-structure to represent the data inside many applications. In UNIX, the
-universal format is a text stream; in Wildcard, it is a relational
-table. Because Wildcard maps the data from all applications to the table
-format, users can master the tools provided by Wildcard and apply them
-to customize many different applications.
+In this work, we have combined scraping and customization into a unified
+activity within a single environment. The goal is to minimize the
+environment switch between \emph{extracting} the data and \emph{using}
+the data. A user might start out by scraping some data, and then switch
+to customizing the website using the results. Then, they might realize
+they need more data to perform their desired task, at which point they
+can easily augment the adapter by demonstrating new columns. All of
+these tasks take place right in the browser, where the user was
+initially already using the website. Instead of bringing the data to
+another tool, we have brought a tool to the data. This directly relates
+to the idea of ``in-place toolchains'' \citep{zotero-60} being an
+integral part of end-user programming systems.
 
-This idea relates to Beaudouin-Lafon and Mackay's notion of
-\emph{polymorphic interface instruments} \autocite{beaudouin-lafon2000},
-which are UI elements that can be used in different contexts (for
-example, a color picker that can be used in many drawing applications).
-It also relates to ideas of literacy in a medium. DiSessa notes that
-textual literacy depends on the fact that writing can be adapted to many
-different genres \autocite{disessa2000}: if people needed to relearn
-reading and writing from scratch when switching from essays to emails,
-the medium would lose its potency. Generic tools are especially
-important for software customization, because a common barrier to
-customizing software is not having enough time
-\autocite{mackay1991}---it's more likely that people will customize
-software frequently if they can reuse the same tools across many
-applications.
+Of course, there is value in specialized tools: Wildcard has nowhere
+near the full capabilities of spreadsheet software or databases.
+Nevertheless, we believe a single, unified environment for scraping and
+customization presents a significantly lower barrier to entry for
+customization.
 
-This design principle leads to several challenges. First, any universal
-abstraction has its limits, and may not naturally express the data in
-every application. We plan to explore the limits of the table
-abstraction further by trying to build adapters for more sites with
-varied data formats. We expect that many types of data will fit easily
-into tables: lists of search results, news articles, and messages can
-all naturally be seen as relations. Documents (e.g.~Google Docs) or
-graphs (e.g.~social network friend graphs) may prove more challenging to
-map to the table abstraction.
+\hypertarget{editing-by-demonstration-1}{%
+\subsection{Editing By Demonstration}\label{editing-by-demonstration-1}}
 
-\hypertarget{low-floor-high-ceiling}{%
-\subsection{Low floor, high ceiling}\label{low-floor-high-ceiling}}
+Many end-user web scraping and macro systems allow users to
+\emph{create} programs by demonstration but do not offer a way to
+\emph{edit} them by demonstration. In Rousillon \citep{chasins2018}, a
+web scraping program created by demonstration can only be edited through
+a high-level, block-based programming language called Helena
+\citep{zotero-51} which does not support providing new demonstrations to
+extend or repair the scraping code. In Vegemite \citep{lin2009}, a web
+automation program created through demonstration can only be edited by
+editing the text-based representation of the program.
 
-Seymour Papert advocated for programming systems to have a ``low
-floor,'' making it easy for novices to get started, and a ``high
-ceiling,'' providing a large range of possibilities for more
-sophisticated users \autocite{resnick2016}. Our goal is for
-spreadsheet-driven customization to meet both of these criteria.
+In Wildcard, if a website's hand-coded adapter ceases to function
+because the website changes, the table may lose its data which means
+that an end-user's customizations may also cease to function.
+Furthermore, end-users are powerless to extend the scraping adapter to
+add columns to the table in order to perform new customizations. This
+goes against MacLean et. al.'s vision of user-tailorable systems
+\citep{maclean1990} that give users ``a feeling of ownership of the
+system, to feel in control of changing the system and to understand what
+can be changed.'' Providing an easy way for users to edit programs is
+therefore fundamental to fully democratizing web customization.
 
-One of the most interesting properties of spreadsheets is that users
-familiar with only a tiny sliver of their functionality (e.g., storing
-tables of numbers and computing simple sums) can still use them in
-valuable ways. This supports the user's natural motivation to continue
-using the tool, and to eventually learn its more powerful features if
-needed \autocite{nardi1991}. In contrast, many traditional programming
-systems require an enormous upfront time investment before someone is
-able to write a program that helps them achieve a useful task.
+Editing by demonstration makes end-users first-class citizens in the
+customization ecosystem. Because users interact with the scraped data
+directly in the context of the website, it is easy to initiate the
+scraping system in editing mode: the scraping system is simply booted up
+using metadata stored with the scraping adapter to the state when the
+demonstration was completed. Users that have gone through the creation
+process will immediately realize what to do in order to extend or repair
+the adapter. Users that have not gone through the creation process might
+have a harder time but we provide visual clues (such as highlighting the
+row to perform demonstrations from with a green border) and live
+programming (immediately preview the results of demonstrations) that
+serve as guides.
 
-As part of ensuring a low floor, we have focused on including features
-that have immediate value for novices. For example, a user can sort a
-table with a single click, or simply type in some annotations. We would
-expect many Wildcard users to start by using these simpler features
-before moving on to more sophisticated features like formulas.
+As discussed in Section~\ref{sec:implementation}, editing by
+demonstration in the web scraping domain is feasible because column
+selectors are independent of each other. However, this is not the case
+with row selectors because column selectors are dependent on them. Our
+system therefore does not support editing rows but this an acceptable
+limitation given our focus on extension and repair which only involve
+column selectors.
 
-Another aspect of providing a low floor is providing an ``in-place
-toolchain'' \autocite{2019}: minimizing the effort of moving from using
-to customizing by making customization tools available in the same
-environment where the user is already using the software. This quality
-is distinct from the level of technical skill needed to use the tool.
-For example, setting up a workflow in an end user programming system
-like \href{https://ifttt.com/}{IFTTT} does not require much programming
-skill, but it does require leaving the user's normal software and
-entering a separate environment; conversely, running a Javascript
-snippet in the browser console requires programming skills, but can be
-done immediately in the flow of using a website.
+\hypertarget{live-programming-1}{%
+\subsection{Live Programming}\label{live-programming-1}}
 
-\begin{longtable}[]{@{}llc@{}}
-\toprule
-\endhead
-& \emph{In-place} & \emph{Not in-place}\tabularnewline
-\emph{End user friendly} & \textbf{Wildcard} & IFTTT\tabularnewline
-\emph{Requires programming} & browser JS console & using Web APIs in
-Python\tabularnewline
-\bottomrule
-\end{longtable}
+In some end-user web scraping systems like Rousillon
+\citep{chasins2018}, users only get \emph{full} feedback about the
+program's execution (generalization and the scraped values) after
+providing all the demonstrations. This means they cannot adjust their
+demonstrations in response to the system's feedback as they demonstrate.
 
-Wildcard provides an in-place toolchain because the spreadsheet can be
-instantly opened in the browser window while using any supported
-website. Once the user starts editing, Wildcard also provides live
-feedback, so that even if a user isn't yet totally familiar with
-Wildcard, they can learn to use the system through experimentation.
+Our end-user web scraping system employs live programming techniques to
+eliminate this edit-compile-debug cycle by running the generalization
+algorithm and generating an adapter after each user demonstration. As we
+showed in Section~\ref{sec:demos}, when a user demonstrates a value of a
+column they wish to scrape, our system immediately shows how it has
+generalized the user's demonstration across the other rows of the data
+by highlighting the all relevant values. It also populates the table
+with the scraped data based on the latest demonstration. The
+highlighting and table population serve to give users a view of how
+their demonstration has been generalized and what data will be available
+in the table once scraped.
 
-Since we have only built a few site adapters and demos so far, it is
-still too early to tell how high the ceiling is for the customizations
-that can be achieved with Wildcard. But we think that with enough
-built-in formulas (both standard spreadsheet formulas for computation,
-and formulas for fetching data from other sources), the language could
-support a wide variety of customizations. We plan to explore this aspect
-further by trying to solve real problems and observing where limitations
-emerge in practice (discussed more in Section~\ref{sec:conclusion}).
+Many successful end-user programming systems such as spreadsheets and
+SQL provide users with immediate results after entering commands. Our
+live programming environment is particularly similar to that of
+FlashProg \citep{mayer2015}, a framework that provides user interface
+support for programming-by-demonstration systems like FlashExtract
+\citep{le2014}, and relates to the idea that an important quality of
+end-user programming is ``interaction with a living system''
+\citep{zotero-60}.
 
-\hypertarget{design-for-an-ecosystem-of-users}{%
-\subsection{Design for an ecosystem of
-users}\label{design-for-an-ecosystem-of-users}}
+Unlike text-based commands which are only valid when complete (e.g
+\texttt{SELECT\ *\ FRO} versus \texttt{SELECT\ *\ FROM\ user\_table}),
+the target of demonstration commands (the value of a DOM element under
+the cursor) is the same during both hover and click (incomplete command
+verus complete command). This allows us to take a small step further by
+executing a command before a user completes it, thereby providing them
+with a preview of the results on hover.
 
-Real-world spreadsheet usage is highly collaborative. Many users only
-perform simple changes, while their coworkers help with writing complex
-formulas or programming macros \autocite{nardi1990}. Inspired by this
-collaborative dynamic, we aim for spreadsheet-driven customization to
-bring together the abilities of different users.
-
-The main way we do this is by separating website customization into two
-separate stages: structured data extraction, performed by programmers
-who code site adapters in Javascript, and then customization using the
-resulting spreadsheet, which is available to all end users. This
-architecture frees end users from needing to think about data
-extraction, and enables a community of end users to reuse the efforts of
-programmers building site adapters.
-
-The group of users building adapters does not necessarily need to be
-limited only to programmers. In the future, we plan to explore enabling
-end users to also create site adapters, drawing on related work in this
-area \autocite{chasins2018,huynh2006}. But even then, we still envision
-a separation between highly motivated, tech-savvy end users building
-adapters, and more casual end users just using the spreadsheet view.
-
-The first party developers of the original software can also play a role
-in enabling customization. Although spreadsheet-driven customization
-does not depend on cooperation from first party website developers,
-their participation in exposing structured data would eliminate the need
-for third party site adapters. The first parties could themselves
-benefit from such a system; providing Wildcard support---a fairly
-low-effort undertaking for a developer with direct access to the
-structured data---would allow users to build extensions to fulfill some
-of their own feature requests. There is also precedent for first parties
-implementing an official client extension API: for several years, Google
-maintained an official extension API in Gmail for Greasemonkey scripts
-to use.
-
-Google no longer maintains its own API, but third parties have continued
-to maintain successful replacements---Gmail.js \autocite{talwar2019} is
-an open source wrapper API with over 70 contributors and hundreds of
-commits. This library demonstrates another benefit of designing for an
-ecosystem: it's easier for many programmers to collectively maintain a
-generic site adapter that can support many extensions, rather than each
-programmer creating custom scraping logic for their own single-purpose
-extension.
+There are limits to this approach. Providing live feedback on websites
+with a large number of DOM elements or complex CSS selectors can slow
+down the generalization process, especially if a user is constantly
+moving their cursor. Furthermore, many datasets are too large to preview
+in the table in their entirety; the user might benefit more from the
+live feedback if it could summarize large datasets. For example,
+FlashProg provides a summary of the generalization through a color-coded
+minimap next to the scrollbar of its extraction interface.
 
@@
 
-Spreadsheet-driven customization relates to existing work in four areas:
-malleable software, web customization, spreadsheet-driven applications,
-and web scraping.
+End-user web scraping for customization relates to existing work in
+end-user web scraping by a number of tools.
 
-\hypertarget{malleable-software}{%
-\subsection{Malleable software}\label{malleable-software}}
+FlashProg \citep{mayer2015} is a framework that provides user interface
+support for FlashExtract \citep{le2014}, a framework for data scraping
+by examples. FlashProg's interface provides immediate visual feedback
+about the generalization and scrapes the matched values in an output
+tab. In addition, it has a program viewer tab that contains a high level
+description of what the generated program is doing and provides a list
+of alternative programs. Finally, it has a disambiguation tab that
+utilizes conversational clarification to disambiguate programs, the
+conservations with the user serving as inputs to generate better
+programs. Though FlashProg has many desirable features we aim to
+implement in future iterations, it does not offer a unified environment
+within a browser for scraping and customizing websites.
 
-In the broadest sense, Wildcard is inspired by systems aiming to make
-software into a dynamic medium where end users frequently create and
-modify software to meet their own needs, rather than only consuming
-applications built by programmers. These systems include Smalltalk
-\autocite{kay1977}, Hypercard \autocite{hypercard2019}, Boxer
-\autocite{disessa1986}, Webstrates \autocite{klokmose2015}, and
-Dynamicland \autocite{victor}. In fact, the name Wildcard comes from the
-internal pre-release name for Hypercard, a project which doubly inspired
-our work by promoting both software modification by end users and the
-ideas behind the Web.
+Roussillon \citep{chasins2018} is a tool that enables end-users to
+scrape distributed, hierarchical web data. Its interface does not
+provide \emph{full} live feedback about its generalizations or the
+values to be scrapped until all the demonstrations have been provided
+and the generated program has been run. If run on a website it has
+encountered before, Roussillon makes all the previously determined
+generalizations visible to the user by color-coding the values on the
+website that belong to the same column. This is a desirable feature for
+our system as users will not have to actively explore in order to
+discover which values are available for scraping and how they are
+related to each other. On the extension and repair front, Roussillon
+presents the web scraping code generated by demonstration as an
+editable, high-level, block-based language called Helena
+\citep{zotero-51}. While Helena can be used to perform more complex
+editing tasks like adding control flow, it presents a change in the
+model used for creation. Our system maintains the model used for
+creation by allowing users to extend and repair web scraping code via
+demonstration.
 
-Although Wildcard shares broad goals with these projects, it employs a
-different solution strategy. These other systems generally require
-building software from scratch in a new environment. On the other hand,
-Wildcard aims to maximize the malleability of software built with
-existing tools.
+Vegemite \citep{lin2009} is a tool for end-user programming of mashups.
+It has two interfaces: one for scraping values from a website and
+another for creating scripts that operate on the scraped values. The web
+scraping interface does not provide live feedback about the
+generalization on hover but after a user clicks, the interface shows the
+result of the system's generalization by highlighting the all matched
+values. Furthermore, even though the interface also has a table, the
+table is only populated with the scraped values after all the
+demonstrations have been provided. The scripting interface utilizes
+CoScripter \citep{leshed2008} which is used to record operations on the
+scraped values for automation. For example, the scripting interface can
+be used to demonstrate the task of copying an address in the table,
+pasting it into a walk score calculator and pasting the result back into
+the table. The script would then be generalized to all the rows and
+re-run to fill in the remaining walk scores. CoScripter provides the
+generated automation program as text-based commands, such as ``paste
+address into `Walk Score' input,'' which can be edited after the program
+is created via ``sloppy programming'' \citep{lin2009} techniques.
+However, this editing does not extend to the web scraping interface used
+for demonstrations.
 
-With substantial future work, we think Wildcard could become more
-similar to these other projects, growing from a platform for tweaking
-existing software into a platform for building new software from
-scratch. This would likely end up resembling existing tools for building
-spreadsheet-driven applications (discussed more below), but with an
-additional focus on customization by end users of the software.
-
-\hypertarget{web-customization}{%
-\subsection{Web customization}\label{web-customization}}
-
-Wildcard's goals are closely shared with other systems that provide
-interfaces in the browser for end users to customize websites.
-
-\hypertarget{structured-augmentation}{%
-\subsubsection{Structured augmentation}\label{structured-augmentation}}
-
-Wildcard's solution approach is most similar to other tools that
-identify structured data in a web page and then use that structure to
-support end user customization of the page.
-
-Sifter \autocite{huynh2006} enables users to sort and filter lists of
-data on web pages, which resembles Wildcard's sorting functionality. The
-underlying mechanism is similar, since Sifter extracts structured data
-from the page to enable its user-facing functionality. However, the
-systems also have significant differences:
-
-\begin{itemize}
-\tightlist
-\item
-  Wildcard hides data extraction from end users by having programmers
-  develop site adapters, whereas Sifter uses a combination of automated
-  heuristics and interactive user feedback to involve end users in
-  extracting data. User studies of Sifter indicated that users were
-  surprised by the need to participate in the data augmentation process,
-  which influenced our decision to hide this process from the user. We
-  suspect Wildcard's workflow results in a simpler end user experience,
-  but at the cost of only working with a smaller subset of supported
-  websites.
-\item
-  Wildcard supports a broad set of customizations. Sifter only supports
-  sorting and filtering.
-\item
-  Wildcard shows the structured data table directly to the user. Sifter
-  only shows sorting controls, and does not reveal the underlying data
-  table.
-\end{itemize}
-
-Thresher \autocite{hogue2005} enables users to create wrappers which map
-unstructured website content to Semantic Web content. Like Wildcard and
-Sifter, Thresher augments the page: once semantic content has been
-identified, it creates context menus in the original website which allow
-users to take actions based on that content. Wildcard and Thresher focus
-on complementary parts of the customization process. Thresher aims to
-enable end users to create content wrappers, but the actions available
-on the structured data are determined in advance. Conversely, Wildcard
-delegates wrapper creation to programmers, but gives end users more
-flexibility to use the structured data in an open-ended way.
-
-\hypertarget{sloppy-augmentation}{%
-\subsubsection{Sloppy augmentation}\label{sloppy-augmentation}}
-
-``Sloppy programming'' \autocite{little2010} tools like Chickenfoot
-\autocite{bolin2005} and Coscripter \autocite{leshed2008} enable users
-to create web automation scripts without directly interacting with the
-DOM. The scripts can perform actions like filling in text boxes and
-clicking on buttons. Users express the desired page elements in natural,
-informal terms (e.g.~writing ``the username box'' to represent the
-textbox closest to the label ``username''), and then the system uses a
-set of heuristics to determine which elements most likely match the
-user's intent. This approach allows for expressing a wide variety of
-commands with minimal training, but it also has downsides
-\autocite{little2010}:
-
-\begin{itemize}
-\tightlist
-\item
-  \emph{Reliability}: It can be difficult to know whether a command will
-  consistently work over time. Changes to the website or to the system's
-  heuristics can cause unexpected changes in behavior.
-\item
-  \emph{Discoverability}: it can be difficult for users to explore the
-  space of possible commands.
-\end{itemize}
-
-Wildcard offers a sharp contrast to sloppy programming, instead choosing
-to expose a high degree of structure through the spreadsheet table.
-Wildcard offers more consistency; for example, clicking a sort header
-will always work correctly as long as the site adapter is maintained.
-Wildcard also offers clearer affordances for what types of actions are
-possible. On the other hand, Wildcard's explicit site adapter approach
-means that fewer websites can be customized, and also that users can't
-perform customizations if the relevant data is not exposed in the
-spreadsheet.
-
-Another difference between Wildcard and these tools is that there is no
-way for users to express imperative workflows with sequences of actions
-in Wildcard. Chickenfoot and Coscripter have shown these types of
-workflows to be useful in practice so it might be worth considering how
-to incorporate them, but it's not obvious how such workflows could fit
-into Wildcard. Spreadsheets have a fundamentally different computation
-model, and site adapters created by programmers cannot easily account
-for every possible action a user might want to perform in a page.
-
-\hypertarget{spreadsheet-driven-applications}{%
-\subsection{Spreadsheet-driven
-applications}\label{spreadsheet-driven-applications}}
-
-Many researchers and companies have explored the idea of
-\emph{spreadsheet-driven applications}: using spreadsheets as a backing
-data store and computation layer for interactive web applications,
-enabling end users to create such applications more easily. Research
-projects like Object Spreadsheets \autocite{mccutchen2016}, Quilt
-\autocite{benson2014}, Gneiss \autocite{chang2014}, and Marmite
-\autocite{wong2007}, as well as commercial tools like Airtable
-\autocite{zotero-79} and Glide \autocite{zotero-81} allow users to view
-data in a spreadsheet table, compute over the data using formulas, and
-then connect the table to a GUI. Because many users are already familiar
-with spreadsheets, this way of creating applications tends to be much
-easier than traditional software methods; for example, in a user study
-of Quilt, many users were able to create applications in under 10
-minutes, even if they expected it would take them many hours.
-
-Wildcard builds on this idea, but applies it to modifying existing
-applications, rather than building new applications from scratch. For
-many people, we suspect that tweaking existing applications provides
-more motivation as a starting point for programming than creating a new
-application from scratch.
-
-An important design decision for tools in this space is how far to
-deviate from traditional spreadsheets like Microsoft Excel or Google
-Sheets. Quilt and Glide use existing spreadsheet software as a backend,
-providing maximum familiarity for users, and even compatibility with
-existing spreadsheets. Gneiss has its own spreadsheet implementation
-with additional features useful for building GUIs. Marmite provides a
-live data view that resembles a spreadsheet, but programming is actually
-done using a separate data flow pane rather than spreadsheet formulas.
-Marmite's approach led to some confusion in a user study, because users
-expected behavior more similar to spreadsheets \autocite{wong2007}.
-Airtable deviates the furthest: although the user interface resembles a
-spreadsheet, the underlying structure is a relational database with
-typed columns. Wildcard's table is most similar to Airtable; the
-structure of a relational table is most appropriate for most data in
-websites, and we have not yet found a need for arbitrary untyped cells.
-
-\hypertarget{web-scraping-data-extraction}{%
-\subsection{Web scraping / data
-extraction}\label{web-scraping-data-extraction}}
-
-Web scraping tools focus on extracting structured data out of
-unstructured web pages. Web scraping is closely related to the
-implementation of Wildcard, but has different end goals: web scraping
-generally extracts static data for processing in another environment,
-whereas Wildcard customizes the application's UI by maintaining a
-bidirectional connection between the extracted data and the page.
-
-Web scraping tools differ in how much structure they attempt to map onto
-the data. Some tools like Rousillon \autocite{chasins2018} extract data
-in a minimally structured relational format; other tools like Piggy Bank
-\autocite{huynh2005} more ambitiously map the data to a rich semantic
-schema. In Wildcard, we chose to avoid semantic schemas, in order to
-minimize the work associated with creating a site adapter.
-
-In the future, we might try to integrate existing web scraping tools, to
-help create more reliable site adapters for Wildcard with less work, and
-to open up adapter creation to end users. Although Wildcard has
-additional requirements beyond traditional web scraping as discussed in
-Section~\ref{sec:implementation}, there is still enough overlap that
-existing tools might prove helpful.
+Sifter \citep{huynh2006} is a tool that augments well structured
+websites with advanced sorting and filtering functionality. Like
+Wildcard, it uses web scraping to extract data from websites in order to
+enable customizations (sorting and filtering). It performs the web
+scraping automatically using a variety of heuristics and solicits
+guidance from the user if this fails. While automatic web scraping seems
+desirable, it is unclear how useful it is if the goal is customization.
+Given a row with ten scrapable values, and therefore ten columns, would
+a user prefer to simply demonstrate the value for the single column they
+are interested in or un-demonstrate the nine values they are not
+interested in? This is a question we can only answer after performing a
+user study.
 
 \hypertarget{sec:conclusion}{%
-\section{Conclusion and Future Work}\label{sec:conclusion}}
+\section{Conclusion And Future Work}\label{sec:conclusion}}
 
-In this paper, we have presented \emph{spreadsheet-driven
-customization}, a technique that enables end users to customize software
-by augmenting an application's UI with a spreadsheet. We still have many
-open questions which we hope to answer through targeted development and
-usage of Wildcard.{\footnote{Up to date information about Wildcard is
-  available on the project website
-  (\url{https://geoffreylitt.com/wildcard}), which includes a signup for
-  receiving updates and notifications about a public release. We also
-  welcome hearing from readers who might be interested in being private
-  beta testers or who have feedback on the project.}}
+In this paper, we presented our progress towards \emph{end-user web
+scraping for customization}, to empower end-users in Wildcard's
+ecosystem to create, extend and repair scraping adapters. There are
+several outstanding issues and open questions we hope to address in
+future work.
 
-The most important question is: what are the limits of this
-computational model? What types of useful customizations can it support
-or not support? While initial demos suggest a variety of use cases, we
-plan to develop more site adapters and demos to explore this question
-further. We will start by privately testing the system with our own
-needs and then eventually deploy the tool publicly once it has a stable
-API and can support a critical mass of sites and use cases. We also plan
-to run usability studies to evaluate and improve the design of the tool.
+Like existing approaches, web scraping in our current implementation is
+limited to what can be demonstrated. This is problematic if users want
+to scrape the URL associated with a link element, which is not visible,
+or only scrape a substring of a value. To solve this, we plan to harness
+Wildcard's formula language. End-users will be able to use formulas
+targeted at web scraping to access DOM element properties and
+attributes. For example, a formula like
+\texttt{=GetAttribute(link\_column,\ ‘href’)} could be used to scrape
+URLs of link elements. End-users will also be able to use formulas
+targeted at data processing. For example, a formula like
+\texttt{=GetSubstring(name\_column,\ 1,\ 2)} could be used to scrape
+substrings of text values. Such web scraping and data processing
+formulas will give end-users some of the power available to programmers
+that write web scraping code in Javascript which supports a wide variety
+of DOM access and processing ability.
 
-We suspect that some areas of the current model may prove overly
-simplistic. For example, Wildcard's data model currently shows a single
-table at a time, without any notion of relationships between tables. A
-richer data model with foreign keys might help support certain use
-cases. For designing a spreadsheet interface on top of a richer
-relational model, we could learn from other systems with this design
-\autocite{mccutchen2016,bakke2016}.
+To assess our design principles, we plan to carry out a broader
+evaluation of our system through a user study. Furthermore, we plan to
+incorporate the program viewer and disambiguation features of FlashProg
+\citep{mayer2015} to give users more insight and control into the
+generalization process.
 
-Another question is how easily site adapters can be created and
-maintained for real websites, which often include complex markup and
-change frequently. We plan to explore this question by creating adapters
-for sites with different data structures and in different domains, and
-perhaps running user tests with programmers. Possible future
-improvements we've considered include developing automated heuristics to
-assist with the adapter creation process and developing new abstractions
-that make it easier for programmers to efficiently create robust
-adapters.
+Our end goal is to empower end-users to customize websites in an
+intuitive and flexible way, and thus make the web more malleable for all
+of its users.
 
-Ultimately, we hope that spreadsheet-driven customization helps the Web
-reach its full potential as a dynamic medium that users can mold to
-their own needs.
+% \printbibliography
 
-\acks
-Thanks to Tarfah Alrashed, Glen Chiacchieri, David Karger, Steve Krouse, Rob Miller, Santiago Perez De Rosso, Arvind Satyanarayan, Daniel Windham, and Maggie Yellen for providing valuable feedback on this work.
-
-\printbibliography
+%%
+%% The next two lines define the bibliography style to be used, and
+%% the bibliography file.
+\bibliographystyle{ACM-Reference-Format}
+\bibliography{references.bib}
 
 \end{document}
-
-% Local Variables:
-% TeX-engine: luatex
-% End:
+\endinput
+%%
+%% End of file `sample-sigconf.tex'.

### 2021-02-13 compile-latex.sh

@@ -3,18 +3,17 @@ set -e
 pandoc \
   --filter conditional-render \
   --filter pandoc-crossref \
-  --filter pandoc-citeproc \
+    --citeproc \
   -s \
   -o \
   paper.tex \
-  --template=templates/pandoc-template-programming.pandoc \
-  --biblatex \
+  --template=templates/sigconf.pandoc \
+  --natbib \
   --metadata=format:pdf \
   paper.md
 
 pdflatex paper.tex
-biber paper
+bibtex paper
 pdflatex -interaction=batchmode paper.tex
 pdflatex -interaction=batchmode paper.tex
-cp paper.pdf ~/dev/homepage/source/wildcard/salon2020
 open paper.pdf

### 2021-02-13 paper.tex
Can now generate pdfs

@@
   should be able to scrape data and use it in a single, unified
-  environment, (b) users should be able to extend and repair the
-  programs that scrape data via demonstration and (c) users should
-  receive live feedback during their demonstrations.
+  environment, (b) users should be able to extend and repair the program
+  that scrapes data via demonstration and (c) users should receive live
+  feedback when providing demonstrations to scrape data.
 
   We have successfully used our system to create, extend and repair
-  adapters by demonstration on a variety of websites. We provide example
+  adapters by demonstration on a variety of websites and provide example
   usage scenarios that showcase each of our design principles.
@@
 \citep{bolin2005}, Thresher \citep{hogue2005}, Sifter \citep{huynh2006}
-and Vegemite {[}lin2009{]} help users tweak and adapt websites to fit
+and Vegemite \citep{lin2009} help users tweak and adapt websites to fit
 their unique requirements, ranging from reorganizing or annotating
@@
 leave their native notebook environment to perform wrangling limited the
-usefulness of these tools.'' In web scraping, if a user comes across an
+usefulness of these tools.'' This was a major reason Wrex was developed
+as an add-on to Jupyter notebooks, the environment in which data
+scientists use their data. In web scraping, if a user comes across an
 omission while working with data scraped from a website, they need to
@@
 re-run it. Sometimes, the divide is more subtle. Vegemite
-\citep{lin2009}, a system for end-user programming of mashups, had
-separate steps for scraping data from a website and augmenting that data
-via automation tasks. During a user study, participants reported that
-``it was confusing to use one technique to create the initial table, and
-another technique to add information to a new column.''
+\citep{lin2009}, a system for end-user programming of mashups, had a
+unified environment for scraping and augmenting data but separate
+interfaces for the scraping and augmentation tasks. During a user study,
+participants reported that ``it was confusing to use one technique to
+create the initial table, and another technique to add information to a
+new column.''
 

### 2021-02-14 paper.tex
add two figures to the paper
Added screenshots and descriptions for pdf version, outputing index.html vs paper.html and both paper.pdf and index.pdf. need to figure out why pdy-only divs are getting rendered in html

--- 2021-02-13 paper.tex
@@
 \documentclass[sigconf,10pt]{acmart}
-
-\usepackage{color}
-\usepackage{fancyvrb}
-\newcommand{\VerbBar}{|}
-\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
-\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
-% Add ',fontsize=\small' for more characters per line
-\newenvironment{Shaded}{}{}
-\newcommand{\AlertTok}[1]{\textcolor[rgb]{1.00,0.00,0.00}{\textbf{#1}}}
-\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.38,0.63,0.69}{\textbf{\textit{#1}}}}
-\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.49,0.56,0.16}{#1}}
-\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.25,0.63,0.44}{#1}}
-\newcommand{\BuiltInTok}[1]{#1}
-\newcommand{\CharTok}[1]{\textcolor[rgb]{0.25,0.44,0.63}{#1}}
-\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.38,0.63,0.69}{\textit{#1}}}
-\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.38,0.63,0.69}{\textbf{\textit{#1}}}}
-\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.53,0.00,0.00}{#1}}
-\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.00,0.44,0.13}{\textbf{#1}}}
-\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.56,0.13,0.00}{#1}}
-\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.25,0.63,0.44}{#1}}
-\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.73,0.13,0.13}{\textit{#1}}}
-\newcommand{\ErrorTok}[1]{\textcolor[rgb]{1.00,0.00,0.00}{\textbf{#1}}}
-\newcommand{\ExtensionTok}[1]{#1}
-\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.25,0.63,0.44}{#1}}
-\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.02,0.16,0.49}{#1}}
-\newcommand{\ImportTok}[1]{#1}
-\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.38,0.63,0.69}{\textbf{\textit{#1}}}}
-\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.00,0.44,0.13}{\textbf{#1}}}
-\newcommand{\NormalTok}[1]{#1}
-\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.40,0.40,0.40}{#1}}
-\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.00,0.44,0.13}{#1}}
-\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.74,0.48,0.00}{#1}}
-\newcommand{\RegionMarkerTok}[1]{#1}
-\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.25,0.44,0.63}{#1}}
-\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.73,0.40,0.53}{#1}}
-\newcommand{\StringTok}[1]{\textcolor[rgb]{0.25,0.44,0.63}{#1}}
-\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.10,0.09,0.49}{#1}}
-\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.25,0.44,0.63}{#1}}
-\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.38,0.63,0.69}{\textbf{\textit{#1}}}}
 
@@
 %% allowing the author to define a "short title" to be used in page headers.
-\title{End-user Web Scraping For Customization}
+\title{Towards End-user Web Scraping For Customization}
 
@@
   this malleability is only accessible to programmers with knowledge of
-  HTML, CSS, Javascript and the DOM. To broaden access to customization,
-  our prior work developed an approach that empowers end-users to
-  customize websites without traditional programming via a browser
-  extension called Wildcard. Wildcard's customizations are powered by
-  web scraping adapters which are currently written in Javascript by
-  programmers. This means that end-users can only customize a website if
-  a programmer has written an adapter for it. Furthermore, end-users do
-  not have the ability to extend adapters in order to perform new
-  customizations or repair adapters to fix broken customizations.
+  HTML and Javascript. To broaden access to customization, our prior
+  work developed an approach that empowers end-users to customize
+  websites without traditional programming via a browser extension
+  called Wildcard. However, Wildcard only opened part of the
+  customization process to end-users, and still required programmers to
+  write site-specific adapters to map website data to a table structure.
+  This means that end-users can only customize a website if a programmer
+  has written an adapter for it. Furthermore, end-users do not have the
+  ability to extend adapters in order to perform new customizations or
+  repair adapters to fix broken customizations.
 
@@
 specifies how to scrape the website content and set up a bidirectional
-synchronization with Wildcard's table view. Take Alice, an end-user who
-uses Wildcard to customize her experience on Google Scholar as shown
-above. Wildcard's sorting customization gives her the power to sort
-publications by title which the website does not natively allow. She
-thinks this will be useful on Weather.com to sort the ten day forecast
-by the weather descriptions so that she can quickly find all the sunny
-days. Unfortunately, a programmer has not coded an adapter for
-Weather.com so Alice is unable to customize it. Additionally, if the
-adapter for Google Scholar stops functioning when the website changes,
-Alice has no recourse to repair it on her own.
+synchronization with Wildcard's table view. Even though programmers can
+share adapters with end-users, this means that an end-user can only use
+Wildcard on websites where some programmer has already written an
+adapter. Additionally, if an adapter doesn't scrape the desired data, or
+stops functioning correctly when a website changes, an end-user has no
+recourse to extend or repair it on their own.
+
+\begin{figure*}
+  \includegraphics[width=\textwidth]{media/overview.png}
+  \caption{\label{fig:overview}Our work enables end-users to create Wildcard site adapters by demonstration.}
+\end{figure*}
 
@@
 demonstration within the browser. Using this scraping system, an
-end-user can perform end-to-end web customizations using Wildcard on
-arbitrary websites, without ever needing to code an adapter. Through a
-series of examples, we show that end-users can utilize our system to
-successfully create Wildcard adapters on a variety of websites via
-demonstration (Section~\ref{sec:demos}). We also describe key aspects of
-our system and how web scraping for customization reveals a constraint
-that simplifies the \emph{wrapper induction} \citep{kushmerick2000} task
-used to generalize user demonstrations
-(Section~\ref{sec:implementation}).
+end-user can perform web customizations using Wildcard on arbitrary
+websites, without ever needing to code an adapter. Through a series of
+examples, we show that our system can create Wildcard adapters on a
+variety of websites via demonstration (Section~\ref{sec:demos}). We also
+describe key aspects of our system and how web scraping for
+customization leads to a constraint that simplifies the \emph{wrapper
+induction} \citep{kushmerick2000} task used to generalize user
+demonstrations (Section~\ref{sec:implementation}).
 
@@
 In this section, we show how end-users can create, extend and repair
-adapters for Wildcard via demonstration.
+adapters for Wildcard via demonstration.{ These demos are best viewed as
+videos in the online version of this paper
+(\url{https://kapaya.github.io/px21}).}
 
@@
 
-Alice, our end-user from Section~\ref{sec:introduction}, wants to
-customize her experience on Weather.com by sorting the ten-day forecast
-based on the description of the weather on each day, allowing her to
-easily view all the sunny days. She starts the adapter creation process
-by clicking a context menu item within the Weather.com page, and hovers
-over a data value she might like to scrape.
+Jen wants to customize her experience on Weather.com by sorting the
+ten-day forecast based on the description of the weather on each day,
+allowing her to easily view all the sunny days. She starts the adapter
+creation process by clicking a context menu item within the Weather.com
+page, and hovers over a data value she might like to scrape.
 
-The system provides live feedback as Alice hovers, demonstrating the
-\textbf{live programming} principle:
+\begin{figure*}
+  \includegraphics[width=\textwidth]{media/creating.png}
+  \caption{\label{fig:creating} Creating an adapter: 1) column data will be scraped into, 2) system's controls, 3) demonstrated column value and row from which colums should be demonstrated from 4) column values determined by generalization algorithm 5) column values populated in table, 6) next column to scrape data into and 7) button to save adapter created by demonstration}
+\end{figure*}
 
@@
   The selected row of data is annotated in the page with a border, to
-  indicate that she will be demonstrating values from within that row.
+  indicate that she will be demonstrating values from within that row (1
+  in Figure~\ref{fig:creating}).
 \item
@@
   background, to show how the system has generalized her demonstration
-  across all the rows in the data.
+  across all the rows in the data (3 \& 4 in Figure~\ref{fig:creating}).
 \item
   A table view appears at the bottom of the screen, and displays how the
-  values will appear in the data table.
+  values will appear in the data table (5 in Figure~\ref{fig:creating}).
 \end{itemize}
 
-Alice tries hovering over several other elements in the page, taking
+Jen tries hovering over several other elements in the page, taking
 advantage of the live feedback environment to decide what data would be
@@
 page indicates which column corresponds to the previously scraped data.
-Finally, she ends the adapter creation process and is able to
-immediately sort the forecast by the weather description column, because
-Wildcard provides a \textbf{unified environment} that combines both
-scraping and customizing:
+Finally, she ends the adapter creation process (7 in
+Figure~\ref{fig:creating}) and is able to immediately sort the forecast
+by the weather description column, because Wildcard provides a
+\textbf{unified environment} that combines both scraping and
+customizing.
 
@@
 
-Alice has previously used Wildcard to customize timeanddate.com. In
-addition to sorting the list of holidays in a year by the day of the
-week, she also wants to sort them by category so she can view all the
-federal holidays together. Previously, she would have needed to find a
-programmer to help her edit the adapter code to incorporate this
-additional data, but using our system's support for \textbf{editing by
-demonstration}, Alice can extend the adapter herself.
+Jen uses Wildcard on timeanddate.com as can be seen from 1 in
+Figure~\ref{fig:extending}. In addition to sorting the list of holidays
+in a year by the day of the week, she also wants to sort them by
+category so she can view all the federal holidays together. Previously,
+she would have needed to find a programmer to help her edit the adapter
+code to incorporate this additional data, but using our system's support
+for \textbf{editing by demonstration}, Jen can extend the adapter
+herself.
 
-While viewing the website, she clicks the ``Edit Adapter'' button above
-the Wildcard table to initiate the adapter editing process. As she
-hovers over the currently scraped values, the columns they belong to are
-highlighted. Finally, she clicks on ``Federal Holiday'' to add the new
-column of data and saves the changes. Alice then proceeds to sort the
-list by the type of holiday without the intervention of a programmer.
+\begin{figure*}
+  \includegraphics[width=\textwidth]{media/extending.png}
+  \caption{\label{fig:extending} Extending an adapter: 1) table showing current columns and rows, 2) button for initiating adapter extension process, 3) new column value demonstrated and generalized, 4) new column values in the table and 5) button to save adapter extended by demonstration.}
+\end{figure*}
+
+While viewing the website, she clicks the ``Edit Adapter'' button (2 in
+Figure~\ref{fig:extending}) above the Wildcard table to initiate the
+adapter editing process. As she hovers over the currently scraped
+values, the columns they belong to are highlighted. Finally, she clicks
+on ``Federal Holiday'' (3 in Figure~\ref{fig:extending}) to add the new
+column of data to the table (4 in Figure~\ref{fig:extending}) and saves
+the changes (5 in Figure~\ref{fig:extending}). Jen then proceeds to sort
+the list by the type of holiday without the intervention of a
+programmer.
 
@@
 
-Alice next visits Google Scholar to look up references for her thesis
+Jen next visits Google Scholar to look up references for her thesis
 project. Unfortunately, the customization she had applied to sort
@@
 Scholar) is no longer working. In fact, the column in the Wildcard table
-that contained all the publication titles is empty, because the
-website's internals changed and broke the adapter's scraping logic.
-Alice can repair this on her own, again taking advantage of
-\textbf{editing by demonstration}.
+that contained all the publication titles is empty (1 in
+Figure~\ref{fig:repairing}), because the website's internals changed and
+broke the adapter's scraping logic. Jen can repair this on her own,
+again taking advantage of \textbf{editing by demonstration}.
 
-Alice initiates the editing process, and initially hovers over the
-desired value to demonstrate the column she wants to scrape. However,
-the \textbf{live programming} interface indicates to her that the values
-would be populated into column D; instead, she wants the values to be
-inserted into column A where they previously appeared. So, Alice clicks
-on the symbol for column A to indicate that she wants to scrape the
-values into that column. She then proceeds to re-apply her customization
-to the website by sorting the publications by their title without the
+Jen initiates the editing process (2 in Figure~\ref{fig:repairing}), and
+initially hovers over the desired value to demonstrate the column she
+wants to scrape. However, the \textbf{live programming} interface
+indicates to her that the values would be populated into column D;
+instead, she wants the values to be inserted into column A where they
+previously appeared. So, Jen clicks on the symbol for column A (3 in
+Figure~\ref{fig:repairing}) to indicate that she wants to scrape the
+values into that column and demonstrates the first publication title (4
+in Figure~\ref{fig:repairing}). The missing values are now back in the
+table (5 in Figure~\ref{fig:repairing}). She then proceeds to save her
+changes (6 in fig:repairing) and re-apply her customization to the
+website by sorting the publications by their title without the
 intervention of a programmer.
+
+\begin{figure*}
+  \includegraphics[width=\textwidth]{media/repairing.png}
+  \caption{\label{fig:repairing} Repairing an adapter: 1) empty column in table because website changed and adapter can no longer scrape values, 2) button for initiating adapter repair 3) column to scrape data into, 4) missing column value demonstrated and generalized, 5) missing column values back in the table and 6) button to save adapter repaired by demonstration.}
+\end{figure*}
 
@@
   We generate a single \emph{row selector} for the website: a CSS
-  selector that returns a set of DOM elements corresponding to
-  individual rows of the table.
+  selector that returns a set of Document Object Model (DOM) elements
+  corresponding to individual rows of the table.
 \item
@@
 
-\begin{Shaded}
-\begin{Highlighting}[]
-\KeywordTok{\textless{}body\textgreater{}}
-    \KeywordTok{\textless{}h1\textgreater{}}\NormalTok{ Team Iron Man }\KeywordTok{\textless{}/h1\textgreater{}}
-    \KeywordTok{\textless{}div}\OtherTok{ class=}\StringTok{’container’}\KeywordTok{\textgreater{}}
-        \KeywordTok{\textless{}div}\OtherTok{ class=}\StringTok{\textquotesingle{}avenger\textquotesingle{}}\KeywordTok{\textgreater{}}
-            \KeywordTok{\textless{}div}\OtherTok{ class=}\StringTok{\textquotesingle{}names\textquotesingle{}}\KeywordTok{\textgreater{}}
-                \KeywordTok{\textless{}span}\OtherTok{ class=}\StringTok{\textquotesingle{}super\_hero\_name\textquotesingle{}}\KeywordTok{\textgreater{}}\NormalTok{ Iron Man }\KeywordTok{\textless{}/span\textgreater{}}
-                \KeywordTok{\textless{}span}\OtherTok{ class=}\StringTok{\textquotesingle{}real\_name\textquotesingle{}}\KeywordTok{\textgreater{}}\NormalTok{ Tony Stark }\KeywordTok{\textless{}/span\textgreater{}}
-            \KeywordTok{\textless{}/div\textgreater{}}
-           \KeywordTok{\textless{}span}\OtherTok{ class=}\StringTok{’gender’}\KeywordTok{\textgreater{}}\NormalTok{ Male }\KeywordTok{\textless{}/span\textgreater{}}
-        \KeywordTok{\textless{}/div\textgreater{}}
-        \KeywordTok{\textless{}div}\OtherTok{ class=}\StringTok{\textquotesingle{}avenger\textquotesingle{}}\KeywordTok{\textgreater{}}
-            \KeywordTok{\textless{}div}\OtherTok{ class=}\StringTok{\textquotesingle{}names\textquotesingle{}}\KeywordTok{\textgreater{}}
-                \KeywordTok{\textless{}span}\OtherTok{ class=}\StringTok{\textquotesingle{}super\_hero\_name\textquotesingle{}}\KeywordTok{\textgreater{}}\NormalTok{  Black Widow }\KeywordTok{\textless{}/span\textgreater{}}
-                \KeywordTok{\textless{}span}\OtherTok{ class=}\StringTok{\textquotesingle{}real\_name\textquotesingle{}}\KeywordTok{\textgreater{}}\NormalTok{ Natalia Romanoff }\KeywordTok{\textless{}/span\textgreater{}}
-            \KeywordTok{\textless{}/div\textgreater{}}
-            \KeywordTok{\textless{}span}\OtherTok{ class=}\StringTok{’gender’}\KeywordTok{\textgreater{}}\NormalTok{ Female }\KeywordTok{\textless{}/span\textgreater{}}
-        \KeywordTok{\textless{}/div\textgreater{}}
-\NormalTok{        ...}
-    \KeywordTok{\textless{}/div\textgreater{}}
-\KeywordTok{\textless{}/body\textgreater{}}
-\end{Highlighting}
-\end{Shaded}
+\begin{figure*}
+  \includegraphics[width=\textwidth]{media/algorithm.png}
+  \caption{\label{fig:algorithm}Our system applies a heuristic to identify DOM elements that correspond to rows in the data table.}
+\end{figure*}
 
-The user performs a demonstration by clicking on the SPAN element
-containing ``Tony Stark.'' Our algorithm traverses upwards from the
-demonstrated element, considering each successive parent element as a
-potential candidate for the row element. For each parent element \(n\),
-the process is as follows:
+The user performs a demonstration by clicking on element (a) in
+Figure~\ref{fig:algorithm} containing ``Tony Stark.'' Our algorithm
+traverses upwards from the demonstrated element, considering each
+successive parent element ((b1), (c1) and (d) in
+Figure~\ref{fig:algorithm}) as a potential candidate for the row
+element. For each parent element \(n\), the process is as follows:
 
@@
 \item
-  compute a selector \(s\) that when executed on \(n\) only returns the
-  demonstrated element
+  compute a column selector \(s\) that when executed on \(n\) only
+  returns the demonstrated element
 \item
@@
 
-Notice how the row-sibling constraint simplifies the problem: row
+Notice how the \emph{row-sibling constraint} simplifies the problem: row
 candidates without siblings that return an element after \(s\) is
-executed on them have \(n_{siblings}\) = 0, thus disqualifying them.
-Furthermore, a candidate element \(n\) is only accepted as the row
-element if the row selector associated with it only matches itself and
-elements that are its direct siblings.
+executed on them ((b1) in Figure~\ref{fig:algorithm}) have
+\(n_{siblings}\) = 0, thus disqualifying them. Furthermore, a candidate
+element \(n\) is only accepted as the row element if the row selector
+\(n_{selector}\) associated with it only matches itself and elements
+that are its direct siblings.
 
-From the parent of the initial SPAN element, the algorithm moves up the
-DOM tree until it reaches the BODY element. Then, it generates a
-selector for each \(n\) and discards any \(n\) with a selector that
-matches elements that are either not itself or a direct sibling.
-Finally, the algorithm picks an \(n\) with the largest, positive
-\(n_{siblings}\), preferring nodes lower in the tree as a tiebreaker.
-\(s\) is used as the selector for the column.
-
-Applying this to our example, if the user clicks on the SPAN element
-containing ``Tony Stark,'' , the first parent element is the DIV with
-the class \emph{names}This DIV has a sibling SPAN element, but the
-sibling doesn't return an element when \emph{.super\_hero}, the selector
-that identifies the initial SPAN in the DIV, is executed on it. As a
-result, it has \(n_{siblings}\) = 0. At the level above that, we
-consider the DIV with class \emph{avenger}, which has at least one
-sibling that returns an element when the selector \emph{.super\_hero} is
-executed on it. Finally, the level above that once again has no siblings
-that return an element when the selector \emph{.super\_hero} is executed
-on them. Therefore, our algorithm returns the DIV element and outputs
-\emph{.avenger} as the row selector and \emph{.super\_hero} as the
-column selector. These selectors are used to generate a DOM scraping
-adapter which returns the DOM elements corresponding to a superhero data
-row in the table.
+The algorithm stops traversing upwards once it reaches the BODY element.
+Then, it generates a selector \(n_{selector}\) for each \(n\) and
+discards any \(n\) with an \(n_{selector}\) that matches elements that
+are either not itself or a direct sibling. Finally, the algorithm picks
+an \(n\) with the largest, positive \(n_{siblings}\), preferring nodes
+lower in the tree as a tiebreaker. \(n_{selector}\) is used as the
+selector for the row and \(s\) is used as the selector for the column.
+The row and column selectors are used to generate a scraping adapter
+which returns the DOM elements corresponding to a superhero data row in
+the table and sets up the bidirectional synchronization.
 
@@
 may not represent data on the website that should be related as part of
-the same table by customizations such as sorting and filtering. Take the
-following sample HTML layout showing two tables of superheros (Team Iron
-Man and Team Captain America):
+the same table by customizations such as sorting and filtering.
 
-\begin{Shaded}
-\begin{Highlighting}[]
-\KeywordTok{\textless{}body\textgreater{}}
-  \KeywordTok{\textless{}h1\textgreater{}}\NormalTok{ Team Iron Man }\KeywordTok{\textless{}/h1\textgreater{}}
-  \KeywordTok{\textless{}div}\OtherTok{ class=}\StringTok{’container’}\KeywordTok{\textgreater{}}
-      \KeywordTok{\textless{}div}\OtherTok{ class=}\StringTok{\textquotesingle{}avenger\textquotesingle{}}\KeywordTok{\textgreater{}}
-          \KeywordTok{\textless{}span}\OtherTok{ class=}\StringTok{\textquotesingle{}super\_hero\_name\textquotesingle{}}\KeywordTok{\textgreater{}}\NormalTok{ Iron Man }\KeywordTok{\textless{}/span\textgreater{}}
-      \KeywordTok{\textless{}/div\textgreater{}}
-      \KeywordTok{\textless{}div}\OtherTok{ class=}\StringTok{\textquotesingle{}avenger\textquotesingle{}}\KeywordTok{\textgreater{}}
-          \KeywordTok{\textless{}span}\OtherTok{ class=}\StringTok{\textquotesingle{}super\_hero\_name\textquotesingle{}}\KeywordTok{\textgreater{}}\NormalTok{  Black Widow }\KeywordTok{\textless{}/span\textgreater{}}
-      \KeywordTok{\textless{}/div\textgreater{}}
-\NormalTok{      ...}
-  \KeywordTok{\textless{}/div\textgreater{}}
-  \KeywordTok{\textless{}h1\textgreater{}}\NormalTok{ Team Captain America }\KeywordTok{\textless{}/h1\textgreater{}}
-  \KeywordTok{\textless{}div\textgreater{}}
-      \KeywordTok{\textless{}div}\OtherTok{ class=}\StringTok{\textquotesingle{}avenger\textquotesingle{}}\KeywordTok{\textgreater{}}
-          \KeywordTok{\textless{}span}\OtherTok{ class=}\StringTok{\textquotesingle{}super\_hero\_name\textquotesingle{}}\KeywordTok{\textgreater{}}\NormalTok{ Captain America }\KeywordTok{\textless{}/span\textgreater{}}
-      \KeywordTok{\textless{}/div\textgreater{}}
-      \KeywordTok{\textless{}div}\OtherTok{ class=}\StringTok{\textquotesingle{}avenger\textquotesingle{}}\KeywordTok{\textgreater{}}
-          \KeywordTok{\textless{}span}\OtherTok{ class=}\StringTok{\textquotesingle{}super\_hero\_name\textquotesingle{}}\KeywordTok{\textgreater{}}\NormalTok{  Scarlet Witch }\KeywordTok{\textless{}/span\textgreater{}}
-      \KeywordTok{\textless{}/div\textgreater{}}
-\NormalTok{      ...}
-  \KeywordTok{\textless{}/div\textgreater{}}
-\KeywordTok{\textless{}/body\textgreater{}}
-\end{Highlighting}
-\end{Shaded}
+\begin{figure*}
+  \includegraphics[width=\textwidth]{media/limitations.png}
+  \caption{\label{fig:limitations} Our generalization algorithm cannot generalize on websites with the shown layouts.
+The elements with the blue border correspond to rows of the data in each layout respectively.}
+\end{figure*}
 
-Without the constraint that row elements have to be direct siblings, the
-row generalization algorithm could determine the row selector to be
-\emph{.avenger} because it matches the largest number of parallel
-structures (has the largest \(n_{siblings}\)). While this may be the
-correct result for the task of extraction, it is not for the task of
-customization. The selector matches all rows across the two tables so
-the sorting and filtering customizations could place rows in the
-incorrect table and thereby distort what the tables represent. Because
-of this, our system currently does not support such DOM structures but
-we plan to explore the possibility of extracting multiple tables from a
-website and joining them.
+For \emph{Generalization Limitation 1} shown in
+Figure~\ref{fig:limitations}, without the constraint that row elements
+have to be direct siblings, the row generalization algorithm could
+determine the row selector to be \emph{.avenger} (elements with blue
+border in Figure~\ref{fig:limitations}) because it matches the largest
+number of parallel structures (has the largest \(n_{siblings}\)). While
+this may be the correct result for the task of extraction, it is not for
+the task of customization. The selector matches all rows across the two
+tables so the sorting and filtering customizations could place rows in
+the incorrect table and thereby distort what the tables represent.
+Because of this, our system currently does not support such DOM
+structures but we plan to explore the possibility of extracting multiple
+tables from a website and joining them.
 
-Another structure that our system cannot currently generalize over is
-one in which column elements are not contained within a row element that
-is a direct sibling of all the other row elements. Take the following
-sample HTML layout showing a table of superheros:
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\KeywordTok{\textless{}body\textgreater{}}
-  \KeywordTok{\textless{}h1}\OtherTok{ class=}\StringTok{\textquotesingle{}super\_hero\_name\textquotesingle{}}\KeywordTok{\textgreater{}}\NormalTok{ Iron Man }\KeywordTok{\textless{}/h1\textgreater{}}
-  \KeywordTok{\textless{}span}\OtherTok{ class=}\StringTok{\textquotesingle{}real\_name\textquotesingle{}}\KeywordTok{\textgreater{}}\NormalTok{ Real Name: Tony Stark }\KeywordTok{\textless{}/span\textgreater{}}
-  \KeywordTok{\textless{}h1}\OtherTok{ class=}\StringTok{\textquotesingle{}super\_hero\_name\textquotesingle{}}\KeywordTok{\textgreater{}}\NormalTok{ Captain America }\KeywordTok{\textless{}/h1\textgreater{}}
-  \KeywordTok{\textless{}span}\OtherTok{ class=}\StringTok{\textquotesingle{}real\_name\textquotesingle{}}\KeywordTok{\textgreater{}}\NormalTok{ Real Name: Steven Rogers }\KeywordTok{\textless{}/span\textgreater{}}
-  \KeywordTok{\textless{}h1}\OtherTok{ class=}\StringTok{\textquotesingle{}super\_hero\_name\textquotesingle{}}\KeywordTok{\textgreater{}}\NormalTok{ Black Widow }\KeywordTok{\textless{}/h1\textgreater{}}
-  \KeywordTok{\textless{}span}\OtherTok{ class=}\StringTok{\textquotesingle{}real\_name\textquotesingle{}}\KeywordTok{\textgreater{}}\NormalTok{ Real Name: Natalia Romanoff }\KeywordTok{\textless{}/span\textgreater{}}
-\NormalTok{  ...}
-\KeywordTok{\textless{}/body\textgreater{}}
-\end{Highlighting}
-\end{Shaded}
-
-This page contains one table of data in which rows are made up of an H1
-tag (super hero name) and a SPAN tag (real name). For the task of
+For \emph{Generalization Limitation 2} shown in
+Figure~\ref{fig:limitations}, website contains one table of data in
+which rows are made up of the alternating H1 and SPAN tags (elements
+with blue border in Figure~\ref{fig:limitations}). For the task of
 extraction, the DOM elements can be scraped using the shown classes to
@@
 adapters would need to switch into an IDE to write code as part of
-customizing a new website, making it a much less unified environment.
+customizing a new website.
 
@@
 often happens in different environments. The creators of Wrex
-\citep{drosos2020}, a programming-by-example system for data wrangling,
-reported that ``although data scientists were aware of and appreciated
-the productivity benefits of existing data wrangling tools, having to
-leave their native notebook environment to perform wrangling limited the
-usefulness of these tools.'' In web scraping, if a user comes across an
-omission while working with data scraped from a website, they need to
-switch from the environment in which they are using the data to the
-environment in which they wrote their scraping code in order to edit and
-re-run it. Sometimes, the divide is more subtle. Vegemite
-\citep{lin2009}, a system for end-user programming of mashups, had
-separate steps for scraping data from a website and augmenting that data
-via automation tasks. During a user study, participants reported that
-``it was confusing to use one technique to create the initial table, and
-another technique to add information to a new column.''
+\citep{drosos2020}, an end-user programming-by-example system for data
+wrangling, reported that ``although data scientists were aware of and
+appreciated the productivity benefits of existing data wrangling tools,
+having to leave their native notebook environment to perform wrangling
+limited the usefulness of these tools.'' This was a major reason Wrex
+was developed as an add-on to Jupyter notebooks, the environment in
+which data scientists use their data. In web scraping, if a user comes
+across an omission while working with data scraped from a website, they
+need to switch from the environment in which they are using the data to
+the environment in which they wrote their scraping code in order to edit
+and re-run it. In web customization, Vegemite \citep{lin2009}, a system
+for end-user programming of mashups, reported that participants of its
+user study thought ``it was confusing to use one technique to create the
+initial table, and another technique to add information to a new
+column.'' This hints at the need for a unified environment and a unified
+workflow.
 
-In this work, we have combined scraping and customization into a unified
-activity within a single environment. The goal is to minimize the
+In this work, we have combined scraping and customization into a single,
+unified environment with a unified workflow. The goal is to minimize the
 environment switch between \emph{extracting} the data and \emph{using}
-the data. A user might start out by scraping some data, and then switch
-to customizing the website using the results. Then, they might realize
-they need more data to perform their desired task, at which point they
-can easily augment the adapter by demonstrating new columns. All of
-these tasks take place right in the browser, where the user was
-initially already using the website. Instead of bringing the data to
-another tool, we have brought a tool to the data. This directly relates
-to the idea of ``in-place toolchains'' \citep{zotero-60} being an
-integral part of end-user programming systems.
+the data. A user might start out by scraping some data on a website, and
+then switch to customizing the website using the results. Then, they
+might realize they need more data to perform their desired task, at
+which point they can easily extend the adapter by demonstrating new
+columns. All of these tasks take place right in the browser, where the
+user was initially already using the website. Instead of bringing the
+data to another tool, we have brought a tool to the data. This directly
+relates to the idea of ``in-place toolchains'' \citep{zotero-60} being
+an integral part of end-user programming systems.
 
@@
 
-Unlike text-based commands which are only valid when complete (e.g
+Unlike text-based commands which are only valid once complete (e.g
 \texttt{SELECT\ *\ FRO} versus \texttt{SELECT\ *\ FROM\ user\_table}),
@@
 by examples. FlashProg's interface provides immediate visual feedback
-about the generalization and scrapes the matched values in an output
+about the generalization and scrapes the matched values into an output
 tab. In addition, it has a program viewer tab that contains a high level
@@
 
-Roussillon \citep{chasins2018} is a tool that enables end-users to
-scrape distributed, hierarchical web data. Its interface does not
-provide \emph{full} live feedback about its generalizations or the
-values to be scrapped until all the demonstrations have been provided
-and the generated program has been run. If run on a website it has
-encountered before, Roussillon makes all the previously determined
-generalizations visible to the user by color-coding the values on the
-website that belong to the same column. This is a desirable feature for
-our system as users will not have to actively explore in order to
-discover which values are available for scraping and how they are
-related to each other. On the extension and repair front, Roussillon
-presents the web scraping code generated by demonstration as an
-editable, high-level, block-based language called Helena
-\citep{zotero-51}. While Helena can be used to perform more complex
-editing tasks like adding control flow, it presents a change in the
-model used for creation. Our system maintains the model used for
-creation by allowing users to extend and repair web scraping code via
-demonstration.
+Rousillon \citep{chasins2018} is a tool that enables end-users to scrape
+distributed, hierarchical web data. Its interface does not provide
+\emph{full} live feedback about its generalizations or the values to be
+scrapped until all the demonstrations have been provided and the
+generated program has been run. If run on a website it has encountered
+before, Rousillon makes all the previously determined generalizations
+visible to the user by color-coding the values on the website that
+belong to the same column. This is a desirable feature for our system as
+users will not have to actively explore in order to discover which
+values are available for scraping and how they are related to each
+other. On the extension and repair front, Rousillon presents the web
+scraping code generated by demonstration as an editable, high-level,
+block-based language called Helena \citep{zotero-51}. While Helena can
+be used to perform more complex editing tasks like adding control flow,
+it presents a change in the model used for creation. Our system
+maintains the model used for creation by allowing users to extend and
+repair web scraping code via demonstration.
 
@@
 Wildcard, it uses web scraping to extract data from websites in order to
-enable customizations (sorting and filtering). It performs the web
-scraping automatically using a variety of heuristics and solicits
-guidance from the user if this fails. While automatic web scraping seems
-desirable, it is unclear how useful it is if the goal is customization.
-Given a row with ten scrapable values, and therefore ten columns, would
-a user prefer to simply demonstrate the value for the single column they
-are interested in or un-demonstrate the nine values they are not
-interested in? This is a question we can only answer after performing a
-user study.
+enable customizations (sorting and filtering). Unlike Wildcard, it does
+not support adding annotations to websites and running computations on
+the scraped data using a spreadsheet formula language. Both of these
+significantly expand the types of customizations end-users can make to
+websites. Sifter performs the web scraping automatically using a variety
+of heuristics and solicits guidance from the user if this fails. While
+automatic web scraping seems desirable, it is unclear how useful it is
+if the goal is customization. Given a row with ten scrapable values, and
+therefore ten columns, would a user prefer to simply demonstrate the
+value for the single column they are interested in or un-demonstrate the
+nine values they are not interested in? This is a question we can only
+answer after performing a user study.
 
@@
 To assess our design principles, we plan to carry out a broader
-evaluation of our system through a user study. Furthermore, we plan to
-incorporate the program viewer and disambiguation features of FlashProg
-\citep{mayer2015} to give users more insight and control into the
-generalization process.
+evaluation of our system through a user study. So far, we have only
+tested the system amongst overselves and a small number of collegues.
+More testing is needed to understand whether it can be succussfully used
+among a broader set set of users across a wider variety of websites.
+Furthermore, we plan to incorporate the program viewer and
+disambiguation features of FlashProg \citep{mayer2015} to give users
+more insight and control into the generalization process.
 

### 2021-02-14 compile-html.sh

@@ -6,7 +6,7 @@ set -e
   --metadata=format:html \
   -s \
   --number-sections \
-  -o paper.html \
+  -o index.html \
   --css basic.css \
   --toc \
   --toc-depth=1 \

### 2021-02-14 compile-latex.sh

@@ -16,4 +16,4 @@ pdflatex paper.tex
 bibtex paper
 pdflatex -interaction=batchmode paper.tex
 pdflatex -interaction=batchmode paper.tex
-open paper.pdf
+cp paper.pdf index.pdf

### 2021-02-14 watch.sh
fix watch command

@@ -4,7 +4,7 @@ set -e
 ps aux | grep node | grep browser-sync | awk '{ print $2}' | xargs kill
 
 ls *.md | entr ./compile-html.sh &
-browser-sync start --server --files paper.html --no-notify --no-open --port 9000 &
+browser-sync start --server --files index.html --no-notify --no-open --port 9000 &
 
-open "http://localhost:9000/paper.html"
+open "http://localhost:9000/index.html"
 

### 2021-02-14 compile-html.sh
fix conditional rendering

@@ -2,6 +2,7 @@ set -e
 
  pandoc \
   --filter pandoc-crossref \
+  --filter conditional-render \
   --citeproc \
   --metadata=format:html \
   -s \

### 2021-02-14 paper.tex
update references to demo figures

@@
 
+The workflow steps are shown in Figure~\ref{fig:creating}:
+
 \begin{itemize}
@@
   The selected row of data is annotated in the page with a border, to
-  indicate that she will be demonstrating values from within that row (1
-  in Figure~\ref{fig:creating}).
+  indicate that she will be demonstrating values from within that row
+  (Part 1).
 \item
@@
   background, to show how the system has generalized her demonstration
-  across all the rows in the data (3 \& 4 in Figure~\ref{fig:creating}).
+  across all the rows in the data (Part 3 and 4).
 \item
   A table view appears at the bottom of the screen, and displays how the
-  values will appear in the data table (5 in Figure~\ref{fig:creating}).
+  values will appear in the data table (Part 5).
 \end{itemize}
@@
 page indicates which column corresponds to the previously scraped data.
-Finally, she ends the adapter creation process (7 in
-Figure~\ref{fig:creating}) and is able to immediately sort the forecast
-by the weather description column, because Wildcard provides a
-\textbf{unified environment} that combines both scraping and
-customizing.
+Finally, she ends the adapter creation process (Part 7) and is able to
+immediately sort the forecast by the weather description column, because
+Wildcard provides a \textbf{unified environment} that combines both
+scraping and customizing.
 
@@
 
-Jen uses Wildcard on timeanddate.com as can be seen from 1 in
-Figure~\ref{fig:extending}. In addition to sorting the list of holidays
-in a year by the day of the week, she also wants to sort them by
-category so she can view all the federal holidays together. Previously,
-she would have needed to find a programmer to help her edit the adapter
-code to incorporate this additional data, but using our system's support
-for \textbf{editing by demonstration}, Jen can extend the adapter
-herself.
+Jen uses Wildcard on timeanddate.com. In addition to sorting the list of
+holidays in a year by the day of the week, she also wants to sort them
+by category so she can view all the federal holidays together.
+Previously, she would have needed to find a programmer to help her edit
+the adapter code to incorporate this additional data, but using our
+system's support for \textbf{editing by demonstration}, Jen can extend
+the adapter herself.
 
@@
 
-While viewing the website, she clicks the ``Edit Adapter'' button (2 in
-Figure~\ref{fig:extending}) above the Wildcard table to initiate the
-adapter editing process. As she hovers over the currently scraped
-values, the columns they belong to are highlighted. Finally, she clicks
-on ``Federal Holiday'' (3 in Figure~\ref{fig:extending}) to add the new
-column of data to the table (4 in Figure~\ref{fig:extending}) and saves
-the changes (5 in Figure~\ref{fig:extending}). Jen then proceeds to sort
-the list by the type of holiday without the intervention of a
-programmer.
+The workflow is shown in Figure~\ref{fig:extending}. While viewing the
+website, she clicks the ``Edit Adapter'' button (Part 2) above the
+Wildcard table to initiate the adapter editing process. As she hovers
+over the currently scraped values, the columns they belong to are
+highlighted. Finally, she clicks on ``Federal Holiday'' (Part 3) to add
+the new column of data to the table (Part 4) and saves the changes (Part
+5). Jen then proceeds to sort the list by the type of holiday without
+the intervention of a programmer.
 
@@
 Scholar) is no longer working. In fact, the column in the Wildcard table
-that contained all the publication titles is empty (1 in
-Figure~\ref{fig:repairing}), because the website's internals changed and
-broke the adapter's scraping logic. Jen can repair this on her own,
-again taking advantage of \textbf{editing by demonstration}.
+that contained all the publication titles is empty, because the
+website's internals changed and broke the adapter's scraping logic. Jen
+can repair this on her own, again taking advantage of \textbf{editing by
+demonstration}.
 
-Jen initiates the editing process (2 in Figure~\ref{fig:repairing}), and
-initially hovers over the desired value to demonstrate the column she
-wants to scrape. However, the \textbf{live programming} interface
-indicates to her that the values would be populated into column D;
-instead, she wants the values to be inserted into column A where they
-previously appeared. So, Jen clicks on the symbol for column A (3 in
-Figure~\ref{fig:repairing}) to indicate that she wants to scrape the
-values into that column and demonstrates the first publication title (4
-in Figure~\ref{fig:repairing}). The missing values are now back in the
-table (5 in Figure~\ref{fig:repairing}). She then proceeds to save her
-changes (6 in fig:repairing) and re-apply her customization to the
-website by sorting the publications by their title without the
-intervention of a programmer.
+The workflow is shown in Figure~\ref{fig:repairing}. Jen initiates the
+editing process (Part 2), and initially hovers over the desired value to
+demonstrate the column she wants to scrape. However, the \textbf{live
+programming} interface indicates to her that the values would be
+populated into column D; instead, she wants the values to be inserted
+into column A where they previously appeared. So, Jen clicks on the
+symbol for column A (Part 3) to indicate that she wants to scrape the
+values into that column and demonstrates the first publication title
+(Part 4). The missing values are now back in the table (Part 5). She
+then proceeds to save her changes (Part 6) and re-apply her
+customization to the website by sorting the publications by their title
+without the intervention of a programmer.
 

### 2021-02-14 paper.tex
Added references to commercial scraping tools

--- 2021-02-14 paper.tex
@@
 need to switch from the environment in which they are using the data to
-the environment in which they wrote their scraping code in order to edit
-and re-run it. In web customization, Vegemite \citep{lin2009}, a system
-for end-user programming of mashups, reported that participants of its
-user study thought ``it was confusing to use one technique to create the
-initial table, and another technique to add information to a new
-column.'' This hints at the need for a unified environment and a unified
-workflow.
+the environment in which they created their scraping code in order to
+edit and re-run it. This can be seen in many end-user web scraping
+systems like Rousillon \citep{chasins2018} and commercial tools like
+import.io \citep{zotero-77}, dexi.io \citep{dexi.io}, Octoparse
+\citep{zotero-83} and ParseHub \citep{zotero-86}. In web customization,
+the creators of Vegemite \citep{lin2009}, a system for end-user
+programming of mashups, reported that participants of its user study
+thought ``it was confusing to use one technique to create the initial
+table, and another technique to add information to a new column.'' This
+hints at the need for both a unified environment and a unified workflow.
 
@@
 a high-level, block-based programming language called Helena
-\citep{zotero-51} which does not support providing new demonstrations to
-extend or repair the scraping code. In Vegemite \citep{lin2009}, a web
-automation program created through demonstration can only be edited by
-editing the text-based representation of the program.
+\citep{zotero-51}. Helena supports adding control flow logic
+(conditional execution, wait times etc) which is invaluable for
+automating access to websites. However, it does not support extending
+the web scraping code to add new columns after the demonstration or
+repairing it to provide new selectors if the website changes. In
+Vegemite \citep{lin2009}, a web automation program created through
+demonstration can only be edited by editing the text-based
+representation of the automtation. In fact, only the automation script
+that works on the scraped website data can be edited. If a user needs to
+add a new column or repair an exisiting one in the table, they need to
+re-demonstrate the columns and then re-run the automation script.
 
@@
 be used to perform more complex editing tasks like adding control flow,
-it presents a change in the model used for creation. Our system
+it does not support adding or repairing columns after the demonstrations
+and presents a change in the model used for creation. Our system
 maintains the model used for creation by allowing users to extend and
@@
 scraping interface does not provide live feedback about the
-generalization on hover but after a user clicks, the interface shows the
-result of the system's generalization by highlighting the all matched
-values. Furthermore, even though the interface also has a table, the
-table is only populated with the scraped values after all the
+generalization on hover but after a user clicks a value, the interface
+shows the result of the system's generalization by highlighting the all
+matched values. Furthermore, even though the interface also has a table,
+the table is only populated with the scraped values after all the
 demonstrations have been provided. The scripting interface utilizes
@@
 However, this editing does not extend to the web scraping interface used
-for demonstrations.
+for demonstrations and presents a change in the model used for creation.
 
@@
 value for the single column they are interested in or un-demonstrate the
-nine values they are not interested in? This is a question we can only
-answer after performing a user study.
+nine values they are not interested in? This automatic web scraping
+aproach can be also be seen in tools like import.io \citep{zotero-77} so
+it is certainly worth evaluating as part of a user study.
 

### 2021-02-14 paper.tex
Fixed import.io reference

@@
 add a new column or repair an exisiting one in the table, they need to
-re-demonstrate the columns and then re-run the automation script.
+re-demonstrate the columns and then re-run the automation script. One
+exception to point out is import.io {[}zotero-77{]} which allows users
+to add new columns by demonstration and delete columns and
+re-demonstrate them which could serve the purpose of repair.
 
@@
 
-In some end-user web scraping systems like Rousillon
-\citep{chasins2018}, users only get \emph{full} feedback about the
-program's execution (generalization and the scraped values) after
-providing all the demonstrations. This means they cannot adjust their
-demonstrations in response to the system's feedback as they demonstrate.
+In many programming-by-demonstration web scraping systems, users only
+get \emph{full} feedback about the program's execution (generalization
+and the scraped values) after providing all the demonstrations. This
+means they cannot adjust their demonstrations in response to the
+system's feedback as they demonstrate.
 

### 2021-02-14 paper.tex
add page numbers

@@
 \documentclass[sigconf,10pt]{acmart}
+
+\settopmatter{printfolios=true}
 
@@
 re-demonstrate the columns and then re-run the automation script. One
-exception to point out is import.io {[}zotero-77{]} which allows users
+exception to point out is import.io \citep{zotero-77} which allows users
 to add new columns by demonstration and delete columns and

### 2021-02-14 paper.tex
fix reference dates

@@
 systems like Rousillon \citep{chasins2018} and commercial tools like
-import.io \citep{zotero-77}, dexi.io \citep{dexi.io}, Octoparse
-\citep{zotero-83} and ParseHub \citep{zotero-86}. In web customization,
+import.io \citep{import.io}, dexi.io \citep{dexi.io}, Octoparse
+\citep{octoparse} and ParseHub \citep{parsehub}. In web customization,
 the creators of Vegemite \citep{lin2009}, a system for end-user

### 2021-02-14 paper.tex
edit pass of web version, added new system limitation amongst other changes

@@
   We have successfully used our system to create, extend and repair
-  adapters by demonstration on a variety of websites. We provide example
-  usage scenarios that showcase each of our design principles.
+  adapters by demonstration on a variety of websites and we provide
+  example usage scenarios that showcase each of our design principles.
 \end{abstract}
@@
 
-Notice how the \emph{row-sibling constraint} simplifies the problem: row
+Notice how the \emph{row-sibling} constraint simplifies the problem: row
 candidates without siblings that return an element after \(s\) is
@@
 determine the row selector to be \emph{.avenger} (elements with blue
-border in Figure~\ref{fig:limitations}) because it matches the largest
-number of parallel structures (has the largest \(n_{siblings}\)). While
-this may be the correct result for the task of extraction, it is not for
-the task of customization. The selector matches all rows across the two
-tables so the sorting and filtering customizations could place rows in
+border) because it matches the largest number of parallel structures
+(has the largest \(n_{siblings}\)). While this may be the correct result
+for the task of extraction, it is not for the task of customization. The
+selector matches all rows across the two tables (elements with green
+border) so the sorting and filtering customizations could place rows in
 the incorrect table and thereby distort what the tables represent.
-Because of this, our system currently does not support such DOM
-structures but we plan to explore the possibility of extracting multiple
-tables from a website and joining them.
+Because of this, our system currently does not support such layouts but
+we plan to explore the possibility of extracting multiple tables from a
+website and joining them.
 
@@
 which rows are made up of the alternating H1 and SPAN tags (elements
-with blue border in Figure~\ref{fig:limitations}). For the task of
-extraction, the DOM elements can be scraped using the shown classes to
-output a table in which the values of the H1 tags form the first column
-and the values of the SPAN tag form the second column. For the task of
-customization, our system would need to know what the row boundaries
-were in order for customizations such as sorting and filtering to work
-as expected. In Wildcard, this can be done with a hand-coded adapter by
-creating artificial row boundaries. In the above DOM structure, an
-artificial row boundary could be created by representing a row as an H1
-tag and the SPAN tag that immediately follows it. These artificial rows
-would form a single unit which would not distort the website after a
-sorting or filtering customization. We plan to explore how such
-artificial row boundaries might be created via demonstration in order to
-support these structures (which are not uncommon, and can be seen, for
-example, in HackerNews).
+with blue border). For the task of extraction, the DOM elements can be
+scraped using the shown classes to output a table in which the values of
+the H1 tags form the first column and the values of the SPAN tag form
+the second column. For the task of customization, our system would need
+to know what the row boundaries were in order for customizations such as
+sorting and filtering to work as expected. In Wildcard, this can be done
+with a hand-coded adapter by creating artificial row boundaries. In
+\emph{Generalization Limitation 2}'s layout, an artificial row boundary
+could be created by representing a row as an H1 tag and the SPAN tag
+that immediately follows it. These artificial rows would form a single
+unit which would not distort the website after a sorting or filtering
+customization. We plan to explore how such artificial row boundaries
+might be created via demonstration in order to support these structures
+(which are not uncommon, and can be seen, for example, in HackerNews).
+
+Another major limitation of our system is our current lack of support
+for scraping data loaded after the initial websites render as the user
+scrolls. Hand-coded adapters can specify event listeners on the DOM to
+re-execute the scraping code when new data is loaded as a user scrolls.
+In future work, will we provide a mechanism for end-users to specify
+when the adapter created via demonstration should re-execute its
+scraping code in response to user scrolling. There is a similar
+limitation for websites that have paged data but it is not clear how
+suitable such pages are for customization to begin with.
 
@@
 edit and re-run it. This can be seen in many end-user web scraping
-systems like Rousillon \citep{chasins2018} and commercial tools like
-import.io \citep{import.io}, dexi.io \citep{dexi.io}, Octoparse
-\citep{octoparse} and ParseHub \citep{parsehub}. In web customization,
-the creators of Vegemite \citep{lin2009}, a system for end-user
-programming of mashups, reported that participants of its user study
-thought ``it was confusing to use one technique to create the initial
-table, and another technique to add information to a new column.'' This
-hints at the need for both a unified environment and a unified workflow.
+systems like Rousillon \citep{chasins2018}and FlashExtract
+\citep{le2014} and commercial tools like import.io \citep{zotero-77},
+dexi.io \citep{dexi.io}, Octoparse \citep{zotero-83} and ParseHub
+\citep{zotero-86}. In web customization, the creators of Vegemite
+\citep{lin2009}, a system for end-user programming of mashups, reported
+that participants of its user study thought ``it was confusing to use
+one technique to create the initial table, and another technique to add
+information to a new column.'' This hints at the need for both a unified
+environment and a unified workflow.
 
@@
 demonstration can only be edited by editing the text-based
-representation of the automtation. In fact, only the automation script
-that works on the scraped website data can be edited. If a user needs to
-add a new column or repair an exisiting one in the table, they need to
-re-demonstrate the columns and then re-run the automation script. One
-exception to point out is import.io \citep{zotero-77} which allows users
-to add new columns by demonstration and delete columns and
-re-demonstrate them which could serve the purpose of repair.
+representation of the automtation demonstrations. In fact, only the
+demonstrations used to perform automations on the scraped website data
+can be edited. If a user needs to add a new column or repair an
+exisiting one in the scraped data table, they need to re-demonstrate the
+columns and then re-run the automation script. One exception to existing
+editing models worth pointing out is import.io \citep{zotero-77}. It
+allows users to add new columns by demonstration but it is not clear
+whether deleting a column and re-demonstrating it could serve the
+purpose of repair.
 
@@
 customization ecosystem. Because users interact with the scraped data
-directly in the context of the website, it is easy to initiate the
-scraping system in editing mode: the scraping system is simply booted up
-using metadata stored with the scraping adapter to the state when the
-demonstration was completed. Users that have gone through the creation
-process will immediately realize what to do in order to extend or repair
-the adapter. Users that have not gone through the creation process might
-have a harder time but we provide visual clues (such as highlighting the
-row to perform demonstrations from with a green border) and live
-programming (immediately preview the results of demonstrations) that
-serve as guides.
+through a unified environment directly in the context of the website, it
+is easy to initiate the scraping system in editing mode: the scraping
+system is simply booted up using metadata stored with the scraping
+adapter to the state when the demonstration was completed. Users that
+have gone through the creation process will immediately realize what to
+do in order to extend or repair the adapter. Users that have not gone
+through the creation process might have a harder time but we provide
+visual clues (such as highlighting the row to perform demonstrations
+from with a green border) and live programming (immediately preview the
+results of demonstrations) that serve as guides.
 
@@
 
-In many programming-by-demonstration web scraping systems, users only
-get \emph{full} feedback about the program's execution (generalization
-and the scraped values) after providing all the demonstrations. This
-means they cannot adjust their demonstrations in response to the
-system's feedback as they demonstrate.
+In many programming-by-demonstration web scraping systems
+\citep[\citet{lin2009}]{chasins2018}, users only get \emph{full}
+feedback about the program's execution (generalization and the scraped
+values) after providing \emph{all} the demonstrations. This means they
+cannot adjust their demonstrations in response to the system's feedback
+as they demonstrate.
 

### 2021-02-14 paper.tex

@@
 
+\textless\textless\textless\textless\textless\textless\textless{} HEAD
 This type of divide between tasks appears in other domains. In data
@@
 information to a new column.'' This hints at the need for both a unified
-environment and a unified workflow.
+environment and a unified workflow. ======= This type of divide between
+tasks appears in other domains. In data science, workflows revolve
+between cleaning and using data but this often happens in different
+environments. The creators of Wrex \citep{drosos2020}, an end-user
+programming-by-example system for data wrangling, reported that
+``although data scientists were aware of and appreciated the
+productivity benefits of existing data wrangling tools, having to leave
+their native notebook environment to perform wrangling limited the
+usefulness of these tools.'' This was a major reason Wrex was developed
+as an add-on to Jupyter notebooks, the environment in which data
+scientists use their data. In web scraping, if a user comes across an
+omission while working with data scraped from a website, they need to
+switch from the environment in which they are using the data to the
+environment in which they created their scraping code in order to edit
+and re-run it. This can be seen in many end-user web scraping systems
+like Rousillon \citep{chasins2018} and commercial tools like import.io
+\citep{import.io}, dexi.io \citep{dexi.io}, Octoparse \citep{octoparse}
+and ParseHub \citep{parsehub}. In web customization, the creators of
+Vegemite \citep{lin2009}, a system for end-user programming of mashups,
+reported that participants of its user study thought ``it was confusing
+to use one technique to create the initial table, and another technique
+to add information to a new column.'' This hints at the need for both a
+unified environment and a unified workflow.
+\textgreater\textgreater\textgreater\textgreater\textgreater\textgreater\textgreater{}
+dff119bf9a1215fb2847215abe2c9722e90542f1
 
@@
 programs. Though FlashProg has many desirable features we aim to
-implement in future iterations, it does not offer a unified environment
-within a browser for scraping and customizing websites.
+implement in future iterations, its implementation does not align with
+our goal to provide a unified environment within a browser for scraping
+and customizing websites.
 
 Rousillon \citep{chasins2018} is a tool that enables end-users to scrape
-distributed, hierarchical web data. Its interface does not provide
-\emph{full} live feedback about its generalizations or the values to be
-scrapped until all the demonstrations have been provided and the
-generated program has been run. If run on a website it has encountered
-before, Rousillon makes all the previously determined generalizations
-visible to the user by color-coding the values on the website that
-belong to the same column. This is a desirable feature for our system as
-users will not have to actively explore in order to discover which
-values are available for scraping and how they are related to each
-other. On the extension and repair front, Rousillon presents the web
-scraping code generated by demonstration as an editable, high-level,
-block-based language called Helena \citep{zotero-51}. While Helena can
-be used to perform more complex editing tasks like adding control flow,
-it does not support adding or repairing columns after the demonstrations
-and presents a change in the model used for creation. Our system
-maintains the model used for creation by allowing users to extend and
-repair web scraping code via demonstration.
+distributed, hierarchical web data. Because demonstrations can span
+across several websites and involve complex data access automtation
+tasks, its interface does not provide \emph{full} live feedback about
+its generalizations or the values to be scrapped until all the
+demonstrations have been provided and the generated program has been
+run. If run on a website it has encountered before, Rousillon makes all
+the previously determined generalizations visible to the user by
+color-coding the values on the website that belong to the same column.
+This is a desirable feature for our system as users will not have to
+actively explore in order to discover which values are available for
+scraping and how they are related to each other. On the extension and
+repair front, Rousillon presents the web scraping code generated by
+demonstration as an editable, high-level, block-based language called
+Helena \citep{zotero-51}. While Helena can be used to perform more
+complex editing tasks like adding control flow, it does not support
+adding or repairing columns after the demonstrations and presents a
+change in the model used for creation. Our system maintains the model
+used for creation by allowing users to extend and repair web scraping
+code via demonstration.
 
@@
 
-Like existing approaches, web scraping in our current implementation is
-limited to what can be demonstrated. This is problematic if users want
-to scrape the URL associated with a link element, which is not visible,
-or only scrape a substring of a value. To solve this, we plan to harness
-Wildcard's formula language. End-users will be able to use formulas
-targeted at web scraping to access DOM element properties and
-attributes. For example, a formula like
+Like existing programming-by-demonstration approaches, web scraping in
+our current implementation is limited to what can be demonstrated. This
+is problematic if users want to scrape the URL associated with a link
+element, which is not visible, or only scrape a substring of a value. To
+solve this, we plan to harness Wildcard's formula language. End-users
+will be able to use formulas targeted at web scraping to access DOM
+element properties and attributes. For example, a formula like
 \texttt{=GetAttribute(link\_column,\ ‘href’)} could be used to scrape

### 2021-02-14 paper.tex
Fixed typos after pasting into gdoc

--- 2021-02-14 paper.tex
@@
   \includegraphics[width=\textwidth]{media/creating.png}
-  \caption{\label{fig:creating} Creating an adapter: 1) column data will be scraped into, 2) system's controls, 3) demonstrated column value and row from which colums should be demonstrated from 4) column values determined by generalization algorithm 5) column values populated in table, 6) next column to scrape data into and 7) button to save adapter created by demonstration}
+  \caption{\label{fig:creating} Creating an adapter: 1) column data will be scraped into, 2) system's controls, 3) demonstrated column value and row from which columns should be demonstrated from 4) column values determined by generalization algorithm 5) column values populated in table, 6) next column to scrape data into and 7) button to save adapter created by demonstration}
 \end{figure*}
@@
 systems like Rousillon \citep{chasins2018}and FlashExtract
-\citep{le2014} and commercial tools like import.io \citep{zotero-77},
-dexi.io \citep{dexi.io}, Octoparse \citep{zotero-83} and ParseHub
-\citep{zotero-86}. In web customization, the creators of Vegemite
+\citep{le2014} and commercial tools like import.io \citep{import.io},
+dexi.io \citep{dexi.io}, Octoparse \citep{octoparse} and ParseHub
+\citep{parsehub}. In web customization, the creators of Vegemite
 \citep{lin2009}, a system for end-user programming of mashups, reported
@@
 data to another tool, we have brought a tool to the data. This directly
-relates to the idea of ``in-place toolchains'' \citep{zotero-60} being
+relates to the idea of ``in-place toolchains'' \citep{zotero-1362} being
 an integral part of end-user programming systems.
@@
 a high-level, block-based programming language called Helena
-\citep{zotero-51}. Helena supports adding control flow logic
+\citep{zotero-1349}. Helena supports adding control flow logic
 (conditional execution, wait times etc) which is invaluable for
@@
 demonstration can only be edited by editing the text-based
-representation of the automtation demonstrations. In fact, only the
+representation of the automation demonstrations. In fact, only the
 demonstrations used to perform automations on the scraped website data
-can be edited. If a user needs to add a new column or repair an
-exisiting one in the scraped data table, they need to re-demonstrate the
-columns and then re-run the automation script. One exception to existing
-editing models worth pointing out is import.io \citep{zotero-77}. It
-allows users to add new columns by demonstration but it is not clear
-whether deleting a column and re-demonstrating it could serve the
-purpose of repair.
+can be edited. If a user needs to add a new column or repair an existing
+one in the scraped data table, they need to re-demonstrate the columns
+and then re-run the automation script. One exception to existing editing
+models worth pointing out is import.io \citep{import.io}. It allows
+users to add new columns by demonstration but it is not clear whether
+deleting a column and re-demonstrating it could serve the purpose of
+repair.
 
@@
 end-user programming is ``interaction with a living system''
-\citep{zotero-60}.
+\citep{zotero-1362}.
 
@@
 the cursor) is the same during both hover and click (incomplete command
-verus complete command). This allows us to take a small step further by
+versus complete command). This allows us to take a small step further by
 executing a command before a user completes it, thereby providing them
@@
 programs. Though FlashProg has many desirable features we aim to
-implement in future iterations, it does not offer a unified environment
-within a browser for scraping and customizing websites.
+implement in future iterations, its implementation does not align with
+our goal to provide a unified environment within a browser for scraping
+and customizing websites.
 
 Rousillon \citep{chasins2018} is a tool that enables end-users to scrape
-distributed, hierarchical web data. Its interface does not provide
-\emph{full} live feedback about its generalizations or the values to be
-scrapped until all the demonstrations have been provided and the
-generated program has been run. If run on a website it has encountered
-before, Rousillon makes all the previously determined generalizations
-visible to the user by color-coding the values on the website that
-belong to the same column. This is a desirable feature for our system as
-users will not have to actively explore in order to discover which
-values are available for scraping and how they are related to each
-other. On the extension and repair front, Rousillon presents the web
-scraping code generated by demonstration as an editable, high-level,
-block-based language called Helena \citep{zotero-51}. While Helena can
-be used to perform more complex editing tasks like adding control flow,
-it does not support adding or repairing columns after the demonstrations
-and presents a change in the model used for creation. Our system
-maintains the model used for creation by allowing users to extend and
-repair web scraping code via demonstration.
+distributed, hierarchical web data. Because demonstrations can span
+across several websites and involve complex data access automation
+tasks, its interface does not provide \emph{full} live feedback about
+its generalizations or the values to be scrapped until all the
+demonstrations have been provided and the generated program has been
+run. If run on a website it has encountered before, Rousillon makes all
+the previously determined generalizations visible to the user by
+color-coding the values on the website that belong to the same column.
+This is a desirable feature for our system as users will not have to
+actively explore in order to discover which values are available for
+scraping and how they are related to each other. On the extension and
+repair front, Rousillon presents the web scraping code generated by
+demonstration as an editable, high-level, block-based language called
+Helena \citep{zotero-1349}. While Helena can be used to perform more
+complex editing tasks like adding control flow, it does not support
+adding or repairing columns after the demonstrations and presents a
+change in the model used for creation. Our system maintains the model
+used for creation by allowing users to extend and repair web scraping
+code via demonstration.
 
@@
 nine values they are not interested in? This automatic web scraping
-aproach can be also be seen in tools like import.io \citep{zotero-77} so
-it is certainly worth evaluating as part of a user study.
+approach can be also be seen in tools like import.io \citep{import.io}
+so it is certainly worth evaluating as part of a user study.
 
@@
 evaluation of our system through a user study. So far, we have only
-tested the system amongst overselves and a small number of collegues.
-More testing is needed to understand whether it can be succussfully used
+tested the system amongst ourselves and a small number of colleagues.
+More testing is needed to understand whether it can be successfully used
 among a broader set set of users across a wider variety of websites.

### 2021-02-14 paper.tex
Edits after pdf pass

@@
   customization process to end-users, and still required programmers to
-  write site-specific adapters to map website data to a table structure.
-  This means that end-users can only customize a website if a programmer
-  has written an adapter for it. Furthermore, end-users do not have the
-  ability to extend adapters in order to perform new customizations or
-  repair adapters to fix broken customizations.
+  write site-specific adapters to map website data to a table view
+  through which the customizations are made. This means that end-users
+  can only customize a website if a programmer has written an adapter
+  for it. Furthermore, end-users do not have the ability to extend
+  adapters in order to perform new customizations or repair adapters to
+  fix broken customizations.
 
@@
 
-The workflow steps are shown in Figure~\ref{fig:creating}:
+The system provides live feedback as Jen hovers, demonstrating the
+\textbf{live programming} principle. The workflow steps are shown in
+Figure~\ref{fig:creating}:
 
@@
   indicate that she will be demonstrating values from within that row
-  (Part 1).
+  (Part 3).
 \item

### 2021-02-14 paper.tex
edit demos and implementation

@@
 \begin{abstract}
-  Websites are malleable: users can install browser extensions and run
-  arbitrary Javascript in the developer console to change them. However,
-  this malleability is only accessible to programmers with knowledge of
-  HTML and Javascript. To broaden access to customization, our prior
-  work developed an approach that empowers end-users to customize
-  websites without traditional programming via a browser extension
-  called Wildcard. However, Wildcard only opened part of the
-  customization process to end-users, and still required programmers to
-  write site-specific adapters to map website data to a table view
-  through which the customizations are made. This means that end-users
-  can only customize a website if a programmer has written an adapter
-  for it. Furthermore, end-users do not have the ability to extend
-  adapters in order to perform new customizations or repair adapters to
-  fix broken customizations.
+  Websites are malleable: users can run code in the browser to customize
+  them. However, this malleability is typically only accessible to
+  programmers with knowledge of HTML and Javascript. Previously, we
+  developed a tool called Wildcard which empowers end-users to customize
+  websites through a data table interface without doing traditional
+  programming. However, there is a limit on end-user flexibility with
+  Wildcard, because programmers need to create site-specific adapters
+  mapping website data to a table view. This means that end-users can
+  only customize a website if a programmer has written an adapter for
+  it, and cannot extend or repair existing adapters.
 
   In this paper, we extend Wildcard with a new system for \emph{end-user
-  web scraping for customization} which enables end-users to create,
-  extend and repair adapters by demonstration. We describe three design
+  web scraping for customization}. It enables end-users to create,
+  extend and repair adapters, by performing concrete demonstrations of
+  how the webpage UI maps to a data table. We describe three design
   principles that guided our system's development and are applicable to
@@
 %% the work being presented. Separate the keywords with commas.
-\keywords{end-user programming, software customization, web browser extensions}
+\keywords{end-user programming, software customization, web scraping, programming by example}
 
@@
 Wildcard has a key limitation. In order to enable end-users to customize
-a website, a Javascript programmer first needs to code an adapter that
+a website, a programmer first needs to code a Javascript adapter that
 specifies how to scrape the website content and set up a bidirectional
@@
   and repair the programs by demonstration. This enables users to build
-  on other user's work, and is especially important in the context of
-  web scraping since programs that scrape data sometimes break as the
-  underlying website changes.
+  on other users' work, and is especially important in the context of
+  web scraping since scrapers break as the underlying website changes.
 \item
@@
   background, to show how the system has generalized her demonstration
-  across all the rows in the data (Part 3 and 4).
+  across all the rows in the data (Part 4).
 \item
@@
 
-Jen uses Wildcard on timeanddate.com. In addition to sorting the list of
-holidays in a year by the day of the week, she also wants to sort them
-by category so she can view all the federal holidays together.
-Previously, she would have needed to find a programmer to help her edit
-the adapter code to incorporate this additional data, but using our
-system's support for \textbf{editing by demonstration}, Jen can extend
-the adapter herself.
+Jen has previously used Wildcard to customize timeanddate.com, sorting
+holidays by day of the week. She comes up with a new customization idea:
+sorting holidays by category so she can view all the federal holidays
+together. The current site adapter she is using does not populate the
+category column in the table, so she needs to extend the adapter. She
+can immediately perform the extension in the context of the page, using
+our system's support for \textbf{editing by demonstration}.
 
@@
 that have direct siblings with a similar structure. We refer to this as
-the \emph{row-sibling} constraint. Later in this section, we describe
-how the constraint provides a useful simplification of the wrapper
-induction task and discuss the resulting limitations this puts on our
-system in a section that follows.
+the \emph{row-sibling} constraint. Later, we describe how the constraint
+provides a useful simplification of the wrapper induction task and
+discuss the resulting limitations this puts on our system.
 
@@
 Figure~\ref{fig:algorithm}) as a potential candidate for the row
-element. For each parent element \(n\), the process is as follows:
+element. For each parent element \texttt{el}, the process is as follows:
 
@@
 \item
-  compute a column selector \(s\) that when executed on \(n\) only
-  returns the demonstrated element
+  compute a column selector \texttt{selector} that, when executed on
+  \texttt{el}, only returns the demonstrated element
 \item
-  for each sibling \(m\) of \(n\), execute \(s\) on \(m\) and record
-  whether the selector returned an element. Intuitively, if the selector
-  returns an element, this suggests that the sibling \(m\) has some
-  parallel structure to \(n\)
+  for each sibling \texttt{el\textquotesingle{}} of \texttt{el}, execute
+  \texttt{selector} on \texttt{el\textquotesingle{}} and record whether
+  the selector returns an element. If it does, this suggests that
+  \texttt{el\textquotesingle{}} has some parallel structure to
+  \texttt{el}.
 \item
-  compute \(n_{siblings}\), the number of sibling elements of \(n\) for
-  which \(s\) returned an element
+  compute \(n_{siblings}\), the number of sibling elements of
+  \texttt{el} which have parallel structure.
 \end{enumerate}
 
-Notice how the \emph{row-sibling} constraint simplifies the problem: row
-candidates without siblings that return an element after \(s\) is
-executed on them ((b1) in Figure~\ref{fig:algorithm}) have
-\(n_{siblings}\) = 0, thus disqualifying them. Furthermore, a candidate
-element \(n\) is only accepted as the row element if the row selector
-\(n_{selector}\) associated with it only matches itself and elements
-that are its direct siblings.
+Notice how the \emph{row-sibling} constraint simplifies the problem. Row
+candidates without siblings with parallel structure ((b1) in
+Figure~\ref{fig:algorithm}) have \(n_{siblings}\) = 0, thus
+disqualifying them.
 
 The algorithm stops traversing upwards once it reaches the BODY element.
-Then, it generates a selector \(n_{selector}\) for each \(n\) and
-discards any \(n\) with an \(n_{selector}\) that matches elements that
-are either not itself or a direct sibling. Finally, the algorithm picks
-an \(n\) with the largest, positive \(n_{siblings}\), preferring nodes
-lower in the tree as a tiebreaker. \(n_{selector}\) is used as the
-selector for the row and \(s\) is used as the selector for the column.
-The row and column selectors are used to generate a scraping adapter
-which returns the DOM elements corresponding to a superhero data row in
-the table and sets up the bidirectional synchronization.
+It chooses the element with the largest positive value of
+\(n_{siblings}\) as the row element, preferring nodes lower in the tree
+as a tiebreaker. It then generates a \emph{row selector} which returns
+the row element and all its direct siblings. The column selector is the
+selector that traverses from the row element to the demonstrated data
+value. These row and column selectors are then used to generate a
+scraping adapter which returns the DOM elements corresponding to a data
+row in the table and sets up the bidirectional synchronization.
 
@@
 may not represent data on the website that should be related as part of
-the same table by customizations such as sorting and filtering.
+the same table by customizations such as sorting and filtering. In
+Figure~\ref{fig:limitations} we demonstrate two examples where this
+limitation becomes relevant.
 
@@
   \includegraphics[width=\textwidth]{media/limitations.png}
-  \caption{\label{fig:limitations} Our generalization algorithm cannot generalize on websites with the shown layouts.
+  \caption{\label{fig:limitations} Two example pages where our generalization algorithm does not currently work.
 The elements with the blue border correspond to rows of the data in each layout respectively.}
@@
 
-For \emph{Generalization Limitation 1} shown in
-Figure~\ref{fig:limitations}, without the constraint that row elements
-have to be direct siblings, the row generalization algorithm could
-determine the row selector to be \emph{.avenger} (elements with blue
-border) because it matches the largest number of parallel structures
-(has the largest \(n_{siblings}\)). While this may be the correct result
-for the task of extraction, it is not for the task of customization. The
-selector matches all rows across the two tables (elements with green
-border) so the sorting and filtering customizations could place rows in
-the incorrect table and thereby distort what the tables represent.
-Because of this, our system currently does not support such layouts but
-we plan to explore the possibility of extracting multiple tables from a
-website and joining them.
+\emph{Generalization Limitation 1} shows a case where the data is
+displayed in a grouped structure. Without the constraint that row
+elements have to be direct siblings, the row generalization algorithm
+could determine the row selector to be \emph{.avenger} (elements with
+blue border) because it matches the largest number of parallel
+structures (has the largest \(n_{siblings}\)). While this may be the
+correct result for the task of extraction, it is not necessarily
+suitable for the task of customization. When the user sorts and filters,
+this could result in rows moving between the two tables, disrupting the
+nested layout and producing a confusing result. Because of this, our
+system currently does not support such layouts. In the future, we may
+explore the possibility of extracting multiple tables from a website and
+joining them together.
 
-For \emph{Generalization Limitation 2} shown in
-Figure~\ref{fig:limitations}, website contains one table of data in
-which rows are made up of the alternating H1 and SPAN tags (elements
-with blue border). For the task of extraction, the DOM elements can be
-scraped using the shown classes to output a table in which the values of
-the H1 tags form the first column and the values of the SPAN tag form
-the second column. For the task of customization, our system would need
-to know what the row boundaries were in order for customizations such as
-sorting and filtering to work as expected. In Wildcard, this can be done
-with a hand-coded adapter by creating artificial row boundaries. In
-\emph{Generalization Limitation 2}'s layout, an artificial row boundary
-could be created by representing a row as an H1 tag and the SPAN tag
-that immediately follows it. These artificial rows would form a single
-unit which would not distort the website after a sorting or filtering
-customization. We plan to explore how such artificial row boundaries
-might be created via demonstration in order to support these structures
-(which are not uncommon, and can be seen, for example, in HackerNews).
+\emph{Generalization Limitation 2}, also in
+Figure~\ref{fig:limitations}, shows a case where the website contains
+one table of data in which rows are made up of alternating H1 and SPAN
+tags (elements with blue border). This poses a challenge because each
+row does not correspond directly to a single DOM element; instead, each
+row consists of multiple consecutive DOM elements without any grouped
+structure. Moving the rows when customizing the webpage would require
+treating multiple consecutive elements as a single row. This is
+supported in the underlying Wildcard system, but not yet by our tool.
 
-Another major limitation of our system is our current lack of support
-for scraping data loaded after the initial websites render as the user
-scrolls. Hand-coded adapters can specify event listeners on the DOM to
-re-execute the scraping code when new data is loaded as a user scrolls.
-In future work, will we provide a mechanism for end-users to specify
-when the adapter created via demonstration should re-execute its
-scraping code in response to user scrolling. There is a similar
-limitation for websites that have paged data but it is not clear how
-suitable such pages are for customization to begin with.
+Our system also does not support scraping data loaded after the initial
+websites render as the user scrolls. Site adapters hand-coded in
+Javascript can specify event listeners on the DOM to re-execute the
+scraping code when new data is loaded as a user scrolls. In future work,
+we plan to provide a mechanism for end-users to specify when a
+demonstrated adapter should re-execute its scraping code in response to
+user scrolling. We also do not support scraping data across multiple
+pages of related data, but this context poses more fundamental
+challenges to the idea of web customization, since users would somehow
+need to perform customizations across multiple pages in coordination.
 

### 2021-02-14 paper.tex
edit design principles + related

@@
 adapters would need to switch into an IDE to write code as part of
-customizing a new website.
+customizing a new website. This divide between tasks is common in other
+domains:
 
-This type of divide between tasks appears in other domains. In data
-science, workflows revolve between cleaning and using data but this
-often happens in different environments. The creators of Wrex
-\citep{drosos2020}, an end-user programming-by-example system for data
-wrangling, reported that ``although data scientists were aware of and
-appreciated the productivity benefits of existing data wrangling tools,
-having to leave their native notebook environment to perform wrangling
-limited the usefulness of these tools.'' This was a major reason Wrex
-was developed as an add-on to Jupyter notebooks, the environment in
-which data scientists use their data. In web scraping, if a user comes
-across an omission while working with data scraped from a website, they
-need to switch from the environment in which they are using the data to
-the environment in which they created their scraping code in order to
-edit and re-run it. This can be seen in many end-user web scraping
-systems like Rousillon \citep{chasins2018}and FlashExtract
-\citep{le2014} and commercial tools like import.io \citep{import.io},
-dexi.io \citep{dexi.io}, Octoparse \citep{octoparse} and ParseHub
-\citep{parsehub}. In web customization, the creators of Vegemite
-\citep{lin2009}, a system for end-user programming of mashups, reported
-that participants of its user study thought ``it was confusing to use
-one technique to create the initial table, and another technique to add
-information to a new column.'' This hints at the need for both a unified
-environment and a unified workflow.
+\begin{itemize}
+\tightlist
+\item
+  In \textbf{data science}, workflows revolve between cleaning and using
+  data but this often happens in different environments. The creators of
+  Wrex \citep{drosos2020}, an end-user programming-by-example system for
+  data wrangling, reported that ``although data scientists were aware of
+  and appreciated the productivity benefits of existing data wrangling
+  tools, having to leave their native notebook environment to perform
+  wrangling limited the usefulness of these tools.'' This was a major
+  reason Wrex was developed as an add-on to Jupyter notebooks, the
+  environment in which data scientists use their data.
+\item
+  In \textbf{web scraping,} if a user comes across an omission while
+  working with data scraped from a website, they need to switch from the
+  environment in which they are using the data to the environment in
+  which they created their scraping code in order to edit and re-run it.
+  This can be seen in many end-user web scraping systems like Rousillon
+  \citep{chasins2018}and FlashExtract \citep{le2014} and commercial
+  tools like import.io \citep{import.io}, dexi.io \citep{dexi.io},
+  Octoparse \citep{octoparse} and ParseHub \citep{parsehub}.
+\item
+  In \textbf{web customization}, the creators of Vegemite
+  \citep{lin2009}, a system for end-user programming of mashups,
+  reported that participants of its user study thought ``it was
+  confusing to use one technique to create the initial table, and
+  another technique to add information to a new column.'' This hints at
+  the need for both a unified environment and a unified workflow.
+\end{itemize}
 
@@
 user was initially already using the website. Instead of bringing the
-data to another tool, we have brought a tool to the data. This directly
-relates to the idea of ``in-place toolchains'' \citep{zotero-1362} being
-an integral part of end-user programming systems.
+data to another tool, we have brought a tool to the data. This principle
+relates to the idea of ``in-place toolchains'' \citep{zotero-1362} for
+end-user programming systems: that users should be able to program using
+familiar tools in the context where they already use their software.
 
@@
 
-In Wildcard, if a website's hand-coded adapter ceases to function
-because the website changes, the table may lose its data which means
-that an end-user's customizations may also cease to function.
-Furthermore, end-users are powerless to extend the scraping adapter to
-add columns to the table in order to perform new customizations. This
-goes against MacLean et. al.'s vision of user-tailorable systems
-\citep{maclean1990} that give users ``a feeling of ownership of the
-system, to feel in control of changing the system and to understand what
-can be changed.'' Providing an easy way for users to edit programs is
-therefore fundamental to fully democratizing web customization.
+In the prior iteration of Wildcard, if a website's hand-coded adapter
+stops working correctly because the website changes, an end-user's
+customizations will often break too. Furthermore, end-users cannot
+extend the scraping adapter to add columns to the table in order to
+perform new customizations. This goes against MacLean et. al.'s vision
+of user-tailorable systems \citep{maclean1990} that give users ``a
+feeling of ownership of the system, to feel in control of changing the
+system and to understand what can be changed.'' Providing an easy way
+for users to edit programs is therefore fundamental to fully
+democratizing web customization.
 
@@
 In many programming-by-demonstration web scraping systems
-\citep[\citet{lin2009}]{chasins2018}, users only get \emph{full}
-feedback about the program's execution (generalization and the scraped
-values) after providing \emph{all} the demonstrations. This means they
-cannot adjust their demonstrations in response to the system's feedback
-as they demonstrate.
+\citep{chasins2018, lin2009}, users only get \emph{full} feedback about
+the program's execution (generalization and the scraped values) after
+providing \emph{all} the demonstrations. This means they cannot adjust
+their demonstrations in response to the system's feedback as they
+demonstrate.
 

### 2021-02-14 paper.tex
fix citations on both pdf and html

@@
 the target of demonstration commands (the value of a DOM element under
-the cursor) is the same during both hover and click (incomplete command
-versus complete command). This allows us to take a small step further by
-executing a command before a user completes it, thereby providing them
+the cursor) is the same during both hover and click. This allows us to
+execute a command before a user completes it, thereby providing them
 with a preview of the results on hover.
@@
 tasks, its interface does not provide \emph{full} live feedback about
-its generalizations or the values to be scrapped until all the
+its generalizations or the values to be scraped until all the
 demonstrations have been provided and the generated program has been
@@
 
-Sifter \citep{huynh2006} is a tool that augments well structured
-websites with advanced sorting and filtering functionality. Like
-Wildcard, it uses web scraping to extract data from websites in order to
-enable customizations (sorting and filtering). Unlike Wildcard, it does
-not support adding annotations to websites and running computations on
-the scraped data using a spreadsheet formula language. Both of these
-significantly expand the types of customizations end-users can make to
-websites. Sifter performs the web scraping automatically using a variety
-of heuristics and solicits guidance from the user if this fails. While
-automatic web scraping seems desirable, it is unclear how useful it is
-if the goal is customization. Given a row with ten scrapable values, and
-therefore ten columns, would a user prefer to simply demonstrate the
-value for the single column they are interested in or un-demonstrate the
-nine values they are not interested in? This automatic web scraping
-approach can be also be seen in tools like import.io \citep{import.io}
-so it is certainly worth evaluating as part of a user study.
+Sifter \citep{huynh2006} is a tool that augments websites with advanced
+sorting and filtering functionality. Similarly to Wildcard, it uses web
+scraping techniques to extract data from websites in order to enable
+customizations. However, Wildcard supports a broader range of
+customizations beyond sorting and filtering, including adding
+annotations to websites and running computations with a spreadsheet
+formula language.
+
+Our scraping tool intentionally provides less automation than Sifter.
+Sifter attempts to automatically detect items and fields on the page
+with a variety of clever heuristics, including automatically detecting
+link tags and considering the size of elements on the page. It then
+gives the user the option of correcting the result if the heuristics do
+not work properly. In contrast, our heuristics are simpler and make
+fewer assumptions about the structure of websites. Rather, we give more
+control to the user from the beginning of the process, and incorporate
+live feedback to help the user provide useful demonstrations. We
+hypothesize that focusing on a tight feedback loop rather than
+automation may support a scraping process that is just as fast as an
+automated one, but gives the user finer control and extends to a greater
+variety of websites where more complex heuristics do not apply. However,
+further user testing is required to actually validate this hypothesis.
 
@@
 More testing is needed to understand whether it can be successfully used
-among a broader set set of users across a wider variety of websites.
+among a broader set of users across a wider variety of websites.
 Furthermore, we plan to incorporate the program viewer and
@@
 \bibliographystyle{ACM-Reference-Format}
-\bibliography{references.bib}
+\bibliography{references-bibtex.bib}
 

### 2021-02-14 compile-html.sh

@@ -13,4 +13,5 @@ set -e
   --toc-depth=1 \
   --variable=toc-title:"Contents" \
   --template=templates/pandoc-template-html.html \
+  --bibliography=references-biblatex.bib \
   paper.md

### 2021-02-14 compile-latex.sh

@@ -3,7 +3,8 @@ set -e
 pandoc \
   --filter conditional-render \
   --filter pandoc-crossref \
-    --citeproc \
+  --citeproc \
+  --bibliography=references-bibtex.bib\
   -s \
   -o \
   paper.tex \

### 2021-02-14 paper.tex

@@
   \caption{\label{fig:limitations} Two example pages where our generalization algorithm does not currently work.
-The elements with the blue border correspond to rows of the data in each layout respectively.}
+The elements with the blue border correspond to rows of the data and the elements with green borders correspond to tables of data in each layout respectively.
+For the layout on the left, sorting could lead to rows from one table ending up in the other.
+For the layout on the right, sorting would lead to a distortion of the table since the column elements cannot be moved as a unit.}
 \end{figure*}
@@
 End-user web scraping for customization relates to existing work in
-end-user web scraping by a number of tools.
+end-user web scraping and end-user web customization by a number of
+tools.
+
+\hypertarget{end-user-web-scraping}{%
+\subsection{End-user Web Scraping}\label{end-user-web-scraping}}
 
@@
 
+\hypertarget{end-user-web-customization}{%
+\subsection{End-user Web
+Customization}\label{end-user-web-customization}}
+
 Vegemite \citep{lin2009} is a tool for end-user programming of mashups.
@@
 annotations to websites and running computations with a spreadsheet
-formula language.
-
-Our scraping tool intentionally provides less automation than Sifter.
-Sifter attempts to automatically detect items and fields on the page
-with a variety of clever heuristics, including automatically detecting
-link tags and considering the size of elements on the page. It then
-gives the user the option of correcting the result if the heuristics do
-not work properly. In contrast, our heuristics are simpler and make
-fewer assumptions about the structure of websites. Rather, we give more
-control to the user from the beginning of the process, and incorporate
-live feedback to help the user provide useful demonstrations. We
-hypothesize that focusing on a tight feedback loop rather than
-automation may support a scraping process that is just as fast as an
-automated one, but gives the user finer control and extends to a greater
-variety of websites where more complex heuristics do not apply. However,
-further user testing is required to actually validate this hypothesis.
+formula language. Our scraping tool intentionally provides less
+automation than Sifter. Sifter attempts to automatically detect items
+and fields on the page with a variety of clever heuristics, including
+automatically detecting link tags and considering the size of elements
+on the page. It then gives the user the option of correcting the result
+if the heuristics do not work properly. In contrast, our heuristics are
+simpler and make fewer assumptions about the structure of websites.
+Rather, we give more control to the user from the beginning of the
+process, and incorporate live feedback to help the user provide useful
+demonstrations. We hypothesize that focusing on a tight feedback loop
+rather than automation may support a scraping process that is just as
+fast as an automated one, but gives the user finer control and extends
+to a greater variety of websites where more complex heuristics do not
+apply. However, further user testing is required to actually validate
+this hypothesis.
 

### 2021-02-14 paper.tex
Made final edits

@@
   developed a tool called Wildcard which empowers end-users to customize
-  websites through a data table interface without doing traditional
-  programming. However, there is a limit on end-user flexibility with
-  Wildcard, because programmers need to create site-specific adapters
-  mapping website data to a table view. This means that end-users can
-  only customize a website if a programmer has written an adapter for
-  it, and cannot extend or repair existing adapters.
+  websites through a spreadsheet-like table interface without doing
+  traditional programming. However, there is a limit to end-user agency
+  with Wildcard, because programmers need to first create site-specific
+  adapters mapping website data to the table interface. This means that
+  end-users can only customize a website if a programmer has written an
+  adapter for it, and cannot extend or repair existing adapters.
 
@@
   extend and repair adapters, by performing concrete demonstrations of
-  how the webpage UI maps to a data table. We describe three design
-  principles that guided our system's development and are applicable to
-  other end-user web scraping and customization systems: (a) users
-  should be able to scrape data and use it in a single, unified
-  environment, (b) users should be able to extend and repair the
+  how the website user interface maps to a data table. We describe three
+  design principles that guided our system's development and are
+  applicable to other end-user web scraping and customization systems:
+  (a) users should be able to scrape data and use it in a single,
+  unified environment, (b) users should be able to extend and repair the
   programs that scrape data via demonstration and (c) users should
@@
   example usage scenarios that showcase each of our design principles.
+  Our ultimate goal is to empower end-users to customize websites in an
+  intuitive and flexible way, and thus make websites more malleable for
+  all of its users.
 \end{abstract}
@@
 Many websites on the internet do not meet the exact needs of all of
-their users. End-user web customization systems like Chickenfoot
-\citep{bolin2005}, Thresher \citep{hogue2005}, Sifter \citep{huynh2006}
-and Vegemite \citep{lin2009} help users tweak and adapt websites to fit
-their unique requirements, ranging from reorganizing or annotating
-content on the website to automating common tasks. In our prior work, we
-presented Wildcard \citep{litt2020a}, a customization system which
-enables end-users to customize websites through direct manipulation. It
-does this by augmenting websites with a table view that shows their
-underlying structured data. The table is bidirectionally synchronized
-with the original website, so end-users can easily customize the website
-by interacting with the table, including sorting and filtering data,
-adding annotations, and running computations in a spreadsheet formula
-language.
+their users. End-user web customization systems like Thresher
+\citep{hogue2005}, Sifter \citep{huynh2006} and Vegemite \citep{lin2009}
+help users tweak and adapt websites to fit their unique requirements,
+ranging from reorganizing or annotating content on the website to
+automating common tasks. In our prior work, we presented Wildcard
+\citep{litt2020a}, a customization system which enables end-users to
+customize websites through direct manipulation. It does this by
+augmenting websites with a table view that shows their underlying
+structured data. The table is bidirectionally synchronized with the
+original website, so end-users can easily customize the website by
+interacting with the table, including sorting and filtering data, adding
+annotations, and running computations in a spreadsheet formula language.
 
@@
 
-Finally, we share our broader vision for web scraping for customization,
-and some opportunities for future work, including a proposal for how
-Wildcard's spreadsheet-like formula language might augment
-demonstrations to provide end-users with more expressiveness in the web
-scraping process (Section~\ref{sec:conclusion}).
+Finally, we share our broader vision for \emph{end-user web scraping for
+customization}, and some opportunities for future work, including a
+proposal for how Wildcard's spreadsheet-like formula language might
+augment demonstrations to provide end-users with more expressiveness in
+the web scraping process (Section~\ref{sec:conclusion}).
 
@@
 \item
-  The selected row of data is annotated in the page with a border, to
-  indicate that she will be demonstrating values from within that row
-  (Part 3).
+  The row of data is annotated in the page with a border, to indicate
+  that she will be demonstrating values from within that row (Part 3).
 \item
-  The selected column of data is highlighted in the page with a green
-  background, to show how the system has generalized her demonstration
-  across all the rows in the data (Part 4).
+  The column of data is highlighted in the page with a green background,
+  to show how the system has generalized her demonstration across all
+  the rows in the data (Part 4).
 \item
@@
 
-Jen next visits Google Scholar to look up references for her thesis
-project. Unfortunately, the customization she had applied to sort
-publications by their title (which is not natively supported by Google
-Scholar) is no longer working. In fact, the column in the Wildcard table
-that contained all the publication titles is empty, because the
-website's internals changed and broke the adapter's scraping logic. Jen
-can repair this on her own, again taking advantage of \textbf{editing by
-demonstration}.
+Jen next visits Google Scholar to look up references for a project.
+Unfortunately, the customization she had applied to sort publications by
+their title (which is not natively supported by Google Scholar) is no
+longer working. In fact, the column in the Wildcard table that contained
+all the publication titles is empty, because the website's internals
+changed and broke the adapter's scraping logic. Jen can repair this on
+her own, again taking advantage of \textbf{editing by demonstration}.
 
@@
 then proceeds to save her changes (Part 6) and re-apply her
-customization to the website by sorting the publications by their title
-without the intervention of a programmer.
+customization to the website by sorting the publications by their title.
 
@@
 the basic intuition is to find a large set of elements with similar
-parallel structure. Consider the following sample HTML layout, which
-displays a truncated table of superheroes, with each row containing some
-nested structure:
+parallel structure. Consider the sample HTML layout in
+Figure~\ref{fig:algorithm}, which displays a truncated table of
+superheroes, with each row containing some nested structure:
 
@@
 
-The user performs a demonstration by clicking on element (a) in
+The user performs a demonstration by clicking on element \(a\) in
 Figure~\ref{fig:algorithm} containing ``Tony Stark.'' Our algorithm
 traverses upwards from the demonstrated element, considering each
-successive parent element ((b1), (c1) and (d) in
+successive parent element (\(b1\), \(c1\) and \(d\) in
 Figure~\ref{fig:algorithm}) as a potential candidate for the row
@@
 \item
-  compute \(n_{siblings}\), the number of sibling elements of
+  compute \(el_{siblings}\), the number of sibling elements of
   \texttt{el} which have parallel structure.
@@
 Notice how the \emph{row-sibling} constraint simplifies the problem. Row
-candidates without siblings with parallel structure ((b1) in
-Figure~\ref{fig:algorithm}) have \(n_{siblings}\) = 0, thus
+candidates without siblings with parallel structure (\(b1\) in
+Figure~\ref{fig:algorithm}) have \(el_{siblings}\) = 0, thus
 disqualifying them.
 
-The algorithm stops traversing upwards once it reaches the BODY element.
-It chooses the element with the largest positive value of
-\(n_{siblings}\) as the row element, preferring nodes lower in the tree
+The algorithm stops traversing upwards once it reaches the \texttt{BODY}
+element. It chooses the element with the largest positive value of
+\(el_{siblings}\) as the row element, preferring nodes lower in the tree
 as a tiebreaker. It then generates a \emph{row selector} which returns
-the row element and all its direct siblings. The column selector is the
-selector that traverses from the row element to the demonstrated data
-value. These row and column selectors are then used to generate a
-scraping adapter which returns the DOM elements corresponding to a data
-row in the table and sets up the bidirectional synchronization.
+the row element and all its direct siblings. The final value of
+\texttt{selector} is the column selector since traverses from the row
+element to the demonstrated data value. These row and column selectors
+are then used to generate a scraping adapter which returns the DOM
+elements corresponding to a data row in the table and sets up the
+bidirectional synchronization.
 
@@
 bidirectional synchronization is set up, users can customize as they
-scrape.
+scrape. Live programming is possible in our system because the
+generalization algorithm and adapters execute very quickly. We are yet
+to benchmark the performance and compare it to other
+programming-by-demonstration systems like FlashExtract \citep{le2014}
+that that provide live feedback.
 
@@
 selector does not affect another column's selector. This is not the case
-for system's in which the output of demonstrations are dependent on each
+for systems in which the output of demonstrations are dependent on each
 other. For example, in a web automation sequence that involves clicking
@@
 \subsection{Limitations}\label{limitations}}
+
+\hypertarget{generalization-algorithm}{%
+\subsection{Generalization Algorithm}\label{generalization-algorithm}}
 
@@
 blue border) because it matches the largest number of parallel
-structures (has the largest \(n_{siblings}\)). While this may be the
+structures (has the largest \(el_{siblings}\)). While this may be the
 correct result for the task of extraction, it is not necessarily
@@
 Figure~\ref{fig:limitations}, shows a case where the website contains
-one table of data in which rows are made up of alternating H1 and SPAN
-tags (elements with blue border). This poses a challenge because each
-row does not correspond directly to a single DOM element; instead, each
-row consists of multiple consecutive DOM elements without any grouped
-structure. Moving the rows when customizing the webpage would require
-treating multiple consecutive elements as a single row. This is
-supported in the underlying Wildcard system, but not yet by our tool.
+one table of data in which rows are made up of alternating \texttt{H1}
+and \texttt{SPAN} tags (elements within blue border). This poses a
+challenge because each row does not correspond directly to a single DOM
+element; instead, each row consists of multiple consecutive DOM elements
+without any grouped structure. Moving the rows when customizing the
+website would require treating multiple consecutive elements as a single
+row. This is supported in the underlying Wildcard system, but not yet by
+our demonstration-based approach.
 
-Our system also does not support scraping data loaded after the initial
-websites render as the user scrolls. Site adapters hand-coded in
+\hypertarget{data-loaded-after-initial-render}{%
+\subsection{Data Loaded After Initial
+Render}\label{data-loaded-after-initial-render}}
+
+Our currently system does not support scraping data loaded after the
+initial websites render as the user scrolls. Site adapters hand-coded in
 Javascript can specify event listeners on the DOM to re-execute the
@@
 relates to the idea of ``in-place toolchains'' \citep{zotero-1362} for
-end-user programming systems: that users should be able to program using
+end-user programming systems: users should be able to program using
 familiar tools in the context where they already use their software.
@@
 scraped values for automation. For example, the scripting interface can
-be used to demonstrate the task of copying an address in the table,
+be used to demonstrate the task of copying an address in the data table,
 pasting it into a walk score calculator and pasting the result back into
@@
 annotations to websites and running computations with a spreadsheet
-formula language. Our scraping tool intentionally provides less
+formula language. Our scraping system intentionally provides less
 automation than Sifter. Sifter attempts to automatically detect items
@@
 
-Our end goal is to empower end-users to customize websites in an
+Our ultimate goal is to empower end-users to customize websites in an
 intuitive and flexible way, and thus make the web more malleable for all

### 2021-02-15 paper.tex
fix a couple typos

@@
   Our ultimate goal is to empower end-users to customize websites in an
-  intuitive and flexible way, and thus make websites more malleable for
-  all of its users.
+  intuitive and flexible way, making the web more malleable for all of
+  its users.
 \end{abstract}
@@
 scrape. Live programming is possible in our system because the
-generalization algorithm and adapters execute very quickly. We are yet
-to benchmark the performance and compare it to other
+generalization algorithm and adapters execute very quickly. We have yet
+to benchmark the performance in detail and compare it to other
 programming-by-demonstration systems like FlashExtract \citep{le2014}
-that that provide live feedback.
+that provide live feedback.
 
@@
 \hypertarget{generalization-algorithm}{%
-\subsection{Generalization Algorithm}\label{generalization-algorithm}}
+\subsubsection{Generalization
+Algorithm}\label{generalization-algorithm}}
 
@@
 \hypertarget{data-loaded-after-initial-render}{%
-\subsection{Data Loaded After Initial
+\subsubsection{Data Loaded After Initial
 Render}\label{data-loaded-after-initial-render}}

### 2021-02-16 paper.tex
add a note linking to the online version
Fix typo in section 3.4.2

@@
 \settopmatter{printfolios=true}
+
+\usepackage{hyperref}
 
@@
 \maketitle
+
+This paper is directed at publication.
+We have provided a PDF but it is best viewed in the online version (\href{https://kapaya.github.io/px21/}{kapaya.github.io/px21}) which includes videos demonstrating the system.
 
@@
 
-Our currently system does not support scraping data loaded after the
-initial websites render as the user scrolls. Site adapters hand-coded in
+Our system currently does not support scraping data loaded after the
+initial website renders as the user scrolls. Site adapters hand-coded in
 Javascript can specify event listeners on the DOM to re-execute the

### 2021-03-14 paper.tex
Incorporated PX/21 reviews

@@
   example usage scenarios that showcase each of our design principles.
-  Our ultimate goal is to empower end-users to customize websites in an
-  intuitive and flexible way, making the web more malleable for all of
-  its users.
+  Our ultimate goal is to empower end-users to customize websites in the
+  course of their daily use in an intuitive and flexible way, and thus
+  making the web more malleable for all of its users.
 \end{abstract}
@@
 \citep{hogue2005}, Sifter \citep{huynh2006} and Vegemite \citep{lin2009}
-help users tweak and adapt websites to fit their unique requirements,
+help users to tweak and adapt websites to fit their unique requirements,
 ranging from reorganizing or annotating content on the website to
-automating common tasks. In our prior work, we presented Wildcard
-\citep{litt2020a}, a customization system which enables end-users to
-customize websites through direct manipulation. It does this by
-augmenting websites with a table view that shows their underlying
-structured data. The table is bidirectionally synchronized with the
-original website, so end-users can easily customize the website by
-interacting with the table, including sorting and filtering data, adding
-annotations, and running computations in a spreadsheet formula language.
+automating common tasks. Millions of people also use tools like
+Greasemonkey \citep{zotero-90} and Tampermonkey \citep{zotero-92} to
+install browser userscripts, snippets of Javascript code which customize
+the behavior of websites.
+
+In our prior work, we presented Wildcard \citep{litt2020a}, a
+customization system which enables end-users to customize websites
+through direct manipulation. It does this by augmenting websites with a
+table view that shows their underlying structured data. The table is
+bidirectionally synchronized with the original website, so end-users can
+easily customize the website by interacting with the table, including
+sorting and filtering data, adding annotations, and running computations
+in a spreadsheet formula language. Wildcard enables end-users to be
+\emph{creators} of browser userscripts (and not just consumers) without
+having to write Javascript code.
 
@@
 
-Our key contribution is a set of three design principles that guided the
-development of our system, which also offer insights that might be
-applied to other end-user web scraping and customization tools
+We then describe the principles underlying the design of our system
 (Section~\ref{sec:design-principles}):
@@
 \end{itemize}
+
+While each of these principles has been explored in prior work, our
+contribution in this work is combining them into a novel application to
+the domain of end user web scraping and customization.
 
@@
 We implemented our end-user web scraping system as an addition to the
-Wildcard browser extension. We start by describing our implementations
-of row and column generalization, live programming, and editing by
-demonstration, and then discuss some of the current limitations of our
-system.
+Wildcard browser extension. Prior to this work, website adapters were
+manually coded in Javascript by programmers. Now, adapters can be
+automatically created via demonstration. We start by describing our
+implementations of \emph{wrapper induction} \citep{kushmerick2000}, live
+programming, and editing by demonstration, and then discuss some of the
+current limitations of our system.
 
-\hypertarget{generalization-algorithms}{%
-\subsection{Generalization Algorithms}\label{generalization-algorithms}}
+\hypertarget{wrapper-induction-algorithm}{%
+\subsection{Wrapper Induction
+Algorithm}\label{wrapper-induction-algorithm}}
 
@@
 
-At a high level, the generalization algorithm's challenge is to traverse
-far enough up in the DOM tree from the demonstrated element to find the
-element which corresponds to the row. We solve this using a heuristic;
-the basic intuition is to find a large set of elements with similar
-parallel structure. Consider the sample HTML layout in
+At a high level, the wrapper induction algorithm's challenge is to
+traverse far enough up in the DOM tree from the demonstrated element to
+find the element which corresponds to the row. We solve this using a
+heuristic; the basic intuition is to find a large set of elements with
+similar parallel structure. Consider the sample HTML layout in
 Figure~\ref{fig:algorithm}, which displays a truncated table of
@@
 
-Live programming is implemented by continually running the
-generalization algorithm on the DOM element under the user's cursor,
-reverting if the user hovers away and committing when the user clicks.
-The generated row and column selectors are used to highlight all the
-matching elements on the website and create an adapter. Highlighting all
-the matching column elements on the website provides visual feedback
-about the system's generalization to the user. Creating an adapter
-enables the system to populate the table view and set up the
-bidirectional synchronization. Because the table is populated and the
-bidirectional synchronization is set up, users can customize as they
-scrape. Live programming is possible in our system because the
-generalization algorithm and adapters execute very quickly. We have yet
-to benchmark the performance in detail and compare it to other
-programming-by-demonstration systems like FlashExtract \citep{le2014}
-that provide live feedback.
+The idea of ``liveness'' in programming can be traced back to Tanimoto's
+work on VIVA \citep{tanimoto1990}. It generally describes programming
+environments in which programmers receive immediate feedback about a
+program while it is being created. In the context of Wildcard, adapters
+are the program, the table interface is the output of the program and
+the highlighting on the website is the visual representation of the
+program. Live programming in our system is implemented by continually
+re-generating an adapter based on the DOM element under the user's
+cursor and the previous demonstrations if any, reverting if the user
+hovers away and committing when the user clicks. The row and column
+selectors generated during the wrapper induction process are used to
+highlight all the matching elements on the website and create an
+adapter. Highlighting all the matching column elements on the website
+provides visual feedback about the system's generalization to the user.
+Creating an adapter enables the system to populate the table view and
+set up the bidirectional synchronization. Because the table is populated
+and the bidirectional synchronization is set up, users can customize as
+they scrape. Live programming is possible in our system because the
+wrapper induction algorithm and adapters execute very quickly. We have
+yet to benchmark the performance in detail and compare it to other
+end-user web scraping systems like FlashProg \citep{mayer2015} that
+offer live programming environments.
 
@@
 
-\hypertarget{generalization-algorithm}{%
-\subsubsection{Generalization
-Algorithm}\label{generalization-algorithm}}
+Since our system is still under development, it has a variety of
+limitations. In this section we describe two of the most notable ones.
+
+\hypertarget{wrapper-induction-algorithm-1}{%
+\subsubsection{Wrapper Induction
+Algorithm}\label{wrapper-induction-algorithm-1}}
 
@@
 
-Below, we discuss the three design principles underlying our work and
-how they relate to the broader field of end-user web scraping and
-customization.
+Below, we describe our use of three existing design principles in a
+novel way for the domains of end-user web scraping and customization.
 
@@
 data to another tool, we have brought a tool to the data. This principle
-relates to the idea of ``in-place toolchains'' \citep{zotero-1362} for
+relates to the idea of ``in-place toolchains'' \citep{zotero-60} for
 end-user programming systems: users should be able to program using
@@
 a high-level, block-based programming language called Helena
-\citep{zotero-1349}. Helena supports adding control flow logic
+\citep{zotero-51}. Helena supports adding control flow logic
 (conditional execution, wait times etc) which is invaluable for
@@
 \citep{chasins2018, lin2009}, users only get \emph{full} feedback about
-the program's execution (generalization and the scraped values) after
-providing \emph{all} the demonstrations. This means they cannot adjust
-their demonstrations in response to the system's feedback as they
-demonstrate.
+the program's execution (result of wrapper induction and the scraped
+values) after providing \emph{all} the demonstrations. This means they
+cannot adjust their demonstrations in response to the system's feedback
+as they demonstrate.
 
-Our end-user web scraping system employs live programming techniques to
-eliminate this edit-compile-debug cycle by running the generalization
-algorithm and generating an adapter after each user demonstration. As we
-showed in Section~\ref{sec:demos}, when a user demonstrates a value of a
-column they wish to scrape, our system immediately shows how it has
-generalized the user's demonstration across the other rows of the data
-by highlighting the all relevant values. It also populates the table
-with the scraped data based on the latest demonstration. The
-highlighting and table population serve to give users a view of how
-their demonstration has been generalized and what data will be available
-in the table once scraped.
+Our end-user web scraping system provides level 3 liveness under
+Tanimoto's liveness hierarchy \citep{tanimoto1990}. Level 3 liveness
+describes a system that is constantly listening for actions from the
+user, automatically re-constructing and re-executing the program
+whenever one happens instead of requiring an explicit command from the
+user. To eliminate the described edit-compile-debug cycle, our system
+automatically runs the wrapper induction algorithm and generates an
+adapter after each user demonstration. As we showed in
+Section~\ref{sec:demos}, when a user demonstrates a value of a column
+they wish to scrape, our system immediately shows how it has generalized
+the user's demonstration across the other rows of the data by
+highlighting the all relevant values on the website. It also populates
+the table with the scraped data based on the latest demonstration. The
+highlighting and table population serve to provide a visual
+representation of the adapter's execution.
 
@@
 end-user programming is ``interaction with a living system''
-\citep{zotero-1362}.
+\citep{zotero-60}.
 
@@
 demonstration as an editable, high-level, block-based language called
-Helena \citep{zotero-1349}. While Helena can be used to perform more
+Helena \citep{zotero-51}. While Helena can be used to perform more
 complex editing tasks like adding control flow, it does not support
@@
 Like existing programming-by-demonstration approaches, web scraping in
-our current implementation is limited to what can be demonstrated. This
-is problematic if users want to scrape the URL associated with a link
-element, which is not visible, or only scrape a substring of a value. To
-solve this, we plan to harness Wildcard's formula language. End-users
-will be able to use formulas targeted at web scraping to access DOM
-element properties and attributes. For example, a formula like
-\texttt{=GetAttribute(link\_column,\ ‘href’)} could be used to scrape
-URLs of link elements. End-users will also be able to use formulas
-targeted at data processing. For example, a formula like
-\texttt{=GetSubstring(name\_column,\ 1,\ 2)} could be used to scrape
-substrings of text values. Such web scraping and data processing
-formulas will give end-users some of the power available to programmers
-that write web scraping code in Javascript which supports a wide variety
-of DOM access and processing ability.
+our current implementation is limited to what can be demonstrated by
+point-and-click. More generally, this surfaces a fundamental limitation
+of programming-by-demonstration: the inability to specify logic. One
+solution for this is taking advantage of spreadsheet formulas which have
+enabled millions of end-users to specify logic. Because of this,
+Wildcard already includes a spreadsheet-like formula language for
+specifying customizations. We plan to extend this language to augment
+our demonstration-based web scraping with the goal of raising the
+ceiling on the expressiveness available to end-users. One concrete use
+case for this is scraping DOM element attributes which cannot be
+demonstrated by point-and-click but contain valuable data. For example,
+link elements have an \emph{href} attribute which contain the URLs
+associated with the link element and video elements have
+\emph{currentTime} and \emph{duration} attributes which contain data
+about the current playback position and duration respectively. This use
+of spreadsheet-like formulas to specify logic is related to approaches
+taken by Microsoft Power Apps \citep{zotero-94}, Glide
+\citep{zotero-108}, Coda \citep{zotero-110} and Gneiss
+\citep{chang2014}.
 
@@
 More testing is needed to understand whether it can be successfully used
-among a broader set of users across a wider variety of websites.
-Furthermore, we plan to incorporate the program viewer and
-disambiguation features of FlashProg \citep{mayer2015} to give users
-more insight and control into the generalization process.
+among a broader set of users across a wider variety of websites. We also
+plan to provide more insight, feedback and control into the wrapper
+induction process. This is particularly important when the system
+produces an error or is not able to generate an adapter for a website.
+One solution for this would be to incorporate a version of the program
+viewer and disambiguation features of FlashProg \citep{mayer2015}.
+Wrangler \citep{kandel2011}, whose interface is also centered around a
+table representation, could also provide some inspiration.
 
-Our ultimate goal is to empower end-users to customize websites in an
-intuitive and flexible way, and thus make the web more malleable for all
-of its users.
+Our ultimate goal is to empower end-users to customize websites in the
+course of their daily use in an intuitive and flexible way, and thus
+make the web more malleable for all of its users.
 

### 2021-03-14 paper.tex
Changes to 3.2 and minor wording changes in other parts

@@
 
-While each of these principles has been explored in prior work, our
-contribution in this work is combining them into a novel application to
-the domain of end user web scraping and customization.
+While each of these principles has been explored in prior work by
+various researchers, our contribution in this work is combining them in
+a novel way for the domain of end-user web scraping and customization.
 
@@
 the highlighting on the website is the visual representation of the
-program. Live programming in our system is implemented by continually
+program.
+
+Live programming in our system is implemented by continually
 re-generating an adapter based on the DOM element under the user's
@@
 about the current playback position and duration respectively. This use
-of spreadsheet-like formulas to specify logic is related to approaches
-taken by Microsoft Power Apps \citep{zotero-94}, Glide
-\citep{zotero-108}, Coda \citep{zotero-110} and Gneiss
+of spreadsheet-like formulas to enable end-users to specify logic is
+related to approaches taken by Microsoft Power Apps \citep{zotero-94},
+Glide \citep{zotero-108}, Coda \citep{zotero-110} and Gneiss
 \citep{chang2014}.

### 2021-03-14 paper.tex
Add Wildcard citation from Onward!

@@
 
-In our prior work, we presented Wildcard \citep{litt2020a}, a
+In our prior work, we presented Wildcard \citep{litt2020a, litt2020b}, a
 customization system which enables end-users to customize websites
@@
 In order to generate reusable scrapers from user demonstrations, our
-system solves the \emph{wrapper induction} \citep{kushmerick2000} task:
+system solves the wrapper induction \citep{kushmerick2000} task:
 generalizing from a small set of user-provided examples to a scraping

### 2021-04-09 paper.tex
Removed ads from demo screenshots and added acknoledgements section
Removed reference to web version from PDF

@@
 \maketitle
-
-This paper is directed at publication.
-We have provided a PDF but it is best viewed in the online version (\href{https://kapaya.github.io/px21/}{kapaya.github.io/px21}) which includes videos demonstrating the system.
 
@@
 
+\hypertarget{acknowledgements}{%
+\section{Acknowledgements}\label{acknowledgements}}
+
+Thank you to Gloria Lin, Joshua Pollock, the members of MIT's Software
+Design Group, the anonymous reviewers of PX/21 and the particpants of
+PX/21 for providing valuable feedback on this work.
+
 % \printbibliography

### 2021-04-09 paper.tex
Remved link to web version from demos section

@@
 In this section, we show how end-users can create, extend and repair
-adapters for Wildcard via demonstration.{ These demos are best viewed as
-videos in the online version of this paper
-(\url{https://kapaya.github.io/px21}).}
+adapters for Wildcard via demonstration.
 

### 2021-05-11 paper.tex
Preparing paper for publication

@@
 %%\citestyle{acmauthoryear}
+
+%%% The following is specific to <Programming'21> Companion-PX and the paper
+%%% 'Towards End-User Web Scraping for Customization'
+%%% by Kapaya Katongo, Geoffrey Litt, and Daniel Jackson.
+%%%
+\setcopyright{rightsretained}
+\acmPrice{}
+\acmDOI{10.1145/3464432.3464437}
+\acmYear{2021}
+\copyrightyear{2021}
+\acmSubmissionID{prog21pxmain-p5-p}
+\acmISBN{978-1-4503-8986-0/21/03}
+\acmConference[<Programming'21> Companion]{Companion Proceedings of the 5th International Conference on the Art, Science, and Engineering of Programming}{March 22--26, 2021}{Virtual, UK}
+\acmBooktitle{Companion Proceedings of the 5th International Conference on the Art, Science, and Engineering of Programming (<Programming'21> Companion), March 22--26, 2021, Virtual, UK}
 
@@
    <concept>
+       <concept_id>10003120.10003121.10003124.10010868</concept_id>
+       <concept_desc>Human-centered computing~Web-based interaction</concept_desc>
+       <concept_significance>500</concept_significance>
+       </concept>
+   <concept>
        <concept_id>10011007.10011006.10011066.10011069</concept_id>
@@
 
+\ccsdesc[500]{Human-centered computing~Web-based interaction}
 \ccsdesc[500]{Software and its engineering~Integrated and visual development environments}
@@
 %% the work being presented. Separate the keywords with commas.
-\keywords{end-user programming, software customization, web scraping, programming by example}
+\keywords{software customization, browser extensions, end-user programming, spreadsheets, web scraping}
 
@@
 
-\hypertarget{acknowledgements}{%
-\section{Acknowledgements}\label{acknowledgements}}
-
-Thank you to Gloria Lin, Joshua Pollock, the members of MIT's Software
-Design Group, the anonymous reviewers of PX/21 and the particpants of
-PX/21 for providing valuable feedback on this work.
+\section*{Acknowledgments}
+Thank you to Gloria Lin, Joshua Pollock, the members of MIT's Software Design Group,
+the anonymous reviewers of PX/21 and the particpants of PX/21 for providing valuable
+feedback on this work. The authors gratefully acknowledge the support of the CNS division of the National Science Foundation
+through award number 1801399.
 

### 2021-05-11 paper.tex
Update HTML acknowledgements section as well

@@
 \section*{Acknowledgments}
-Thank you to Gloria Lin, Joshua Pollock, the members of MIT's Software Design Group,
-the anonymous reviewers of PX/21 and the particpants of PX/21 for providing valuable
-feedback on this work. The authors gratefully acknowledge the support of the CNS division of the National Science Foundation
-through award number 1801399.
+
+Thank you to Gloria Lin, Joshua Pollock, the members of MIT's Software
+Design Group, the anonymous reviewers of PX/21 and the particpants of
+PX/21 for providing valuable feedback on this work. The authors
+gratefully acknowledge the support of the CNS division of the National
+Science Foundation through award number 1801399.
 

### 2021-06-09 paper.tex
Made changes recommended by conference publishing

@@
 %% The first command in your LaTeX source must be the \documentclass command.
-\documentclass[sigconf,10pt]{acmart}
+\documentclass[sigconf,screen]{acmart}
 
@@
 \usepackage{hyperref}
+\usepackage{microtype}
+\usepackage{balance}
 
@@
 
-%%% The following is specific to <Programming'21> Companion-PX and the paper
+%%% The following is specific to <Programming> '21 Companion-PX and the paper
 %%% 'Towards End-User Web Scraping for Customization'
@@
 \acmISBN{978-1-4503-8986-0/21/03}
-\acmConference[<Programming'21> Companion]{Companion Proceedings of the 5th International Conference on the Art, Science, and Engineering of Programming}{March 22--26, 2021}{Virtual, UK}
-\acmBooktitle{Companion Proceedings of the 5th International Conference on the Art, Science, and Engineering of Programming (<Programming'21> Companion), March 22--26, 2021, Virtual, UK}
+\acmConference[<Programming> '21 Companion]{Companion Proceedings of the 5th International Conference on the Art, Science, and Engineering of Programming}{March 22--26, 2021}{Virtual, UK}
+\acmBooktitle{Companion Proceedings of the 5th International Conference on the Art, Science, and Engineering of Programming (<Programming> '21 Companion), March 22--26, 2021, Virtual, UK}
+
+\pagenumbering{gobble}
 
@@
 %% allowing the author to define a "short title" to be used in page headers.
-\title{Towards End-user Web Scraping For Customization}
+\title{Towards End-User Web Scraping for Customization}
 
@@
 \hypertarget{creating-an-adapter}{%
-\subsection{Creating An Adapter}\label{creating-an-adapter}}
+\subsection{Creating an Adapter}\label{creating-an-adapter}}
 
@@
 \hypertarget{extending-an-adapter}{%
-\subsection{Extending An Adapter}\label{extending-an-adapter}}
+\subsection{Extending an Adapter}\label{extending-an-adapter}}
 
@@
 \hypertarget{repairing-an-adapter}{%
-\subsection{Repairing An Adapter}\label{repairing-an-adapter}}
+\subsection{Repairing an Adapter}\label{repairing-an-adapter}}
 
@@
 \hypertarget{editing-by-demonstration}{%
-\subsection{Editing By Demonstration}\label{editing-by-demonstration}}
+\subsection{Editing by Demonstration}\label{editing-by-demonstration}}
 
@@
 \hypertarget{data-loaded-after-initial-render}{%
-\subsubsection{Data Loaded After Initial
+\subsubsection{Data Loaded after Initial
 Render}\label{data-loaded-after-initial-render}}
@@
 \hypertarget{editing-by-demonstration-1}{%
-\subsection{Editing By Demonstration}\label{editing-by-demonstration-1}}
+\subsection{Editing by Demonstration}\label{editing-by-demonstration-1}}
 
@@
 \hypertarget{end-user-web-scraping}{%
-\subsection{End-user Web Scraping}\label{end-user-web-scraping}}
+\subsection{End-User Web Scraping}\label{end-user-web-scraping}}
 
@@
 \hypertarget{end-user-web-customization}{%
-\subsection{End-user Web
+\subsection{End-User Web
 Customization}\label{end-user-web-customization}}
@@
 \bibliographystyle{ACM-Reference-Format}
+\balance
 \bibliography{references-bibtex.bib}
